---
title: "mi_front_end_prelim_cross_tabs"
author: "Andrew Byrum"
date: "3/16/2022"
output: html_document
---

# {.tabset .tabset-fade .tabset-pills}
```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","tidylog","csgjcr","psych")
```

```{r include=FALSE}
# file path to analytic files
MI_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Converted/Final/Analytic Files")

### import final analytic file
df_mi_front_end_analytic <- read_csv(file = file.path(MI_path, "MI_JJ_joined_file.csv")) %>% 
  ### clean dates and add labels to vars we want to include in tables
  mutate(petition_date = mdy(petition_date),
         disp_date = mdy(disp_date),
         offense_date = mdy(offense_date),
         petition_year = as.character(year(petition_date))) %>% 
  mutate(race_ethnic = factor(race_ethnic,
         levels = c(1,2,3,4,5,6,7),
         labels = c("White", "Black", "Hispanic", "American Indian/Alaska Native","Asian/Pacific Islander", "Multiracial","Other"))) %>% 
  mutate(sex = factor(sex,
         levels = c(1,2),
         labels = c("Female", "Male"))) %>% 
  mutate(off_lvl_disp = factor(off_lvl_disp,
         levels = c(1,2,3,4,5,6),
         labels = c("Felony, Person", "Felony, Non-Person", "Misdemeanor, Person", "Misdemeanor, Non-Person","Status","Other"))) %>% 
  mutate(off_lvl_pet = factor(off_lvl_pet,
         levels = c(1,2,3,4,5,6),
         labels = c("Felony, Person", "Felony, Non-Person", "Misdemeanor, Person", "Misdemeanor, Non-Person","Status","Other"))) %>% 
  mutate(age_cat = factor(age_cat,
         levels = c(1,2,3,4,5),
         labels = c("Less than 12", "12 to 14", "14 to 16", "16 to 18","18+"))) %>% 
  mutate(disp_desc = factor(disp_desc,
         levels = c(1,2,3),
         labels = c("Adjudication", "Non-Adjudication", "Other")))
```

## Analysis Outline

**Number of unique petitions overall**

* Count/Proportion By Demographics (Year, Race/Ethnicity, Offense(off_lvl_pet), Categorical Age)

<br>

**Number of unique petitions filed where CONSENT CALENDAR is an option (cc_id = 1)**

* Count/Proportion By Demographics (Year, Race/Ethnicity, Offense, Categorical Age)

<br>

**Number of unique petitions adjudicated/non-adjudicated/other (disp_desc)**

* Count/Proportion By Demographics (Year, Race/Ethnicity, Offense (off_lvl_disp), Categorical Age)

<br>

**Adjudication (disp_desc=1) RRI (Black:White)**

* We'll need to pull in census juvenile population (10-17) data for each county

<br>

**Avg num of petitions per unique kid id**

* Assess difference in means by race (I don’t know what the race/eth breakdowns look like, if groups are big enough, compare to White)

<br>

**Avg num of adjudications per unique kid id**

* Assess difference in means by race

<br>

## Overall Petitions

<br>

### Count/Proportion by Year
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_year_denom <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_year_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  group_by(petition_year) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_year_denom$`Petition N`*100, digits = 1)) %>% 
  ungroup() 

petition_count_year_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_year_denom$`Petition N`*100, digits = 1)) %>% 
  mutate(petition_year = "Overall")

### combine
petition_count_year_table_combined <- rbind(petition_count_year_table,petition_count_year_table_overall)

### print table via kableextra
kable(petition_count_year_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

### Count/Proportion by Race/Ethnicity (missing race/ethnicity data for 12% of petitions)
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_race_denom <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_race_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  group_by(race_ethnic) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_race_denom$`Petition N`*100, digits = 1)) %>% 
  ungroup() 

### print table via kableextra
kable(petition_count_race_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### Count/Proportion by Gender 
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_gender_denom <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_gender_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  group_by(sex) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_gender_denom$`Petition N`*100, digits = 1)) %>% 
  ungroup() 

### print table via kableextra
kable(petition_count_gender_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### Count/Proportion by Offense (off_lvl_disp; most serious adjudicated offense)
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_off_denom <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_off_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  group_by(off_lvl_disp) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_off_denom$`Petition N`*100, digits = 1)) %>% 
  ungroup() 

### print table via kableextra
kable(petition_count_off_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### Count/Proportion by Age
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_denom <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_age_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_age_denom$`Petition N`*100, digits = 1)) %>% 
  ungroup() 

### print table via kableextra
kable(petition_count_age_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

## Consent Calendar

<br>

### Count/Proportion by Year

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_cc_count_year_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  group_by(petition_year) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_cc_count_year_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(petition_year = "Overall")

### combine
petition_cc_count_year_table_combined <- rbind(petition_cc_count_year_table,petition_cc_count_year_table_overall)

### print table via kableextra
kable(petition_cc_count_year_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

### Count/Proportion by Race/Ethnicity (missing race/ethnicity data for 12% of petitions)

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_race_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  group_by(race_ethnic) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_race_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(race_ethnic = "Overall")

### combine
petition_count_race_table_combined <- rbind(petition_count_race_table,petition_count_race_table_overall)

### print table via kableextra
kable(petition_count_race_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br><br>

### Count/Proportion by Gender 

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_gender_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  group_by(sex) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_gender_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(sex = "Overall")

### combine
petition_count_gender_table_combined <- rbind(petition_count_gender_table,petition_count_gender_table_overall)

### print table via kableextra
kable(petition_count_gender_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br><br>

### Count/Proportion by Offense (off_lvl_disp; most serious adjudicated offense)

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_off_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  group_by(off_lvl_disp) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_off_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(off_lvl_disp = "Overall")

### combine
petition_count_off_table_combined <- rbind(petition_count_off_table,petition_count_off_table_overall)

### print table via kableextra
kable(petition_count_off_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br><br>

### Count/Proportion by Age

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_age_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(age_cat = "Overall") 

### combine
petition_count_age_table_combined <- rbind(petition_count_age_table,petition_count_age_table_overall)

### print table via kableextra
kable(petition_count_age_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Adjudication

<br>

### Count/Proportion by Year

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_cc_count_year_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  group_by(petition_year) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_cc_count_year_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(petition_year = "Overall")

### combine
petition_cc_count_year_table_combined <- rbind(petition_cc_count_year_table,petition_cc_count_year_table_overall)

### print table via kableextra
kable(petition_cc_count_year_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

### Count/Proportion by Race/Ethnicity (missing race/ethnicity data for 12% of petitions)

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_race_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  group_by(race_ethnic) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>%  
  ungroup() 

petition_count_race_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(race_ethnic = "Overall")

### combine
petition_count_race_table_combined <- rbind(petition_count_race_table,petition_count_race_table_overall)

### print table via kableextra
kable(petition_count_race_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br><br>

### Count/Proportion by Gender 

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_gender_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  group_by(sex) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_gender_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(sex = "Overall")

### combine
petition_count_gender_table_combined <- rbind(petition_count_gender_table,petition_count_gender_table_overall)

### print table via kableextra
kable(petition_count_gender_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br><br>

### Count/Proportion by Offense (off_lvl_disp; most serious adjudicated offense)

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_off_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  group_by(off_lvl_disp) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_off_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(off_lvl_disp = "Overall")

### combine
petition_count_off_table_combined <- rbind(petition_count_off_table,petition_count_off_table_overall)

### print table via kableextra
kable(petition_count_off_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br><br>

### Count/Proportion by Age

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_age_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(age_cat = "Overall") 

### combine
petition_count_age_table_combined <- rbind(petition_count_age_table,petition_count_age_table_overall)

### print table via kableextra
kable(petition_count_age_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>
