---
title: "mi_front_end_prelim_cross_tabs"
author: "Andrew Byrum"
date: "3/16/2022"
output: html_document
---

# {.tabset .tabset-fade .tabset-pills}
```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","tidylog","csgjcr","psych")
```

```{r include=FALSE}
# file path to analytic files
MI_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Converted/Final/Analytic Files")

### import final analytic file
df_mi_front_end_analytic <- read_csv(file = file.path(MI_path, "MI_JJ_joined_file.csv")) %>% 
  ### clean dates and add labels to vars we want to include in tables
  mutate(petition_date = mdy(petition_date),
         disp_date = mdy(disp_date),
         offense_date = mdy(offense_date),
         petition_year = as.character(year(petition_date))) %>% 
  mutate(race_ethnic = factor(race_ethnic,
         levels = c(1,2,3,4,5,6,7),
         labels = c("White", "Black", "Hispanic", "American Indian/Alaska Native","Asian/Pacific Islander", "Multiracial","Other"))) %>% 
  mutate(sex = factor(sex,
         levels = c(1,2),
         labels = c("Female", "Male"))) %>% 
  mutate(off_lvl_disp = factor(off_lvl_disp,
         levels = c(1,2,3,4,5,6),
         labels = c("Felony, Person", "Felony, Non-Person", "Misdemeanor, Person", "Misdemeanor, Non-Person","Status","Other"))) %>% 
  mutate(off_lvl_pet = factor(off_lvl_pet,
         levels = c(1,2,3,4,5,6),
         labels = c("Felony, Person", "Felony, Non-Person", "Misdemeanor, Person", "Misdemeanor, Non-Person","Status","Other"))) %>% 
  mutate(age_cat_old = factor(age_cat,
         levels = c(1,2,3,4,5),
         labels = c("Less than 12", "12 to 14", "14 to 16", "16 to 18","18+"))) %>% 
  mutate(age_cat = case_when(age < 11 ~ 1,
                             age >= 11 & age < 13 ~ 2,
                             age >= 13 & age < 17 ~ 3,
                             age >= 17 & age < 21 ~ 4),
         age_cat = factor(age_cat,
         levels = c(1,2,3,4),
         labels = c("10 and under", "11 to 12", "13 to 16", "17+"))) %>% 
  mutate(disp_desc = factor(disp_desc,
         levels = c(1,2,3),
         labels = c("Adjudication", "Non-Adjudication", "Other")))
```

## Analysis Outline

**1. Number of unique petitions overall**

*Count/Proportion By Demographics:*

<br>

* Year

* Race/Ethnicity

* Most serious offense, at petition and adjudicated 

* Categorical Age (recoded)

* Petition Rate by County

<br>

**2. Number of unique petitions filed where CONSENT CALENDAR is an option (cc_id = 1)**

*Count/Proportion By Demographics:*

<br>

* Year

* Race/Ethnicity

* Most serious offense, at petition and adjudicated 

* Categorical Age (recoded)


<br>

**3. Number of unique petitions adjudicated/non-adjudicated/other (disp_desc)**

*Count/Proportion By Demographics:*

<br>

* Year

* Race/Ethnicity

* Most serious offense, at petition and adjudicated 

* Categorical Age (recoded)

* Adjudication Rate by County

<br><br>

## Overall Petitions

<br>

### Count/Proportion by Year
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_year_denom <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_year_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  group_by(petition_year) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_year_denom$`Petition N`*100, digits = 1)) %>% 
  ungroup() 

petition_count_year_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_year_denom$`Petition N`*100, digits = 1)) %>% 
  mutate(petition_year = "Overall")

### combine
petition_count_year_table_combined <- rbind(petition_count_year_table,petition_count_year_table_overall)

### print table via kableextra
kable(petition_count_year_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

### Count/Proportion by Race/Ethnicity (missing race/ethnicity data for 12% of petitions)
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_race_denom <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_race_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  group_by(race_ethnic) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_race_denom$`Petition N`*100, digits = 1)) %>% 
  ungroup() 

### print table via kableextra
kable(petition_count_race_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### Count/Proportion by Gender 
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_gender_denom <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_gender_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  group_by(sex) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_gender_denom$`Petition N`*100, digits = 1)) %>% 
  ungroup() 

### print table via kableextra
kable(petition_count_gender_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### Count/Proportion by Offense
```{r echo=FALSE,warning=FALSE, message=FALSE}
### most serious petitioned offense
petition_count_off_denom_pet <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_pet)==TRUE) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_off_table_pet <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_pet)==TRUE) %>% 
  group_by(off_lvl_pet) %>% 
  summarise(`Petitions, at Petition (N)` = n_distinct(pet_id), 
            `Petitions, at Petition (%)` = round(n_distinct(pet_id)/petition_count_off_denom_pet$`Petition N`*100, digits = 1)) %>% 
  ungroup() %>% 
  rename(off_lvl = off_lvl_pet)

### most serious adjudicated offense
petition_count_off_denom_adj <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_off_table_adj <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  group_by(off_lvl_disp) %>% 
  summarise(`Petitions, at Adjudication (N)` = n_distinct(pet_id), 
            `Petitions, at Adjudication (%)` = round(n_distinct(pet_id)/petition_count_off_denom_adj$`Petition N`*100, digits = 1)) %>% 
  ungroup() %>% 
  rename(off_lvl = off_lvl_disp)

### join two tables
petition_count_off_table <- left_join(petition_count_off_table_pet,petition_count_off_table_adj, by = "off_lvl")

### print table via kableextra
kable(petition_count_off_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### Count/Proportion by Age
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_denom <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  summarise(`Petition N` = n_distinct(pet_id)) 

petition_count_age_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Petitions (%)` = round(n_distinct(pet_id)/petition_count_age_denom$`Petition N`*100, digits = 1)) %>% 
  ungroup() 

### print table via kableextra
kable(petition_count_age_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### Petitions per 10k youth by county, 2016-2020
```{r echo=FALSE,message=FALSE,warning=FALSE}
### set theme for now
theme_set(theme_minimal())

### import ezapop race/ethnicity data for 10-17 y/o michigan residents for rate calculation
df_ezapop_race_ethnicity_10_16_county_level <- readr::read_delim("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Ezapop\\ezapop_10_16_race_eth_sex_mi.txt", delim = "|") %>% 
  mutate(county_name =  gsub(" County", "", county_name),
         county_id = as.numeric(paste0(state_code,county_code))) %>% 
  dplyr::select(county_name,county_id,overall_10_16_population)

### create overall file for numerator in % calculation below
df_mi_front_end_analytic_county <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(county_id)==TRUE) %>% 
  distinct(pet_id,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode where there is county data
  group_by(county_id) %>% 
  summarize(placement_case_count = n_distinct(pet_id[age>=10 & age <17])) %>% 
  ungroup() %>% 
  left_join(df_ezapop_race_ethnicity_10_16_county_level, by = "county_id") %>% 
  mutate(placements_per_10k_youth = round(placement_case_count/overall_10_16_population*10000, digits = 1))

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- df_mi_front_end_analytic_county %>%
  pull(placements_per_10k_youth) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels youth pop
label_petition_rate <- c("1399 to 1944","1152 to 1399","859 to 1152", "400 to 859")

### create a new variable with the specified quantiles
df_mi_front_end_analytic_county %<>%
  mutate(placements_per_10k_youth_quartile = cut(-placements_per_10k_youth,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_petition_rate,
                               include.lowest = T)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) 


### plot
ggplot(data = df_mi_front_end_analytic_county,
            mapping = aes(x = reorder(county_anonymous, placements_per_10k_youth), y = placements_per_10k_youth, fill = placements_per_10k_youth_quartile)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(limits=c(min(0), 
                                           max(2050))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 5, y = 1250, label = "Each bar represents one county's\n petition rate", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = "Petitions per 10k Youth") +
    coord_flip() +
  guides(fill = guide_legend(reverse = FALSE)) 
```

<br><br>

## Consent Calendar

<br>

### Count/Proportion by Year

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_cc_count_year_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  group_by(petition_year) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_cc_count_year_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(petition_year = "Overall")

### combine
petition_cc_count_year_table_combined <- rbind(petition_cc_count_year_table,petition_cc_count_year_table_overall)

### print table via kableextra
kable(petition_cc_count_year_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

### Count/Proportion by Race/Ethnicity (missing race/ethnicity data for 12% of petitions)

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_race_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  group_by(race_ethnic) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_race_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(race_ethnic = "Overall")

### combine
petition_count_race_table_combined <- rbind(petition_count_race_table,petition_count_race_table_overall)

### print table via kableextra
kable(petition_count_race_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br><br>

### Count/Proportion by Gender 

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_gender_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  group_by(sex) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_gender_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(sex = "Overall")

### combine
petition_count_gender_table_combined <- rbind(petition_count_gender_table,petition_count_gender_table_overall)

### print table via kableextra
kable(petition_count_gender_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br><br>

### Count/Proportion by Offense (off_lvl_disp; most serious adjudicated offense)

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_off_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  group_by(off_lvl_disp) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_off_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(off_lvl_disp = "Overall")

### combine
petition_count_off_table_combined <- rbind(petition_count_off_table,petition_count_off_table_overall)

### print table via kableextra
kable(petition_count_off_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br><br>

### Count/Proportion by Age

Note: Consent Calendar % is out of counties with consent calendar practice/data (PCS and TCS only) -- noted as "Consent Calendar Eligible"
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_age_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar Eligible (N)` = n_distinct(pet_id[!is.na(cc_ind)==TRUE]),
            `Petitions, Consent Calendar Eligible (%)` = round(n_distinct(pet_id[!is.na(cc_ind)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar Eligible (N)`*100, digits = 1)) %>% 
  mutate(age_cat = "Overall") 

### combine
petition_count_age_table_combined <- rbind(petition_count_age_table,petition_count_age_table_overall)

### print table via kableextra
kable(petition_count_age_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Adjudication

<br>

### Count/Proportion by Year

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_cc_count_year_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  group_by(petition_year) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_cc_count_year_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(petition_year = "Overall")

### combine
petition_cc_count_year_table_combined <- rbind(petition_cc_count_year_table,petition_cc_count_year_table_overall)

### print table via kableextra
kable(petition_cc_count_year_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

### Count/Proportion by Race/Ethnicity (missing race/ethnicity data for 12% of petitions)

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_race_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  group_by(race_ethnic) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>%  
  ungroup() 

petition_count_race_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(race_ethnic)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(race_ethnic = "Overall")

### combine
petition_count_race_table_combined <- rbind(petition_count_race_table,petition_count_race_table_overall)

### print table via kableextra
kable(petition_count_race_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br><br>

### Count/Proportion by Gender 

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_gender_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  group_by(sex) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_gender_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(sex)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(sex = "Overall")

### combine
petition_count_gender_table_combined <- rbind(petition_count_gender_table,petition_count_gender_table_overall)

### print table via kableextra
kable(petition_count_gender_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br><br>

### Count/Proportion by Offense (off_lvl_disp; most serious adjudicated offense)

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_off_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  group_by(off_lvl_disp) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_off_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(off_lvl_disp)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(off_lvl_disp = "Overall")

### combine
petition_count_off_table_combined <- rbind(petition_count_off_table,petition_count_off_table_overall)

### print table via kableextra
kable(petition_count_off_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br><br>

### Count/Proportion by Age

Note: Petitions with Missing Adjudication (what MI calls disposition) data dropped from Adjudication/Non-Adjudication/Other %'s
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  ungroup() 

petition_count_age_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(age_cat)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, with Adj Data (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Petitions, with Adj Data (%)` = round(n_distinct(pet_id[!is.na(disp_desc)==TRUE])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Non-Adjudication (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, with Adj Data (N)`*100, digits = 1),
            `Petitions, Other (%)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, with Adj Data (N)`*100, digits = 1)) %>% 
  mutate(age_cat = "Overall") 

### combine
petition_count_age_table_combined <- rbind(petition_count_age_table,petition_count_age_table_overall)

### print table via kableextra
kable(petition_count_age_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

### Adjudications per 10k youth by county, 2016-2020
```{r echo=FALSE,message=FALSE,warning=FALSE}
### create overall file for numerator in % calculation below
df_mi_front_end_analytic_county_adj <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         !is.na(county_id)==TRUE) %>% 
  distinct(pet_id,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode where there is county data
  group_by(county_id) %>% 
  summarize(adjudication_case_count = n_distinct(pet_id[disp_desc=="Adjudication" & age>=10 & age <17])) %>% 
  ungroup() %>% 
  left_join(df_ezapop_race_ethnicity_10_16_county_level, by = "county_id") %>% 
  mutate(adjudications_per_10k_youth = round(adjudication_case_count/overall_10_16_population*10000, digits = 1))

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- df_mi_front_end_analytic_county_adj %>%
  pull(adjudications_per_10k_youth) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels youth pop
label_adj_rate <- c("520 to 841","396 to 520","230 to 396", "17 to 230")

### create a new variable with the specified quantiles
df_mi_front_end_analytic_county_adj %<>%
  mutate(adjudication_per_10k_youth_quartile = cut(-adjudications_per_10k_youth,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_adj_rate,
                               include.lowest = T)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) 


### plot
ggplot(data = df_mi_front_end_analytic_county_adj,
            mapping = aes(x = reorder(county_anonymous, adjudications_per_10k_youth), y = adjudications_per_10k_youth, fill = adjudication_per_10k_youth_quartile)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(limits=c(min(0), 
                                           max(850))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 15, y = 650, label = "Each bar represents one county's\n adjudication rate", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = "Adjudications per 10k Youth") +
    coord_flip() +
  guides(fill = guide_legend(reverse = FALSE)) 
```

<br><br>
