---
title: "mi_tcs_county_placement_cleaning"
author: "Andrew Byrum"
date: "2/8/2022"
output: html_document
---

# {.tabset .tabset-fade .tabset-pills}
```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","tidylog","csgjcr","psych")
````

## Analysis Outline and Outstanding Questions

**Placement Counts**

* Placement/Detention count by charge category -- both by individual placement and by 'case' over time

*And if time permits:*

*	By race/ethnicity (RRI using MI population juvenile race/ethnicity data for pertinent counties)

* Length of Stay (Mean and median length of stay by charge category -- both by individual placement and by 'case' over time; also by race/ethnicity (with t-tests for statistical significance of differences in means))

**Outstanding Questions**

* How do we code technical violations? How should we account for technical violations as possible reason for post-adjudication detention in particular, given the time between adjudication and placement that we're seeing? Also, based on definition of 'case' we were provided, a new offense results in a new case -- so can we assume all violation data we have for a given case is solely non-offense technical violation data? Or not?

* Are we confident that placements deemed "detention" are in fact detention and not longer-term residential/treatment placements at facilities that have both detention and residential services? 

<br><br>

## Preliminary Cleaning

<br>

### 1. Read in Pertinent TCS Files for Placement Analysis: 'cases', 'charges', 'dispositions', and 'placements'
```{r message=FALSE,warning=FALSE}
### set sharepoint path using csgjcr::csg_sp_path function
sharepoint_tcs_data_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Raw/Courts/JIS/TCS")

### import cases
tcs_cases <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_Cases_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import charges
tcs_charges <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_Charges_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import dispositions
tcs_dispositions <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_DispositionsPerCharge_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import placements
tcs_placements <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_Placements_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import mandatory events (to explore legal status)
tcs_mandatory_events <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_MandatoryEvents_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))
```

<br><br>

### 2. De-dup/figure out primary keys for 'cases', 'charges', 'dispositions', and 'placements' and merge together


From Laura, Tanya, and Susan Svoboda:

For TCS, all data sets may be linked with CourtType, Year, TCSReportCourtJCL, CaseYear, CaseID and CaseType.

Juvenile/Name Number is available on the following data sets:
Cases – JuvenileNbr identifies the juvenile for the TCSreportCourtname.  Some of the FJ casetypes do not have a JuvenileNbr because a juvenile record is not created in adult cases.  In adult cases(in this data set only FJ), if the case had a prior juvenile record the JuvenileNbr will be populated indicated a reoffending juvenile in adult court.

Charges – no juvenile name number in data set – link to cases and use Juvenile Nbr, if needed; 1 to many charges can relate to a case.

MandatoryEvents –   NameNbr identifies the juvenile; 1 to many mandatory events will relate to a case.  Key events, legal status set, adjudication, disposition events etc.

Placements - NameNbr identifies the juvenile; 0 to many placement events will relate to a case.  Would recommend using the PCN events and not use ORD.  Courts should be using PCN events.
Financials –   PayorPatyNameNbr identifies the payor party.  This may or may not be the juvenile; 0 to many financial records will relate to a case.  Link to cases and use Juvenile Nbr, if needed.
Program Results – no juvenile name number in data set – link to cases and use Juvenile Nbr, if needed; 0 to many program results can relate to a case.
Sentencing – no juvenile name number in data set – link to cases and use Juvenile Nbr, if needed.


<br>

```{r message=FALSE,warning=FALSE}
######################################
#### cases
######################################

# de-dup cases file -- there is a very slight discrepancy in N size when de-duping by only juvenile_nbr and case_number as opposed to also including one or more of the above dates; keeping as juvenile_nbr and case_number makes most intuitive sense pending confirmation from JIS contacts (also de-duping by offense_dt as we may need this for later joins...)
tcs_cases_de_dup <- tcs_cases %>%
  filter(!is.na(juvenile_nbr)==TRUE,
         juvenile_nbr!=0, ### there are a handful of records where juvenile_nbr=0; appears to be data error as the records don't consistently share other identifying info like dates and county
         !is.na(case_number)==TRUE) %>% 
  dplyr::rename(case_id = case_number) %>%  ### there are a number of important primary keys which have different names across the files -- here case_id and case_number are the same ID (naming all 'case_id')
  distinct(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,adjudication_dt) %>% 
  mutate(year = as.numeric(year),
         case_year = as.numeric(year))

### 99% of dropped cases are due to 'caseload_action' -- multiple entries as different stages of case are entered 
```

<br><br>

```{r message=FALSE,warning=FALSE}
######################################
#### charges
######################################

# de-dup charges file -- using case_id (same as 'case_number' in tcs_cases and 'id' (which is "Unique ID for the record.")); no records dropped
# note: there are 1,288 records in the cases df that do not appear at all in the charges df; note from Laura and team: "no juvenile name number in data set – link to cases and use Juvenile Nbr, if needed; 1 to many charges can relate to a case."
# case_number identifies case and id uniquely identifies charge within case  
tcs_charges_de_dup <- tcs_charges %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(id)==TRUE) %>% 
  distinct(id,case_id,.keep_all = TRUE) %>% 
  mutate(current_charge_classification_clean = ifelse(str_starts(current_offense,"712A"),"Status",current_offense_classification),
         year = as.numeric(year),
         case_year = as.numeric(case_year)) ### recode status offense (from laura's team: "If you filter on CurrentOffense by 712A – that should give you the status offenses.")
```

<br><br>

```{r message=FALSE,warning=FALSE}
######################################
#### placements
######################################

# de-dup placements file -- using case_id (same as 'case_number' in tcs_cases and 'id' (which is "Unique ID for the record.")); no records dropped 
# looks like there are some pure dups
tcs_placements_de_dup <- tcs_placements %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(name_nbr)==TRUE,
         order_type=="PCN") %>% ### from laura and team: "Would recommend using the PCN events and not use ORD ("ordered to transport"/temporary record).  Courts should be using PCN ("placement change notice") events."
  dplyr::rename(juvenile_nbr= name_nbr) %>% ### there are a number of important primary keys which have different names across the files -- here name_nbr and juvenile_nbr are the same ID (naming all 'juvenile_nbr')
  mutate(placement_los = time_length(difftime(place_end_date, place_begin_date), unit = 'days')) %>% 
  arrange(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,place_begin_date,place_type,-placement_los) %>% ### when all primary keys align, including placement start date, we are de-duping by keeping placement with longer LOS -- so arrange by primary keys and then placement LOS in descending order
  distinct(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,place_begin_date,place_type,.keep_all = TRUE) %>% ### 54 dups dropped
 mutate(unique_placement_id = paste0(juvenile_nbr,case_id,place_begin_date,place_type,place_end_date),
         unique_case_id = paste0(juvenile_nbr,case_id,case_year,case_type),
         unique_youth_id = paste0(court_type,year,tc_sreport_court_jcl,juvenile_nbr),
         year = as.numeric(year),
         case_year = as.numeric(year)) %>% ### create unique IDs for later counts or de-dups -- at placement, case, and youth level
  ungroup()
```

<br><br>

### 3. Start Cleaning w/ Placements (this will serve as base file -- as we interested only in those for whom there is placement data)

Here are our groupings for placement type:
```{r message=FALSE,warning=FALSE}
placement_detention <- c("Calhoun County Juvenile Home","DETENTION","I-Child Vill Det (Not VC Disp)","NON-SECURE DETENTION","OTHER COUNTY DETENTION","Regional Detention Center","SECURE DETENTION")

placement_residential_non_mdhhs <- c("I-Boot Camp","I-CFY Ranch","I-Child Vill Residential","I-Child Vill Secure","I-Private Placement","Independent Placement","INSTITUTIONAL/RESIDENTIAL CARE","PRIVATE AGENCY/INSTITUTION","RESIDENTIAL PLACEMENT","CALHOUN TREATMENT CENTER","Residential Treatment Program")

placement_in_home_aftercare <- c("Aftercare/CV","Bond w/Father","Bond w/Mother","Boot Camp Aftercare","CFY Independent Living","Consent Probation/Father","Consent Probation/Mother","Consent Probation/Other","Consent Probation/Parents","Crossroads For Youth Aftercare","CUS","F01","Father","GDN","Guardian","Home of Guardian-Crt Supervsn","Home of Guardian-DHS Sprv.","Home of Guardian-FIA Supervsn","Home of Parent-Crt Supervision","Home of Parent-DHS Supervision","Home of Parent-FIA Supervision","Home of Parent-No Supervision","Home of parent CRT Supervision","Home of Relative-CRT Supervisi","HOME OF RELATIVE-CRT SUPERVSN","Home of Relative-FIA Supervisi","Home of Relative-FIA Supervsn","I-Child Vill Fam Based Reentry","I-Custodian","Intensive Probation/Father","Intensive Probation/Mother","Intensive Probation/Other","Intensive Probation/Parents","Intensive Reentry Parents","Intensive Reentry Program","Intensive Reentry/Father","Intensive Reentry/Mother","Intensive Reentry/Other","M01","Own Home (Both Parents)","Own Home/Father","Own Home/Mother","PARENTS","PLACED WITH PARENT-CRT SPRV","PLACED WITH PARENT-DHS SPRV","PLACED WITH RELATIVE-CRT SPRV","Probation/Father","Bond w/Parent", "Probation/Mother","Probation/Other","Probation/Parents","PTS","REL","Relative","Relative Placement","Unrelated Unlicensed Home","CFY Day Stud","CFY Work Ed Day St")

placement_mdhhs <- c("DEPARTMENT OF HUMAN SERVICES","DSS","Family Independence Agency","I-Department of Human Services","I-DHHS-150/Del")

placement_awol <- c("Absent without Leave","Order Take Into Custody")

placement_jail <- c("I-Oakland County Jail","Jail")

placement_foster_shelter <- c("Foster Care-Court Supervision","Foster Care-FIA Supervision","PLACED IN FOSTER CARE-DHS SPRV","PLACED IN FOSTER CARE-CRT SPRV","Shelter Home")
```

<br><br>

Create clean placement categories 
```{r message=FALSE,warning=FALSE}
tcs_placements_de_dup %<>%
  mutate(place_type_clean = 
           case_when(
             place_type_desc %in% placement_detention ~ 1,
             place_type_desc %in% placement_residential_non_mdhhs ~ 2,
             place_type_desc %in% placement_mdhhs ~ 3,
             place_type_desc %in% placement_jail ~ 4,
             place_type_desc %in% placement_awol ~ 5,
             place_type_desc %in% placement_in_home_aftercare ~ 6,
             place_type_desc %in% placement_foster_shelter ~ 7,
             TRUE ~ as.numeric(NA)),
         place_type_clean = factor(place_type_clean,
         levels = c(1,2,3,4,5,6,7),
         labels = c("Detention","Residential","MDHHS","Jail","AWOL","In Home/Aftercare","Foster Care/Shelter Home"))) %>% ### use factor function to assign labels to values
  ungroup() %>% 
  mutate(place_year = year(ymd(place_begin_date))) ### create year of placement to use instead of year that case was filed -- to align with Becky's Kalamazoo data when used and to be consistent throughout
```

<br><br>

### Join `Cases` to `Placements` to obtain adjudication date for parsing placements into pre- and post-adjudication groups (to analyze w/ most serious charge and most serious adjudicated charge, respectively)
```{r warning=FALSE, message=FALSE}
### we don't successfully join for 62 placement records out of 10,325 total (0.6%; 99.4% match rate here)
tcs_placements_cases_de_dup <- left_join(tcs_placements_de_dup,tcs_cases_de_dup,by=c("juvenile_nbr","case_id","court_type","year","tc_sreport_court_jcl","case_year","case_type"))
```

<br>

### Join `Charges` to `Placements` to analyze placements counts and LOS by most severe charge (adjudicated charge)
```{r warning=FALSE, message=FALSE}
### we don't successfully join for 885 placement records out of 10,325 total (8.5%; 91.5% match rate here) 
### we also add duplicates -- as more than one charge may link to an individual placement (we will eventually de-dup by most severe adjudicated charge associated with a placement)
### for this analysis, we need charge data so merging via inner_join to keep only records with both placement and charge data
tcs_placements_charges_de_dup <- inner_join(tcs_placements_cases_de_dup,tcs_charges_de_dup,by=c("case_id","court_type","year","tc_sreport_court_jcl","case_year","case_type")) %>% 
  mutate(adjudication_dt = ymd(adjudication_dt),
         place_begin_date = ymd(place_begin_date),
         dispo_date = mdy(dispo_date)) %>% 
  mutate(adjudication_dt = ifelse(is.na(adjudication_dt)==TRUE,dispo_date,adjudication_dt)) %>%  ### alger county appears to only use 'dispo date', not 'adjudication date'
  mutate(before_adjudication_flag = ifelse(place_begin_date<adjudication_dt,1,0),
         after_adjudication_flag = ifelse(place_begin_date>=adjudication_dt,1,0))
```

<br><br>

### Flag charges with adjudication before de-duping by placement/charge

(NOT COUNTING THE FOLLOWING AS ADJUDICATION: CHANGE VENUE/TRANSFER, CONSENT CALENDAR PLAN, CONSENT CALENDAR PROBATION, , DISMISS INCOMPETENT, DISMISSED, DISMISSED INCOMPETENT,DIVERTED, FOUND GUILTY, FOUND NOT COMPETENT, INACTIVE INCOMPETENT, NOT AUTHORIZED, NOT CHARGED, NOT FOUND W/IN PROVISION CODE, NOT GUILTY, REMAND, TRANSFER, TRADITIONAL WAIVER)
```{r message=FALSE,warning=FALSE}
charge_adjudicated <- c("ADMITTED ALLEGATIONS","DESIGNATED GRANTED","FOUND GUILTY","FOUND WITHIN PROVISION OF CODE","GUILTY","NOLO CONTENDERE")

### keep only charges with adjudication
tcs_placements_charges_de_dup %<>% 
  mutate(charge_adjudicated_flag = ifelse(charge_disposition %in% charge_adjudicated,1,0)) %>% 
  # filter(charge_disposition %in% charge_adjudicated) %>%
  mutate(original_offense = str_to_lower(original_offense),
         original_offense = str_replace_all(original_offense,"[:punct:]", ""),
         current_offense = str_to_lower(current_offense),
         current_offense = str_replace_all(current_offense,"[:punct:]", "")) ### remove all punctuation from current_offense and make all lower case -- for merge with current_offense from Emily's lookup table
```

<br><br>

### Read in PACC code lookup table that Emily created
```{r message=FALSE,warning=FALSE}
### set sharepoint path using csgjcr::csg_sp_path function
sharepoint_pacc_lookup_data_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Converted/JDW/")

### import pacc lookup -- jdw -- current offense
jdw_charge_pacc_code_lookup_current <- readr::read_csv(
  file.path(
    sharepoint_pacc_lookup_data_path, "JDWOffCodes_as_csv_abyrum.csv")) %>% 
  clean_names() %>% 
  dplyr::rename(category = category,
                offcode_combined = offcode_combined,
                off_level = off_level,
                severity = severity) %>% 
  mutate(current_offense = str_to_lower(offcode_combined),
         current_offense = str_replace_all(current_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
  distinct(current_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements

### import pacc lookup -- msp -- current offense
msp_charge_pacc_code_lookup_current <- readr::read_csv(
  file.path(
    sharepoint_pacc_lookup_data_path, "MSPOffCodes_as_csv_abyrum.csv")) %>% 
  clean_names() %>% 
  rename(offcode_combined = disposedcode,
         off_level = desposeddegreefelonymisdeme,
         category = off_cat,
         severity = severity) %>% 
  select(-disposeddescription) %>% 
  mutate(current_offense = str_to_lower(offcode_combined),
         current_offense = str_replace_all(current_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
  distinct(current_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements

### stack msp and jdw lookups
jdw_msp_charge_pacc_code_current_lookup <- rbind(jdw_charge_pacc_code_lookup_current,msp_charge_pacc_code_lookup_current) %>% 
  distinct(current_offense,.keep_all=TRUE)
```

```{r message=FALSE,warning=FALSE}
# ### import pacc lookup -- jdw -- original offense
# jdw_charge_pacc_code_lookup_original <- readr::read_csv(
#   file.path(
#     sharepoint_pacc_lookup_data_path, "JDWOffCodes_as_csv_abyrum.csv")) %>% 
#   clean_names() %>% 
#   dplyr::rename(category_original = category,
#                 offcode_combined_original = offcode_combined,
#                 off_level_original = off_level,
#                 severity_original = severity) %>% 
#   mutate(original_offense = str_to_lower(offcode_combined_original),
#          original_offense = str_replace_all(original_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
#   distinct(original_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements
# 
# ### import pacc lookup -- msp -- original offense
# msp_charge_pacc_code_lookup_original <- readr::read_csv(
#   file.path(
#     sharepoint_pacc_lookup_data_path, "MSPOffCodes_as_csv_abyrum.csv")) %>% 
#   clean_names() %>% 
#   rename(offcode_combined_original = disposedcode,
#          off_level_original = desposeddegreefelonymisdeme,
#          category_original = off_cat,
#          severity_original = severity) %>% 
#   select(-disposeddescription) %>% 
#   mutate(original_offense = str_to_lower(offcode_combined_original),
#          original_offense = str_replace_all(original_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
#   distinct(original_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements
# 
# ### stack msp and jdw lookups
# jdw_msp_charge_pacc_code_original_lookup <- rbind(jdw_charge_pacc_code_lookup_original,msp_charge_pacc_code_lookup_original) %>% 
#   distinct(original_offense,.keep_all=TRUE)
```
<br><br>

### Join jdw_charge_pacc_code_lookup to tcs_placements_charges_de_dup
```{r message=FALSE,warning=FALSE}
### no corresponding pacc lookup values for 189 records (189/13955; 1.4%) -- current offense
tcs_placements_charges_de_dup_pacc <- left_join(tcs_placements_charges_de_dup,jdw_msp_charge_pacc_code_current_lookup,by="current_offense") 

# ### NOT USING ORIGINAL OFFENSE -- 2400+ RECORDS HAVE 'PENDING' WHICH OBVIOUSLY DOESN'T MATCH AND LEAVES US WITH TOO MUCH MISSINGNESS HERE
# tcs_placements_charges_de_dup_pacc <- left_join(tcs_placements_charges_de_dup_pacc,jdw_msp_charge_pacc_code_original_lookup,by="original_offense") 
```

<br><br>

Recode several missing offenses based on Emily's notes:
```{r warning=FALSE, message=FALSE}
recode_to_status <- c("712a2d4","722755","ord code 26267")

recode_to_misd_non_person <- c("7503675","7505354a1","ord code 2649","ord code 26492","ord code 2651","ord code 2654","7527971a","9999999904","local orddisorderly")

recode_to_misd_person <- c("75081a1")

recode_to_felony_person <- c("roassault police")
```

<br>

### De-dup by `placement` and `case` -- create flag to designate the most serious charge associated with that unique `placement`/`case`
```{r warning=FALSE, message=FALSE}
# From TCS code book: Current Offense Classification - C/Civil Infraction, F/Felony, M/Misdemeanor, S/Statute, H/High Misdemeanor, O/Other, V/Civil-Other, R/Ordinance, Z/Notice for Advisories

### pre-adjudication
tcs_placements_charges_de_dup_pacc_pre_adj <- tcs_placements_charges_de_dup_pacc %>%
  filter(before_adjudication_flag==1) %>% 
  mutate(current_charge_classification_clean_numeric = case_when(
    (off_level == "F" & category == "Person") | current_offense%in%recode_to_felony_person ~ 1,
    off_level == "F" & category != "Person" ~ 2,
    (off_level == "M" & category == "Person") | current_offense%in%recode_to_misd_person ~ 3,
    (off_level == "M" & category != "Person") | current_offense%in%recode_to_misd_non_person ~ 4,
    off_level == "S" | current_offense%in%recode_to_status ~ 5,
    off_level %in% c("I","X") ~ 6,
    TRUE ~ as.numeric(NA)),
    current_charge_classification_clean_factor = factor(current_charge_classification_clean_numeric,
         levels = c(1,2,3,4,5,6),
         labels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status","Other/Unknown"))) %>% ### use factor function to assign labels to values)
  arrange(unique_placement_id,current_charge_classification_clean_numeric) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) ### now we are back to original cleaned N

### post-adjudication
tcs_placements_charges_de_dup_pacc_post_adj <- tcs_placements_charges_de_dup_pacc %>%
  filter(after_adjudication_flag==1,
         charge_adjudicated_flag==1) %>% 
  mutate(current_charge_classification_clean_numeric = case_when(
    off_level == "F" &  category == "Person" ~ 1,
    off_level == "F" &  category != "Person" ~ 2,
    off_level == "M" &  category == "Person" ~ 3,
    off_level == "M" &  category != "Person" ~ 4,
    off_level == "S" ~ 5,
    off_level %in% c("I","X") ~ 6,
    TRUE ~ as.numeric(NA)),
    current_charge_classification_clean_factor = factor(current_charge_classification_clean_numeric,
         levels = c(1,2,3,4,5,6),
         labels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status","Other/Unknown"))) %>% ### use factor function to assign labels to values)
  arrange(unique_placement_id,current_charge_classification_clean_numeric) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) ### now we are back to original cleaned N
```

<br><br>

## Preliminary Descriptives, County-level

<br>

### Visuals

```{r include=FALSE}
### set theme and font size
theme_set(theme_minimal())

### disable scientific notation for viz
options(scipen=999)

### full jj blue palette for reference -- NEED NEW PALETTE
jj_pal <- c("#00475d","#007392","#0db4e4","#9ed4ef","#d4e9f8")

new_pal_five <- c("#d6df23","#007392","#eeed90","#0db4e4","#315c15")

new_pal_six <- c("#7fc241","#d6df23","#007392","#eeed90","#0db4e4","#315c15")

new_pal_blue_two <- c("#007392","#0db4e4")

new_pal_blue_two_other <- c("#007392","#d6df23")
```

<br>

#### **Pre-Adjudication**

<br>

#### PRE-ADJUDICATION DETENTION: % of detentions for which most serious charge is a status offense

BY COUNTY FOR INTERNAL DISCUSSION (only 7 counties here; Ionia doesn't appear to have any pre-adjudication detention records and mackinac doesn't distinguish detention from residential in placement coding)
```{r echo=FALSE,message=FALSE,warning=FALSE}
### recode offense category into felony, misd, and status
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(current_charge_classification_clean_factor_grouped = case_when(
    current_charge_classification_clean_factor == "Felony, Person" | current_charge_classification_clean_factor == "Felony, Non-Person"  ~ 1,
    current_charge_classification_clean_factor == "Misdemeanor, Person" | current_charge_classification_clean_factor == "Misdemeanor, Non-Person"  ~ 2,
    current_charge_classification_clean_factor == "Status"  ~ 3,
    current_charge_classification_clean_factor == "Other/Unknown"  ~ 4,
    TRUE ~ as.numeric(NA)),
    current_charge_classification_clean_factor_grouped = factor(current_charge_classification_clean_factor_grouped,
         levels = c(1,2,3,4),
         labels = c("Felony","Misdemeanor","Status","Other/Unknown")))


tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) %>% 
  filter(current_charge_classification_clean_factor_grouped=="Status")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention,
            mapping = aes(x = reorder(county_anonymous, `Detention (%)`), y = `Detention (%)`, fill = current_charge_classification_clean_factor_grouped), group = county_anonymous) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.3))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.caption = element_text(hjust = 0.5)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Detention (%)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)


# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\tcs_detention_placement_rate_county_incl_kalamazoo.png", tcs_detention_placement_rate_county_incl_kalamazoo, width = 8, height = 6)
```

<br><br>

#### PRE-ADJUDICATION DETENTION: % of detentions for which most serious charge is a misdemeanor offense

BY COUNTY FOR INTERNAL DISCUSSION (only 7 counties here; Ionia doesn't appear to have any pre-adjudication detention records and mackinac doesn't distinguish detention from residential in placement coding)
```{r echo=FALSE,message=FALSE,warning=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) %>% 
  filter(current_charge_classification_clean_factor_grouped=="Misdemeanor")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention,
            mapping = aes(x = reorder(county_anonymous, `Detention (%)`), y = `Detention (%)`, fill = current_charge_classification_clean_factor_grouped), group = county_anonymous) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(1))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 2.25, y = .8, label = "Each bar represents the % of detentions\nfor misdemeanor offenses within one county", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.caption = element_text(hjust = 0.5)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Detention (%)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)


# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\tcs_detention_placement_rate_county_incl_kalamazoo.png", tcs_detention_placement_rate_county_incl_kalamazoo, width = 8, height = 6)
```

<br><br>

#### PRE-ADJUDICATION DETENTION: detentions by most serious charge (%)

BY COUNTY FOR INTERNAL DISCUSSION (only 7 counties here; Ionia doesn't appear to have any pre-adjudication detention records and mackinac doesn't distinguish detention from residential in placement coding)
```{r echo=FALSE,message=FALSE,warning=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) %>% 
  group_by(county.x) %>% 
  mutate(felony_percent = `Detention (%)`[current_charge_classification_clean_factor_grouped=="Felony"]) %>% 
  filter(current_charge_classification_clean_factor_grouped!="Other/Unknown")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention, aes(y = `Detention (%)`, x = reorder(county.x,-felony_percent), fill = forcats::fct_rev(current_charge_classification_clean_factor_grouped))) + 
  geom_bar(stat = "identity", color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = rev(c("#007392","#0db4e4","#9ed4ef"))) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
    geom_label(
    aes(
      y = `Detention (%)`,
      label = scales::percent(`Detention (%)`,accuracy=1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 5,
    colour = "black",
    show.legend = FALSE
  ) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = "Each bar represents one county.\n'Other/Unknown' offenses excluded (<1% of sample)",
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\Iowa Revocation Reduction\\Work Products\\Presentations\\r_viz\\supervision_status_by_district_2020.png", supervision_status_by_district_2020, width = 9, height = 6.5) 
```
<br><br>

#### **Post-Adjudication**

<br>

#### POST-ADJUDICATION DETENTION: % of detentions for which most serious charge is a status offense

BY COUNTY FOR INTERNAL DISCUSSION (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)
```{r echo=FALSE,message=FALSE,warning=FALSE}
### recode offense category into felony, misd, and status
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  mutate(current_charge_classification_clean_factor_grouped = case_when(
    current_charge_classification_clean_factor == "Felony, Person" | current_charge_classification_clean_factor == "Felony, Non-Person"  ~ 1,
    current_charge_classification_clean_factor == "Misdemeanor, Person" | current_charge_classification_clean_factor == "Misdemeanor, Non-Person"  ~ 2,
    current_charge_classification_clean_factor == "Status"  ~ 3,
    current_charge_classification_clean_factor == "Other/Unknown"  ~ 4,
    TRUE ~ as.numeric(NA)),
    current_charge_classification_clean_factor_grouped = factor(current_charge_classification_clean_factor_grouped,
         levels = c(1,2,3,4),
         labels = c("Felony","Misdemeanor","Status","Other/Unknown")))


tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) %>% 
  filter(current_charge_classification_clean_factor_grouped=="Status")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention,
            mapping = aes(x = reorder(county_anonymous, `Detention (%)`), y = `Detention (%)`, fill = current_charge_classification_clean_factor_grouped), group = county_anonymous) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.5))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 4.5, y = .35, label = "Each bar represents the % of detentions\nfor status offenses within one county", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.caption = element_text(hjust = 0.5)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Detention (%)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)


# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\tcs_detention_placement_rate_county_incl_kalamazoo.png", tcs_detention_placement_rate_county_incl_kalamazoo, width = 8, height = 6)
```

<br><br>

#### POST-ADJUDICATION DETENTION: % of detentions for which most serious charge is a misdemeanor offense

BY COUNTY FOR INTERNAL DISCUSSION (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)
```{r echo=FALSE,message=FALSE,warning=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) %>% 
  filter(current_charge_classification_clean_factor_grouped=="Misdemeanor")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention,
            mapping = aes(x = reorder(county_anonymous, `Detention (%)`), y = `Detention (%)`, fill = current_charge_classification_clean_factor_grouped), group = county_anonymous) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(1))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 1.15, y = .8, label = "Each bar represents the % of detentions\nfor misdemeanor offenses within one county", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.caption = element_text(hjust = 0.5)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Detention (%)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)


# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\tcs_detention_placement_rate_county_incl_kalamazoo.png", tcs_detention_placement_rate_county_incl_kalamazoo, width = 8, height = 6)
```

<br><br>

#### POST-ADJUDICATION DETENTION: detentions by most serious charge (%)

BY COUNTY FOR INTERNAL DISCUSSION (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)
```{r echo=FALSE,message=FALSE,warning=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) %>% 
  group_by(county.x) %>% 
  mutate(felony_percent = `Detention (%)`[current_charge_classification_clean_factor_grouped=="Felony"]) %>% 
  filter(current_charge_classification_clean_factor_grouped!="Other/Unknown")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention, aes(y = `Detention (%)`, x = reorder(county.x,-felony_percent), fill = forcats::fct_rev(current_charge_classification_clean_factor_grouped))) + 
  geom_bar(stat = "identity", color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = rev(c("#007392","#0db4e4","#9ed4ef"))) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
    geom_label(
    aes(
      y = `Detention (%)`,
      label = scales::percent(`Detention (%)`,accuracy=1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 5,
    colour = "black",
    show.legend = FALSE
  ) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = "Each bar represents one county.\n'Other/Unknown' offenses excluded (<1% of sample)",
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\Iowa Revocation Reduction\\Work Products\\Presentations\\r_viz\\supervision_status_by_district_2020.png", supervision_status_by_district_2020, width = 9, height = 6.5) 
```

<br><br>

### Tables

<br>

#### **Pre-Adjudication**

<br>

#### PRE-ADJUDICATION DETENTION: Individual Placements by Charge Classification: Counts and Percentages, 2016-2020

BY COUNTY FOR INTERNAL DISCUSSION (only 7 counties here; Ionia doesn't appear to have any pre-adjudication detention records and mackinac doesn't distinguish detention from residential in placement coding)
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = round(n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]*100, digits = 1)) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`))

### print table via kableextra
kable(tcs_placements_charges_de_dup_ind_place_grouped_pre_detention, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

#### **Post-Adjudication**

<br>

#### POST-ADJUDICATION: Individual Placements by Charge Classification: Counts and Percentages, 2016-2020

BY COUNTY FOR INTERNAL DISCUSSION (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_post_detention <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = round(n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]*100, digits = 1)) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`))

### print table via kableextra
kable(tcs_placements_charges_de_dup_ind_place_grouped_post_detention, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```


<br><br>

## Preliminary Descriptives, Overall


### PRE-ADJUDICATION DETENTION: Individual Placements by Charge Classification: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention")) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention")) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = round(n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`*100, digits = 1)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_de_dup_ind_place_grouped_pre_detention, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### POST-ADJUDICATION: Median and Mean Time between Disposition Date and Placement Start Date, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_de_dup_pacc_post_adj_disp_place_diff <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(!is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention")) %>% 
  # select(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,adjudication_dt,dispo_date,current_charge_classification_clean_factor,place_begin_date,place_end_date,place_type_clean) %>%
  mutate(dispo_date = mdy(dispo_date)) %>% 
  mutate(dispo_placement_diff = time_length(difftime(place_begin_date,dispo_date), unit = 'days')) %>% 
  filter(dispo_placement_diff>=0) ### remove negative time differences which is likely a coding error (n=1)

tcs_placements_charges_dispo_to_placement_median_lag <- tcs_placements_charges_de_dup_pacc_post_adj_disp_place_diff %>% 
  filter(case_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention")) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (Median Days)` = round(median(dispo_placement_diff[place_type_clean=="Detention"], na.rm = TRUE), digits = 0),
            `Detention (Mean Days)` = round(mean(dispo_placement_diff[place_type_clean=="Detention"], na.rm = TRUE), digits = 0),
            # `Residential (Median Days)` = round(median(dispo_placement_diff[place_type_clean=="Residential"], na.rm = TRUE), digits = 0), 
            # `Residential (Mean Days)` = round(mean(dispo_placement_diff[place_type_clean=="Residential"], na.rm = TRUE), digits = 0), 
            # 
            # `MDHHS (Median Days)` = round(median(dispo_placement_diff[place_type_clean=="MDHHS"], na.rm = TRUE), digits = 0),
            # `MDHHS (Mean Days)` = round(mean(dispo_placement_diff[place_type_clean=="MDHHS"], na.rm = TRUE), digits = 0)
            ) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_dispo_to_placement_median_lag, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

### POST-ADJUDICATION: Individual Placements by Charge Classification: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention")) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_post <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention")) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = round(n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`*100, digits = 1)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_de_dup_ind_place_grouped_post, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

```{r eval=FALSE,include=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE) %>% 
  summarise(`Sample N` = n_distinct(unique_placement_id)) 

tcs_placements_charges_off_level_missing <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(charge_disp_code,charge_disposition) %>% 
  summarise(`N` = n_distinct(unique_placement_id), 
            `%` = round(n_distinct(unique_placement_id)/tcs_placements_charges_de_dup_denom$`Sample N`*100, digits = 1)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_off_level_missing, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 


### write out

### set sharepoint path using csgjcr::csg_sp_path function
sharepoint_tcs_data_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Data Questions/TCS/Charges/")

### import cases
openxlsx::write.xlsx(tcs_placements_charges_off_level_missing,
  file.path(
    sharepoint_tcs_data_path, "tcs_placements_disp_codes.xlsx"))
  
```


### PRE-ADJUDICATION DETENTION: Individual Placements by Charge Classification and Year: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
### create detention table by charge -- this is denominator for percentages
detention_charge_over_time_table_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Detention"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `2016` = n_distinct(unique_placement_id[place_year==2016]),
            `2017` = n_distinct(unique_placement_id[place_year==2017]),
            `2018` = n_distinct(unique_placement_id[place_year==2018]),
            `2019` = n_distinct(unique_placement_id[place_year==2019]),
            `2020` = n_distinct(unique_placement_id[place_year==2020])) 

### create detention table by charge
detention_charge_over_time_table_pre <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Detention"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `All Cases (%)` = round(n_distinct(unique_placement_id)/detention_charge_over_time_table_denom$`All Cases (N)`*100,digits=1),
            `2016 (N)` = n_distinct(unique_placement_id[place_year==2016]),
            `2016 (%)` = round(n_distinct(unique_placement_id[place_year==2016])/detention_charge_over_time_table_denom$`2016`*100,digits=1),
            `2017 (N)` = n_distinct(unique_placement_id[place_year==2017]),
            `2017 (%)` = round(n_distinct(unique_placement_id[place_year==2017])/detention_charge_over_time_table_denom$`2017`*100,digits=1),
            `2018 (N)` = n_distinct(unique_placement_id[place_year==2018]),
            `2018 (%)` = round(n_distinct(unique_placement_id[place_year==2018])/detention_charge_over_time_table_denom$`2018`*100,digits=1),
            `2019 (N)` = n_distinct(unique_placement_id[place_year==2019]),
            `2019 (%)` = round(n_distinct(unique_placement_id[place_year==2019])/detention_charge_over_time_table_denom$`2019`*100,digits=1),
            `2020 (N)` = n_distinct(unique_placement_id[place_year==2020]),
            `2020 (%)` = round(n_distinct(unique_placement_id[place_year==2020])/detention_charge_over_time_table_denom$`2020`*100,digits=1)) %>% 
  ungroup() 

### print table via kableextra
kable(detention_charge_over_time_table_pre, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

### POST-ADJUDICATION DETENTION: Individual Placements by Charge Classification and Year: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
### create detention table by charge -- this is denominator for percentages
detention_charge_over_time_table_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Detention"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `2016` = n_distinct(unique_placement_id[place_year==2016]),
            `2017` = n_distinct(unique_placement_id[place_year==2017]),
            `2018` = n_distinct(unique_placement_id[place_year==2018]),
            `2019` = n_distinct(unique_placement_id[place_year==2019]),
            `2020` = n_distinct(unique_placement_id[place_year==2020])) 

### create detention table by charge
detention_charge_over_time_table_post <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Detention"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `All Cases (%)` = round(n_distinct(unique_placement_id)/detention_charge_over_time_table_denom$`All Cases (N)`*100,digits=1),
            `2016 (N)` = n_distinct(unique_placement_id[place_year==2016]),
            `2016 (%)` = round(n_distinct(unique_placement_id[place_year==2016])/detention_charge_over_time_table_denom$`2016`*100,digits=1),
            `2017 (N)` = n_distinct(unique_placement_id[place_year==2017]),
            `2017 (%)` = round(n_distinct(unique_placement_id[place_year==2017])/detention_charge_over_time_table_denom$`2017`*100,digits=1),
            `2018 (N)` = n_distinct(unique_placement_id[place_year==2018]),
            `2018 (%)` = round(n_distinct(unique_placement_id[place_year==2018])/detention_charge_over_time_table_denom$`2018`*100,digits=1),
            `2019 (N)` = n_distinct(unique_placement_id[place_year==2019]),
            `2019 (%)` = round(n_distinct(unique_placement_id[place_year==2019])/detention_charge_over_time_table_denom$`2019`*100,digits=1),
            `2020 (N)` = n_distinct(unique_placement_id[place_year==2020]),
            `2020 (%)` = round(n_distinct(unique_placement_id[place_year==2020])/detention_charge_over_time_table_denom$`2020`*100,digits=1)) %>% 
  ungroup() 

### print table via kableextra
kable(detention_charge_over_time_table_post, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### POST-ADJUDICATION Residential/MDHHS -- Individual Placements by Charge Classification and Year: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
### create Residential/MDHHS table by charge -- this is denominator for percentages
residential_mdhhs_charge_over_time_table_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Residential","MDHHS"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `2016` = n_distinct(unique_placement_id[place_year==2016]),
            `2017` = n_distinct(unique_placement_id[place_year==2017]),
            `2018` = n_distinct(unique_placement_id[place_year==2018]),
            `2019` = n_distinct(unique_placement_id[place_year==2019]),
            `2020` = n_distinct(unique_placement_id[place_year==2020])) 

### create Residential/MDHHS table by charge
residential_mdhhs_charge_over_time_table_post <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Residential","MDHHS"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `All Cases (%)` = round(n_distinct(unique_placement_id)/residential_mdhhs_charge_over_time_table_denom$`All Cases (N)`*100,digits=1),
            `2016 (N)` = n_distinct(unique_placement_id[place_year==2016]),
            `2016 (%)` = round(n_distinct(unique_placement_id[place_year==2016])/residential_mdhhs_charge_over_time_table_denom$`2016`*100,digits=1),
            `2017 (N)` = n_distinct(unique_placement_id[place_year==2017]),
            `2017 (%)` = round(n_distinct(unique_placement_id[place_year==2017])/residential_mdhhs_charge_over_time_table_denom$`2017`*100,digits=1),
            `2018 (N)` = n_distinct(unique_placement_id[place_year==2018]),
            `2018 (%)` = round(n_distinct(unique_placement_id[place_year==2018])/residential_mdhhs_charge_over_time_table_denom$`2018`*100,digits=1),
            `2019 (N)` = n_distinct(unique_placement_id[place_year==2019]),
            `2019 (%)` = round(n_distinct(unique_placement_id[place_year==2019])/residential_mdhhs_charge_over_time_table_denom$`2019`*100,digits=1),
            `2020 (N)` = n_distinct(unique_placement_id[place_year==2020]),
            `2020 (%)` = round(n_distinct(unique_placement_id[place_year==2020])/residential_mdhhs_charge_over_time_table_denom$`2020`*100,digits=1)) %>% 
  ungroup() 

### print table via kableextra
kable(residential_mdhhs_charge_over_time_table_post, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

```{r echo=FALSE,warning=FALSE, message=FALSE}
### Calculate length of stay and create LOS buckets, PRE-ADJUDICATION

### calculate length of stay in two different ways:
# los with everything counted 
# los split into placement type buckets -- making sure to recode '0' as NA so as to not bring down mean LOS when youth was never actually placed somewhere
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  group_by(unique_case_id) %>% ### group by case
  mutate(case_first_place_date = min(place_begin_date),
         case_last_place_date = max(place_end_date)) %>%
  ungroup() %>% 
  mutate(unique_placement_los = time_length(difftime(place_end_date, place_begin_date), unit = 'days'),
         los_unique_placement_detention_only = ifelse(place_type_clean=="Detention",unique_placement_los,NA),
         los_unique_placement_residential_non_mdhhs_only = ifelse(place_type_clean=="Residential",unique_placement_los,NA),
         los_unique_placement_mdhhs_only = ifelse(place_type_clean=="MDHHS",unique_placement_los,NA)) %>% 
  group_by(unique_case_id) %>% 
  mutate(los_case_overall_all_included = sum(unique_placement_los),
         los_case_overall_all_included = ifelse(los_case_overall_all_included==0,NA,los_case_overall_all_included),
         los_overall_detention_only = sum(los_unique_placement_detention_only),
         los_overall_detention_only = ifelse(los_overall_detention_only==0,NA,los_overall_detention_only),
         los_overall_residential_only = sum(los_unique_placement_residential_non_mdhhs_only),
         los_overall_residential_only = ifelse(los_overall_residential_only==0,NA,los_overall_residential_only),
         los_overall_mdhhs_only = sum(los_unique_placement_mdhhs_only),
         los_overall_mdhhs_only = ifelse(los_overall_mdhhs_only==0,NA,los_overall_mdhhs_only)) %>% 
  ungroup()

### create grouped los bins for detention
### mirror becky's approach with the kalamazoo analysis
### recode LOS_placement (1/3=1 "1-3 days") (4/7=2 "4-7 days") (8/14=3 "8-14 days") (15/30=4 "15-30 days") (31/90=5 "1-3 months") (91/max=6 ">3 months"), gen (placement_buckets)
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(los_unique_placement_detention_only_grouped_bin = case_when(
    los_unique_placement_detention_only<3 & los_unique_placement_detention_only!=0 ~ 1,
    los_unique_placement_detention_only>=3 & los_unique_placement_detention_only<7 ~ 2,
    los_unique_placement_detention_only>=7 & los_unique_placement_detention_only<15 ~ 3,
    los_unique_placement_detention_only>=15 & los_unique_placement_detention_only<=30 ~ 4,
    los_unique_placement_detention_only>=30 & los_unique_placement_detention_only<=90 ~ 5,
    los_unique_placement_detention_only>90 ~ 6,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_detention_only_grouped_bin = factor(los_unique_placement_detention_only_grouped_bin,
         levels = c(1,2,3,4,5,6),
         labels = c("1 to 3 Days", "3 to 7 Days", "7 to 14 Days","15 to 30 Days","30 to 90 Days","90 Days+"))) ### use factor function to assign labels to values

### create grouped los bins for residential placement
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(los_unique_placement_residential_only_grouped_bin = case_when(
    los_unique_placement_residential_non_mdhhs_only<32 & los_unique_placement_residential_non_mdhhs_only!=0 ~ 1,
    los_unique_placement_residential_non_mdhhs_only>=32 & los_unique_placement_residential_non_mdhhs_only<92 ~ 2,
    los_unique_placement_residential_non_mdhhs_only>=92 & los_unique_placement_residential_non_mdhhs_only<=275 ~ 3,
    los_unique_placement_residential_non_mdhhs_only>=275 & los_unique_placement_residential_non_mdhhs_only<=549 ~ 4,
    los_unique_placement_residential_non_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_residential_only_grouped_bin = factor(los_unique_placement_residential_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values

### create grouped los bins for mdhhs placement
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(los_unique_placement_mdhhs_only_grouped_bin = case_when(
    los_unique_placement_mdhhs_only<32 & los_unique_placement_mdhhs_only!=0 ~ 1,
    los_unique_placement_mdhhs_only>=32 & los_unique_placement_mdhhs_only<92 ~ 2,
    los_unique_placement_mdhhs_only>=92 & los_unique_placement_mdhhs_only<=275 ~ 3,
    los_unique_placement_mdhhs_only>=275 & los_unique_placement_mdhhs_only<=549 ~ 4,
    los_unique_placement_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_mdhhs_only_grouped_bin = factor(los_unique_placement_mdhhs_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values
```


```{r echo=FALSE,warning=FALSE, message=FALSE}
### Calculate length of stay and create LOS buckets, POST-ADJUDICATION


### calculate length of stay in two different ways:
# los with everything counted 
# los split into placement type buckets -- making sure to recode '0' as NA so as to not bring down mean LOS when youth was never actually placed somewhere
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  group_by(unique_case_id) %>% ### group by case
  mutate(case_first_place_date = min(place_begin_date),
         case_last_place_date = max(place_end_date)) %>%
  ungroup() %>% 
  mutate(unique_placement_los = time_length(difftime(place_end_date, place_begin_date), unit = 'days'),
         los_unique_placement_detention_only = ifelse(place_type_clean=="Detention",unique_placement_los,NA),
         los_unique_placement_residential_non_mdhhs_only = ifelse(place_type_clean=="Residential",unique_placement_los,NA),
         los_unique_placement_mdhhs_only = ifelse(place_type_clean=="MDHHS",unique_placement_los,NA)) %>% 
  group_by(unique_case_id) %>% 
  mutate(los_case_overall_all_included = sum(unique_placement_los),
         los_case_overall_all_included = ifelse(los_case_overall_all_included==0,NA,los_case_overall_all_included),
         los_overall_detention_only = sum(los_unique_placement_detention_only),
         los_overall_detention_only = ifelse(los_overall_detention_only==0,NA,los_overall_detention_only),
         los_overall_residential_only = sum(los_unique_placement_residential_non_mdhhs_only),
         los_overall_residential_only = ifelse(los_overall_residential_only==0,NA,los_overall_residential_only),
         los_overall_mdhhs_only = sum(los_unique_placement_mdhhs_only),
         los_overall_mdhhs_only = ifelse(los_overall_mdhhs_only==0,NA,los_overall_mdhhs_only)) %>% 
  ungroup()

### create grouped los bins for detention
### mirror becky's approach with the kalamazoo analysis
### recode LOS_placement (1/3=1 "1-3 days") (4/7=2 "4-7 days") (8/14=3 "8-14 days") (15/30=4 "15-30 days") (31/90=5 "1-3 months") (91/max=6 ">3 months"), gen (placement_buckets)
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  mutate(los_unique_placement_detention_only_grouped_bin = case_when(
    los_unique_placement_detention_only<3 & los_unique_placement_detention_only!=0 ~ 1,
    los_unique_placement_detention_only>=3 & los_unique_placement_detention_only<7 ~ 2,
    los_unique_placement_detention_only>=7 & los_unique_placement_detention_only<15 ~ 3,
    los_unique_placement_detention_only>=15 & los_unique_placement_detention_only<=30 ~ 4,
    los_unique_placement_detention_only>=30 & los_unique_placement_detention_only<=90 ~ 5,
    los_unique_placement_detention_only>90 ~ 6,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_detention_only_grouped_bin = factor(los_unique_placement_detention_only_grouped_bin,
         levels = c(1,2,3,4,5,6),
         labels = c("1 to 3 Days", "3 to 7 Days", "7 to 14 Days","15 to 30 Days","30 to 90 Days","90 Days+"))) ### use factor function to assign labels to values

### create grouped los bins for residential placement
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  mutate(los_unique_placement_residential_only_grouped_bin = case_when(
    los_unique_placement_residential_non_mdhhs_only<32 & los_unique_placement_residential_non_mdhhs_only!=0 ~ 1,
    los_unique_placement_residential_non_mdhhs_only>=32 & los_unique_placement_residential_non_mdhhs_only<92 ~ 2,
    los_unique_placement_residential_non_mdhhs_only>=92 & los_unique_placement_residential_non_mdhhs_only<=275 ~ 3,
    los_unique_placement_residential_non_mdhhs_only>=275 & los_unique_placement_residential_non_mdhhs_only<=549 ~ 4,
    los_unique_placement_residential_non_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_residential_only_grouped_bin = factor(los_unique_placement_residential_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values

### create grouped los bins for mdhhs placement
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  mutate(los_unique_placement_mdhhs_only_grouped_bin = case_when(
    los_unique_placement_mdhhs_only<32 & los_unique_placement_mdhhs_only!=0 ~ 1,
    los_unique_placement_mdhhs_only>=32 & los_unique_placement_mdhhs_only<92 ~ 2,
    los_unique_placement_mdhhs_only>=92 & los_unique_placement_mdhhs_only<=275 ~ 3,
    los_unique_placement_mdhhs_only>=275 & los_unique_placement_mdhhs_only<=549 ~ 4,
    los_unique_placement_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_mdhhs_only_grouped_bin = factor(los_unique_placement_mdhhs_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values
```

### PRE-ADJUDICATION Median LOS by Charge -- Detention, 2016-2018 (individual placements)
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_median_los_detention_pre <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(case_year%in%c(2016,2017,2018),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean=="Detention") %>% ### only looking at earlier years because we don't want to artificially deflate the median
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (Sample N)` = n_distinct(unique_placement_id[!is.na(los_unique_placement_detention_only)==TRUE & los_unique_placement_detention_only>-1]),
            `Detention (Days)` = round(median(los_unique_placement_detention_only[los_unique_placement_detention_only>-1], na.rm = TRUE), digits = 0)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_median_los_detention_pre, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

### POST-ADJUDICATION Median LOS by Charge -- Detention, Residential, and Treatment, 2016-2018 (individual placements)
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_median_los_all_post <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(case_year%in%c(2016,2017,2018),
         !is.na(current_charge_classification_clean_factor)==TRUE) %>% ### only looking at earlier years because we don't want to artificially deflate the median
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (Sample N)` = n_distinct(unique_placement_id[!is.na(los_unique_placement_detention_only)==TRUE & los_unique_placement_detention_only>-1]),
            `Detention (Days)` = round(median(los_unique_placement_detention_only[los_unique_placement_detention_only>-1], na.rm = TRUE), digits = 0), 
            `Residential (Sample N)` = n_distinct(unique_placement_id[!is.na(los_unique_placement_residential_non_mdhhs_only)==TRUE]),
            `Residential (Days)` = round(median(los_unique_placement_residential_non_mdhhs_only, na.rm = TRUE), digits = 0), 
            `MDHHS (Sample N)` = n_distinct(unique_placement_id[!is.na(los_unique_placement_mdhhs_only)==TRUE]),
            `MDHHS (Days)` = round(median(los_unique_placement_mdhhs_only, na.rm = TRUE), digits = 0)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_median_los_all_post, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
### CCI
cci_los_overall_denom <- jj_assessments_placement_legal_status_clean_has_cci_mdhhs %>% 
    filter(placement_episode_start_year %in% c(2016,2017),
         !is.na(los_overall_all_included_grouped_bin)==TRUE,
         first_place_type_cci_mdhhs=="Child Caring Institution") %>% 
  summarise(n_count = n_distinct(placement_unique_id))

cci_los_overall_grouped <- jj_assessments_placement_legal_status_clean_has_cci_mdhhs %>% 
    filter(placement_episode_start_year %in% c(2016,2017),
         !is.na(los_overall_all_included_grouped_bin),
         first_place_type_cci_mdhhs=="Child Caring Institution") %>% 
    group_by(los_overall_all_included_grouped_bin) %>% 
  summarise(n_count = round(n_distinct(placement_unique_id)/(cci_los_overall_denom$n_count), digits = 2))

## use gather for line plot
cci_los_overall_table <- cci_los_overall_grouped %>%
  gather(year, value, `n_count`) %>% 
  dplyr::rename(los_bins = los_overall_all_included_grouped_bin) %>% 
  mutate(facility = 'CCI')

### MDHHS
mdhhs_los_overall_denom <- jj_assessments_placement_legal_status_clean_has_cci_mdhhs %>% 
    filter(placement_episode_start_year %in% c(2016,2017),
         !is.na(los_overall_all_included_grouped_bin)==TRUE,
         first_place_type_cci_mdhhs=="MDHHS Training School") %>% 
  summarise(n_count = n_distinct(placement_unique_id))

mdhhs_los_overall_grouped <- jj_assessments_placement_legal_status_clean_has_cci_mdhhs %>% 
    filter(placement_episode_start_year %in% c(2016,2017),
         !is.na(los_overall_all_included_grouped_bin),
         first_place_type_cci_mdhhs=="MDHHS Training School") %>% 
    group_by(los_overall_all_included_grouped_bin) %>% 
  summarise(n_count = round(n_distinct(placement_unique_id)/(mdhhs_los_overall_denom$n_count), digits = 2))

## use gather for line plot
mdhhs_los_overall_table <- mdhhs_los_overall_grouped %>%
  gather(year, value, `n_count`) %>% 
  dplyr::rename(los_bins = los_overall_all_included_grouped_bin) %>% 
  mutate(facility = 'MDHHS')


mdhhs_los_overall_table_missing_row <- tribble(
  ~`los_bins`,   ~`year`, ~`value`,    ~`facility`,                 
  "Less than 1 Month", "n_count",as.numeric(0.00), "MDHHS") 

## combine
combined_los_overall_table_detention_only <- rbind(cci_los_overall_table,mdhhs_los_overall_table,mdhhs_los_overall_table_missing_row) 
  
mdhhs_cci_mdhhs_los_bins_2016_2017 <- ggplot(data = combined_los_overall_table_detention_only,
            mapping = aes(x = los_bins, y = value, fill = forcats::fct_rev(los_bins))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = rev(c("#d6df23","#007392","#eeed90","#0db4e4","#315c15"))) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
                                           max(.65))) +
  scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
    theme(axis.text.x = element_text(size = 10, face="bold"),
       axis.ticks.length = unit(0, "cm"),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11,
                              margin=margin(r=10))) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
    facet_grid(forcats::fct_rev(facility) ~ ., scales="free_y", space="free_y", switch="y") +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = scales::percent(as.numeric(value), accuracy = 1), group = forcats::fct_rev(los_bins)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.1,
                  box.padding = 0.1,
                  fill = "white",
                  color = "gray40",
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

mdhhs_cci_mdhhs_los_bins_2016_2017

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_cci_mdhhs_los_bins_2016_2017.png", mdhhs_cci_mdhhs_los_bins_2016_2017, width = 8, height = 6)
```

```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
### data tables to write out: tcs_placements_charges_de_dup_ind_place_grouped_pre_detention,tcs_placements_charges_dispo_to_placement_median_lag,tcs_placements_charges_de_dup_ind_place_grouped_post,detention_charge_over_time_table_pre,detention_charge_over_time_table_post,residential_mdhhs_charge_over_time_table_post,tcs_placements_charges_median_los_detention_pre,tcs_placements_charges_median_los_all_post

C:\Users\abyrum\The Council of State Governments\JC Research - Documents\JC Research - JJ_Michigan - JJ_Michigan\Work Products\Court Data\TCS\Charge Analysis

### write out all tables to excel 
library(xlsx)
write.xlsx(dataframe1, file="C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\Court Data\\TCS\\Charge Analysis\\tcs_placement_charge_analysis_2_24_2022.xlsx", sheetName="sheet1", row.names=FALSE)
write.xlsx(dataframe2, file="filename.xlsx", sheetName="sheet2", append=TRUE, row.names=FALSE)
```

<br><br>

## Basic Sample Descriptives, Charge Data

<br>

#### Charge N's: Unique Placements by Placement/Facility Type, cases filed 2016-2020 

Note: Charges in this table are individual charges, not grouped by individual or case. These are not yet linked to placements -- this is simply the universe of charges in the TCS data. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
# From TCS code book: Current Offense Classification - C/Civil Infraction, F/Felony, M/Misdemeanor, S/Statute, H/High Misdemeanor, O/Other, V/Civil-Other, R/Ordinance, Z/Notice for Advisories
tcs_charges_de_dup %<>%
  mutate(current_offense_classification_clean = case_when(
    current_offense_classification %in% c("C","V") ~ 1,
    current_offense_classification == "F" ~ 2,
    current_offense_classification == "M" ~ 3,
    current_offense_classification == "S" ~ 4,
    current_offense_classification == "H" ~ 5,
    current_offense_classification == "R" ~ 6,
    current_offense_classification == "Z" ~ 7,
    current_offense_classification == "O" ~ 8,
    TRUE ~ as.numeric(NA)),
    current_offense_classification_clean = factor(current_offense_classification_clean,
         levels = c(1,2,3,4,5,6,7,8),
         labels = c("Civil","Felony", "Misdemeanor","Statute","High Misdemeanor","Ordinance","Notice for Advisories","Other"))) %>% ### use factor function to assign labels to values)
  mutate(unique_charge_id = paste0(id,case_id))

### create overall placement count denominator for % in cross-tabs
unique_charge_id_n <- n_distinct(tcs_charges_de_dup$unique_charge_id[!is.na(tcs_charges_de_dup$current_offense_classification_clean)==TRUE])

### all -- grouped by placement type
tcs_charge_type <- tcs_charges_de_dup %>% 
  distinct(unique_charge_id,.keep_all = TRUE) %>% 
  filter(!is.na(current_offense_classification_clean)==TRUE,
         case_year%in%c(2016,2017,2018,2019,2020)) %>% 
  group_by(current_offense_classification_clean) %>% 
  summarise(`Unique Count (N)` = n_distinct(unique_charge_id),
            `Percent of Total (%)` = round(n_distinct(unique_charge_id)/unique_charge_id_n*100, digits = 2)) %>% 
  dplyr::rename(`Charge Classification` = current_offense_classification_clean) %>% 
  mutate(`Charge Classification` = as.character(`Charge Classification`))

### all -- overall
tcs_charge_type_overall <- tcs_charges_de_dup %>% 
  distinct(unique_charge_id,.keep_all = TRUE) %>% 
  filter(!is.na(current_offense_classification_clean)==TRUE,
         case_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Unique Count (N)` = n_distinct(unique_charge_id),
            `Percent of Total (%)` = round(n_distinct(unique_charge_id)/unique_charge_id_n*100, digits = 2)) %>% 
  dplyr::mutate(`Charge Classification` = "Overall") 

### combine tables for kable
tcs_charge_type_table <- rbind(tcs_charge_type,tcs_charge_type_overall)

### print table via kableextra
kable(tcs_charge_type_table, format.args = list(big.mark = ","), align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Codebook

<br>

#### Charges
```{r echo=FALSE,message=FALSE,warning=FALSE}
### import variable labels from 'CSG_TCS_DataDictionary FINAL'
charges_labels <- readxl::read_xlsx(file.path(
    sharepoint_tcs_data_path, "CSG_TCS_DataDictionary FINAL.xlsx"),
  .name_repair = make_clean_names,
  sheet ="Charges", range = "B2:C106") %>% 
  mutate(data_column = make_clean_names(data_column))

### get descriptive statistics and select those of interest
charges_descriptives <- tcs_charges_de_dup %>% 
  describe(.,
           check = FALSE) %>% 
  mutate(data_column = row.names(.)) %>% 
  as_tibble() %>% 
  select(data_column,"n","min","max","mean") %>% 
  mutate(data_column = stringr::str_replace(data_column,"\\*",""))

### add stats to label 
charges_codebook <- left_join(charges_descriptives,charges_labels,by="data_column") %>% 
  select(data_column,tcs_definition=definition,everything())

### print table via kableextra
kable(charges_codebook, format.args = list(big.mark = ","), align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                row_label_position = "l") 
```

<br><br>

#### Placements
```{r echo=FALSE,message=FALSE,warning=FALSE}
### import variable labels from 'CSG_TCS_DataDictionary FINAL'
placements_labels <- readxl::read_xlsx(file.path(
    sharepoint_tcs_data_path, "CSG_TCS_DataDictionary FINAL.xlsx"),
  .name_repair = make_clean_names,
  sheet ="Placements", range = "B2:C52") %>% 
  mutate(data_column = make_clean_names(data_column))

### get descriptive statistics and select those of interest
placements_descriptives <- tcs_placements_de_dup %>% 
  describe(.,
           check = FALSE) %>% 
  mutate(data_column = row.names(.)) %>% 
  as_tibble() %>% 
  select(data_column,"n","min","max","mean") %>% 
  mutate(data_column = stringr::str_replace(data_column,"\\*",""))

### add stats to label 
placements_codebook <- left_join(placements_descriptives,placements_labels,by="data_column") %>% 
  select(data_column,tcs_definition=definition,everything())

### print table via kableextra
kable(placements_codebook, format.args = list(big.mark = ","), align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                row_label_position = "l") 
```

<br><br>

## TCS Placement Data Diagram 

Below is a data diagram outlining the pertinent TCS data files we have received and processed -- noting the primary keys in each to de-duplicate as well as the columns used to join the relational data together. Only entire file is displayed for placements because of size constraints (too many columns, too little room)

<br>

```{r echo=FALSE, out.width = '100%'}
knitr::include_graphics("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\Courts\\JIS\\TCS\\Data Mapping\\michigan_tcs_placement_data_mapping_charges.png")
```

<br><br>

## Questions out to SCAO

*Preliminary Decisions to Confirm*

•	Our goal is to analyze the TCS placement data by charge type, specifically the most serious charge for which a youth is adjudicated per case:

Currently we are joining the charges data file to the placement data file by merging on the following fields based on your previous advice: ‘CourtType’, ‘Year’, ‘TCSReportCourtJCL’, ‘CaseYear’, ‘CaseID’, and ‘CaseType’

We are selecting the most serious charge for which a youth is adjudicated per case using the ‘current_offense_classification’ field – and selecting the most serious classification within a single case

*Questions*

•	What is the difference between ‘current offense’ and ‘original offense’?

•	It appears as though the charges data file is unique by the field, ‘ID’, along with ‘CaseID’. Is this a unique identifier of each charge? The data dictionary notes that this field is the "Unique ID for the record"

•	What is the best way to determine if a youth was or was not adjudicated for a particular charge? The fields, ‘charge_disposition’ and ‘charge_disp_code’ appear to indicate this. Is that correct? And if so, is there a codebook available for ‘charge_disp_code’ to help us determine if a youth was adjudicated or not for a given charge?

Here are the codes I am seeing in the data: AAL, CCP, CHV, DGT, DINC, DIS, DIV, DVT, FNC, FPC, GTD, GTY, INA, INAC, INAR, NAP, NCH, NFPC, NGTY, NOC, PLG, RMD, TRS, TTC, TWAV

<br><br>
