---
title: "mdhhs_placement_viz"
author: "Andrew Byrum"
date: "2/11/2022"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: true
---

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","tidylog","csgjcr","psych","ragg")
````

```{r include=FALSE}
### set sharepoint path using csgjcr::csg_sp_path function
sharepoint_mdhhs_data_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Raw/MDHHS/Placements/Analytic Files")

### read in cleaned mdhhs file
jj_assessments_placement_legal_status_clean <- readr::read_rds(
  file.path(sharepoint_mdhhs_data_path, "jj_mdhhs_placements_analytic_file_to_viz.rds")) 
```

#### Example for Josh to edit example visual w/ legend:

```{r eval=FALSE,echo=FALSE, warning=FALSE, message=FALSE}
### CCI and MDHHS Length of Stay, Distribution within Placement Episodes (LOS added together within episode; e.g. total detention LOS for one placement episode may add the LOS for several unique detention placements), 2015-2018

### Filters: Placement episodes with only in home and/or detention/jail placements are excluded (placement_episode_does_count==1), use only first placement within an episode since we are plotting los calculated at the episode-level (placement_episode_no==1), exclude cases where bins are NA, and only looking at 2015-2018

### CCI denominator for percent calculation
cci_los_overall_denom <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_cci_only_grouped_bin)==TRUE) %>% 
  summarise(n_count = n_distinct(placement_unique_id))

### CCI LOS distribution percent
cci_los_overall_grouped <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_cci_only_grouped_bin)) %>% 
    group_by(los_overall_cci_only_grouped_bin) %>% 
  summarise(percent = round(n_distinct(placement_unique_id)/(cci_los_overall_denom$n_count), digits = 2)) %>% 
  mutate(facility = 'CCI') %>% ### label facility for merge with mdhhs calculation
  rename(los_bins = los_overall_cci_only_grouped_bin)

### MDHHS denominator for percent calculation
mdhhs_los_overall_denom <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_mdhhs_only_grouped_bin)==TRUE) %>% 
  summarise(n_count = n_distinct(placement_unique_id))

### MDHHS LOS distribution percent
mdhhs_los_overall_grouped <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_mdhhs_only_grouped_bin)) %>% 
    group_by(los_overall_mdhhs_only_grouped_bin) %>% 
  summarise(percent = round(n_distinct(placement_unique_id)/(mdhhs_los_overall_denom$n_count), digits = 2)) %>% 
  mutate(facility = 'MDHHS') %>% ### label facility for merge with cci calculation
  rename(los_bins = los_overall_mdhhs_only_grouped_bin)

## combine cci and mdhhs and set facility as factor to order them
combined_los_overall_mdhhs_cci_only <- rbind(cci_los_overall_grouped,mdhhs_los_overall_grouped) %>% 
  filter(facility %in% c("MDHHS","CCI")) %>% 
  mutate(facility = factor(facility,
         levels = c("MDHHS", "CCI")))

### plot
ggplot(data = combined_los_overall_mdhhs_cci_only,
            mapping = aes(x = facility, 
                          y = percent, 
                          fill = forcats::fct_rev(los_bins))) + 
  geom_bar(position = "dodge", 
           stat = "identity") +
  scale_fill_manual(values = rev(c("#d6df23","#007392","#eeed90","#0db4e4","#315c15"))) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                     limits=c(min(0), 
                                           max(.65))) +
  scale_x_discrete(labels = scales::wrap_format(18),
                   limits = rev) +
    theme(strip.text.x = element_text(face = "bold"),
          legend.position = "top",
          axis.text.y = element_text(face = "bold", 
                                     hjust = 1, 
                                     size = 12)) +
    labs(y = NULL, 
         x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = guide_legend(reverse = TRUE)) + 
  geom_label_repel(aes(label = scales::percent(as.numeric(percent), 
                                               accuracy = 1), 
                       group = forcats::fct_rev(los_bins)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.1,
                  box.padding = 0.1,
                  fill = "white",
                  color = "gray40",
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)
```

```{r include=FALSE}
### set theme and font size
theme_set(theme_minimal(20, base_family = "Calibri"))

### disable scientific notation for viz
options(scipen=999)

### palette options for reference
jj_pal_old <- c("#00475d","#007392","#0db4e4","#9ed4ef","#d4e9f8")

new_pal_five <- c("#d6df23","#007392","#eeed90","#0db4e4","#315c15")

new_pal_six <- c("#7fc241","#d6df23","#007392","#eeed90","#0db4e4","#315c15")

new_pal_blue_two <- c("#007392","#0db4e4")

new_pal_blue_two_other <- c("#007392","#d6df23")
```

```{r eval=FALSE, include=FALSE, warning=FALSE, message=FALSE}
### Slide 12, state ward placement disposition risk assessments (with missingness plotted), 2016-2020

### total unique placement episodes (year is year that placement episode starts; many placements in 2015-2020 started prior to 2015)
jj_placement_episode_count_disp_risk_placement_table <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_does_count==1,
         !is.na(disposition_risk_level_earliest_use)==TRUE,
         place_no_of_earliest_cci_mdhhs == placement_episode_no,
         !is.na(living_arrangement_grouped_out_of_home_only)==TRUE,
         placement_begin_date_year%in%c(2016,2017,2018,2019,2020),
         legal_status_ward_flag == "State Ward") %>% 
  group_by(living_arrangement_grouped_out_of_home_only) %>% 
  summarize(`Overall (N)` = n_distinct(placement_unique_id),
            `Overall (N), Non-Missing` = n_distinct(placement_unique_id[disposition_risk_level_earliest_use!="Missing"]),
            `Low` = n_distinct(placement_unique_id[disposition_risk_level_earliest_use=="Low"])/n_distinct(placement_unique_id[disposition_risk_level_earliest_use!="Missing"]), 
            `Moderate` =  n_distinct(placement_unique_id[disposition_risk_level_earliest_use=="Moderate"])/n_distinct(placement_unique_id[disposition_risk_level_earliest_use!="Missing"]), 
            `High` = n_distinct(placement_unique_id[disposition_risk_level_earliest_use=="High"])/n_distinct(placement_unique_id[disposition_risk_level_earliest_use!="Missing"]),
`Missing` = n_distinct(placement_unique_id[disposition_risk_level_earliest_use=="Missing"])/`Overall (N)`) %>% 
  ungroup() %>% 
  dplyr::select(-`Overall (N)`)

## use gather for plotting -- pivot from wide to long
jj_placement_episode_count_disp_risk_placement_table_plot <- jj_placement_episode_count_disp_risk_placement_table %>%
  gather(risk_level, value, `Overall (N), Non-Missing`:`Missing`) %>% 
    mutate(risk_level = factor(risk_level,
                                levels = c("Low","Moderate","High","Missing"))) %>% 
  group_by(living_arrangement_grouped_out_of_home_only) %>% 
  mutate(`Overall (N), Non-Missing` = as.numeric(value[is.na(risk_level)==TRUE])) %>% 
  ungroup() %>% 
  mutate(living_arrangement_grouped_out_of_home_only = ifelse(living_arrangement_grouped_out_of_home_only=="CCI","CCI Facility", "MDHHS Facility")) %>% 
  filter(!is.na(risk_level)==TRUE) %>% 
  mutate(living_arrangement_n = paste0(
      "<span style = 'font-size:16pt'>", living_arrangement_grouped_out_of_home_only, "</span><br><br>",
      "<span style = 'font-size:12pt'><em>", "N: ", `Overall (N), Non-Missing`,"</span><br>",
      "<span style = 'font-size:10pt'><em>","(Non-Missing)", "</em></span>"),
      ) 

### plot
ggplot(data = jj_placement_episode_count_disp_risk_placement_table_plot,
            mapping = aes(x = living_arrangement_n, 
                          y = value, 
                          fill = forcats::fct_rev(risk_level))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = c("gray70","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(label=scales::percent_format(accuracy = 1),
                     limits=c(min(0), max(.75))) +
  scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        axis.text.y = element_markdown()) + 
    labs(y = NULL, x = NULL,
      caption = "% for Low, Moderate, High risk reflects the % of first CCI/MDHHS placements which are non-missing in each risk category.\n% missingness indicates the % of all first CCI/MDHHS placements that have missing disposition risk assessment data.\nAs a result the percentages for low, moderate, and high will add up to 100% and should be considered\nseparately from the % missing.",
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = guide_legend(reverse = TRUE)) + 
  geom_label_repel(aes(label = scales::percent(value, accuracy = .1), group = forcats::fct_rev(risk_level)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.3,
                   box.padding = 0.15,
                  fill = "white",
                  color = c("#9ed4ef","#9ed4ef","#0db4e4","#0db4e4","#007392","#007392","gray70","gray70"),
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE) 
  

# ### print table via kableextra
# kable(jj_placement_episode_count_disp_risk_placement_table, format.args = list(big.mark = ","), align=rep('c')) %>%
#    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") %>% 
#   add_footnote("% for Low, Moderate, High risk reflects the % of first CCI/MDHHS placements which are non-missing in each risk category. % missingness indicates the % of all first CCI/MDHHS placements that have missing disposition risk assessment data. As a result the percentages for low, moderate, and high will add up to 100% and should be considered separately from the % missing row", notation = "none")
```

<br><br>

### Slide 12, state ward placement disposition risk assessments, 2016-2020
```{r echo=FALSE, warning=FALSE, message=FALSE}
### total unique placement episodes (year is year that placement episode starts; many placements in 2015-2020 started prior to 2015)
jj_placement_episode_count_disp_risk_placement_table <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_does_count==1,
         !is.na(disposition_risk_level_earliest_use)==TRUE,
         place_no_of_earliest_cci_mdhhs == placement_episode_no,
         !is.na(living_arrangement_grouped_out_of_home_only)==TRUE,
         placement_begin_date_year%in%c(2016,2017,2018,2019,2020),
         legal_status_ward_flag == "State Ward") %>% 
  group_by(living_arrangement_grouped_out_of_home_only) %>% 
  summarize(`Overall (N)` = n_distinct(placement_unique_id),
            `Overall (N), Missing` = n_distinct(placement_unique_id[disposition_risk_level_earliest_use=="Missing"]),
            `Low` = n_distinct(placement_unique_id[disposition_risk_level_earliest_use=="Low"])/n_distinct(placement_unique_id[disposition_risk_level_earliest_use!="Missing"]), 
            `Moderate` =  n_distinct(placement_unique_id[disposition_risk_level_earliest_use=="Moderate"])/n_distinct(placement_unique_id[disposition_risk_level_earliest_use!="Missing"]), 
            `High` = n_distinct(placement_unique_id[disposition_risk_level_earliest_use=="High"])/n_distinct(placement_unique_id[disposition_risk_level_earliest_use!="Missing"]),
`Missing` = n_distinct(placement_unique_id[disposition_risk_level_earliest_use=="Missing"])/`Overall (N)`) %>% 
  ungroup() %>% 
  dplyr::select(-`Overall (N)`)

## use gather for plotting -- pivot from wide to long
jj_placement_episode_count_disp_risk_placement_table_plot <- jj_placement_episode_count_disp_risk_placement_table %>%
  gather(risk_level, value, `Overall (N), Missing`:`Missing`) %>% 
    mutate(risk_level = factor(risk_level,
                                levels = c("Low","Moderate","High","Missing"))) %>% 
  group_by(living_arrangement_grouped_out_of_home_only) %>% 
  mutate(`Overall (N), Missing` = as.numeric(value[is.na(risk_level)==TRUE]),
         `Placement Episodes Missing Assessments` = scales::percent(mean(as.numeric(value[risk_level=="Missing"]), na.rm = TRUE), 
                                                            accuracy = 1)) %>% 
  ungroup() %>% 
  mutate(living_arrangement_grouped_out_of_home_only = ifelse(living_arrangement_grouped_out_of_home_only=="CCI","CCI", "MDHHS")) %>% 
  filter(!is.na(risk_level)==TRUE,
         risk_level!="Missing") %>% 
  mutate(living_arrangement_n = paste0(
      "<span style = 'font-size:16pt'>", living_arrangement_grouped_out_of_home_only, "</span><br><br>",
      "<span style = 'font-size:12pt'><em>", "No Assessment Data:","</span><br>",
      "<span style = 'font-size:10pt'><em>", "N: ",`Overall (N), Missing`," (",`Placement Episodes Missing Assessments`,")", "</em></span>")
      ) 

### plot
mdhhs_disp_risk_placement <- ggplot(data = jj_placement_episode_count_disp_risk_placement_table_plot,
            mapping = aes(x = forcats::fct_rev(risk_level), 
                          y = value, 
                          fill = forcats::fct_rev(risk_level))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = c("#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(label=scales::percent_format(accuracy = 1),
                     limits=c(min(0), max(.7))) +
  # scale_x_discrete(limits = rev) +
 theme(axis.text.x = element_text(size = 10, face="bold"),
       axis.ticks.length = unit(0, "cm"),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11,
                              margin=margin(r=10))) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
    facet_grid(living_arrangement_grouped_out_of_home_only ~ ., scales="free_y", space="free_y", switch="y") +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = scales::percent(value, accuracy = .1), group = forcats::fct_rev(risk_level)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.3,
                   box.padding = 0.15,
                  fill = "white",
                  color = c("gray40"),
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE) 
  
mdhhs_disp_risk_placement

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_disp_risk_placement.png", mdhhs_disp_risk_placement, width = 8, height = 6)
```

<br><br>

### Slide 13, Placements episodes per 10k youth by county (state and dual wards included in rate), 2015-2020
```{r echo=FALSE,message=FALSE,warning=FALSE}
### import ezapop race/ethnicity data for 10-17 y/o michigan residents for rate calculation
df_ezapop_race_ethnicity_10_17_county_level <- readr::read_delim("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Ezapop\\ezapop_10_17_race_eth_sex_mi.txt", delim = "|") %>% 
  mutate(county_name =  gsub(" County", "", county_name)) %>% 
  dplyr::select(county_name,overall_10_17_population)

### create overall file for denominator in % calculation below
jj_placement_episode_county <- jj_assessments_placement_legal_status_clean %>% 
  filter(!is.na(county_name)==TRUE,
         placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020),
         placement_episode_does_count==1) %>% 
  distinct(person_id,placement_episode_segment,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode where there is county data
  group_by(county_name,placement_episode_start_year) %>% 
  summarize(placement_episode_count = n_distinct(placement_episode_unique_id)) %>% 
  ungroup() %>% 
  group_by(county_name) %>%
  summarize(placement_episode_mean = mean(placement_episode_count,na.rm=TRUE)) %>%
  ungroup() %>%
  left_join(df_ezapop_race_ethnicity_10_17_county_level, by = "county_name") %>% 
  mutate(placements_per_10k_youth = round(placement_episode_mean/overall_10_17_population*10000, digits = 1))

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- jj_placement_episode_county %>%
  pull(placements_per_10k_youth) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels youth pop
label_place_rate <- c("12 to 37","6 to 12","2 to 6", "Less than 2")

### create a new variable with the specified quantiles
jj_placement_episode_county %<>%
  mutate(placements_per_10k_youth_quartile = cut(-placements_per_10k_youth,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_place_rate,
                               include.lowest = T)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) 


### plot
mdhhs_placement_episode_rate_county <- ggplot(data = jj_placement_episode_county,
            mapping = aes(x = reorder(county_anonymous, placements_per_10k_youth), y = placements_per_10k_youth, fill = placements_per_10k_youth_quartile)) + 
  geom_bar(stat = "identity", color="white",size=0.15) +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(limits=c(min(0), 
                                           max(40))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 55, y = 30, label = "Each bar represents one county's\n placement episode rate", colour = "#00475d", size = 4.5) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.caption = element_text(hjust = 0.5)) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = "Placement Episodes\nper 10k Youth") +
    coord_flip() +
  guides(fill = guide_legend(reverse = FALSE)) 

mdhhs_placement_episode_rate_county

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_placement_episode_rate_county.png", mdhhs_placement_episode_rate_county, width = 8, height = 6)
```

<br><br>


```{r eval=FALSE,echo=FALSE,message=FALSE,warning=FALSE}
### Other option for slide 13, Unique placements episodes per 10k youth by county (state wards only), 2015-2020

### import ezapop race/ethnicity data for 10-17 y/o michigan residents for rate calculation
df_ezapop_race_ethnicity_10_17_county_level <- readr::read_delim("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Ezapop\\ezapop_10_17_race_eth_sex_mi.txt", delim = "|") %>% 
  mutate(county_name =  gsub(" County", "", county_name)) %>% 
  dplyr::select(county_name,overall_10_17_population)

### create overall file for denominator in % calculation below
jj_placement_episode_county <- jj_assessments_placement_legal_status_clean %>% 
  filter(!is.na(county_name)==TRUE,
         legal_status_ward_flag == "State Ward") %>% 
  distinct(person_id,placement_episode_segment,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode where there is county data
  group_by(county_name) %>% 
  summarize(placement_episode_count = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020) & placement_episode_does_count==1])) %>% 
  ungroup() %>% 
  left_join(df_ezapop_race_ethnicity_10_17_county_level, by = "county_name") %>% 
  mutate(placements_per_10k_youth = round(placement_episode_count/overall_10_17_population*10000, digits = 1))

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- jj_placement_episode_county %>%
  pull(placements_per_10k_youth) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels youth pop
label_place_rate <- c("42 to 206","19 to 42","6 to 19", "0 to 6")

### create a new variable with the specified quantiles
jj_placement_episode_county %<>%
  mutate(placements_per_10k_youth_quartile = cut(-placements_per_10k_youth,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_place_rate,
                               include.lowest = T)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) 


### plot
ggplot(data = jj_placement_episode_county,
            mapping = aes(x = reorder(county_anonymous, placements_per_10k_youth), y = placements_per_10k_youth, fill = placements_per_10k_youth_quartile)) + 
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(limits=c(min(0), 
                                           max(225))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 55, y = 150, label = "Each bar represents one county's\n placement episode rate", colour = "#00475d", size = 5) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = "Placements per 10k Youth") +
    coord_flip() +
  guides(fill = guide_legend(reverse = FALSE)) 
```


```{r include=FALSE, warning=FALSE, message=FALSE}
# ### Slide 19, Detention, CCI, and MDHHS Length of Stay, Distribution within Placement Episodes (LOS added together within episode; e.g. total detention LOS for one placement episode may add the LOS for several unique detention placements), 2015-2018
# 
# Note: Placement episodes with only in home and/or detention/jail placements are excluded 
# 
# ### create grouped los bins
# jj_assessments_placement_legal_status_clean %<>%
#   # group_by(placement_episode_unique_id) %>% 
#   # mutate(los_overall_cci_only_grouped = sum(los_overall_cci_only, na.rm = TRUE)) %>% 
#   # ungroup() %>% 
#   mutate(los_overall_cci_only_grouped_bin = case_when(
#     los_overall_cci_only<32 & los_overall_cci_only!=0 ~ 1,
#     los_overall_cci_only>=32 & los_overall_cci_only<91 ~ 2,
#     los_overall_cci_only>=91 & los_overall_cci_only<181 ~ 3,
#     los_overall_cci_only>=181 & los_overall_cci_only<=365 ~ 4, 
#     los_overall_cci_only>=365 & los_overall_cci_only<=730 ~ 5, 
#     los_overall_cci_only>730 ~ 6, 
#     TRUE ~ as.numeric(NA)),
#     los_overall_cci_only_grouped_bin = factor(los_overall_cci_only_grouped_bin,
#          levels = c(1,2,3,4,5,6),
#          labels = c("Less than 1 Month", "1 to 3 Months", "3 to 6 Months","6 to 12 Months","12 to 24 Months","24 Months+"))) ### use factor function to assign labels to values
# 
# jj_assessments_placement_legal_status_clean %<>%
#   # group_by(placement_episode_unique_id) %>% 
#   # mutate(los_overall_mdhhs_only_grouped = sum(los_overall_mdhhs_only, na.rm = TRUE)) %>% 
#   # ungroup() %>% 
#   mutate(los_overall_mdhhs_only_grouped_bin = case_when(
#     los_overall_mdhhs_only<32 & los_overall_mdhhs_only!=0 ~ 1,
#     los_overall_mdhhs_only>=32 & los_overall_mdhhs_only<91 ~ 2,
#     los_overall_mdhhs_only>=91 & los_overall_mdhhs_only<181 ~ 3,
#     los_overall_mdhhs_only>=181 & los_overall_mdhhs_only<=365 ~ 4, 
#     los_overall_mdhhs_only>=365 & los_overall_mdhhs_only<=730 ~ 5, 
#     los_overall_mdhhs_only>730 ~ 6, 
#     TRUE ~ as.numeric(NA)),
#     los_overall_mdhhs_only_grouped_bin = factor(los_overall_mdhhs_only_grouped_bin,
#          levels = c(1,2,3,4,5,6),
#          labels = c("Less than 1 Month", "1 to 3 Months", "3 to 6 Months","6 to 12 Months","12 to 24 Months","24 Months+"))) ### use factor function to assign labels to values
# 
# jj_assessments_placement_legal_status_clean %<>%
#   # group_by(placement_episode_unique_id) %>% 
#   # mutate(los_overall_detention_only_grouped = sum(los_overall_detention_only, na.rm = TRUE)) %>% 
#   # ungroup() %>% 
#   mutate(los_overall_detention_only_grouped_bin = case_when(
#     los_overall_detention_only<32 & los_overall_detention_only!=0 ~ 1,
#     los_overall_detention_only>=32 & los_overall_detention_only<91 ~ 2,
#     los_overall_detention_only>=91 & los_overall_detention_only<181 ~ 3,
#     los_overall_detention_only>=181 & los_overall_detention_only<=365 ~ 4, 
#     los_overall_detention_only>=365 & los_overall_detention_only<=730 ~ 5, 
#     los_overall_detention_only>730 ~ 6, 
#     TRUE ~ as.numeric(NA)),
#     los_overall_detention_only_grouped_bin = factor(los_overall_detention_only_grouped_bin,
#          levels = c(1,2,3,4,5,6),
#          labels = c("Less than 1 Month", "1 to 3 Months", "3 to 6 Months","6 to 12 Months","12 to 24 Months","24 Months+"))) ### use factor function to assign labels to values
# 
# ### CCI
# cci_los_overall_denom <- jj_assessments_placement_legal_status_clean %>% 
#     filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
#          placement_episode_does_count==1,
#          placement_episode_no==1,
#          !is.na(los_overall_cci_only_grouped_bin)==TRUE) %>% 
#   summarise(n_count = n_distinct(placement_unique_id))
# 
# cci_los_overall_grouped <- jj_assessments_placement_legal_status_clean %>% 
#     filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
#          placement_episode_does_count==1,
#          placement_episode_no==1,
#          !is.na(los_overall_cci_only_grouped_bin)) %>% 
#     group_by(los_overall_cci_only_grouped_bin) %>% 
#   summarise(n_count = round(n_distinct(placement_unique_id)/(cci_los_overall_denom$n_count), digits = 2))
# 
# ## use gather for line plot
# cci_los_overall_table <- cci_los_overall_grouped %>%
#   gather(year, value, `n_count`) %>% 
#   dplyr::rename(los_bins = los_overall_cci_only_grouped_bin) %>% 
#   mutate(facility = 'CCI')
# 
# ### MDHHS
# mdhhs_los_overall_denom <- jj_assessments_placement_legal_status_clean %>% 
#     filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
#          placement_episode_does_count==1,
#          placement_episode_no==1,
#          !is.na(los_overall_mdhhs_only_grouped_bin)==TRUE) %>% 
#   summarise(n_count = n_distinct(placement_unique_id))
# 
# mdhhs_los_overall_grouped <- jj_assessments_placement_legal_status_clean %>% 
#     filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
#          placement_episode_does_count==1,
#          placement_episode_no==1,
#          !is.na(los_overall_mdhhs_only_grouped_bin)) %>% 
#     group_by(los_overall_mdhhs_only_grouped_bin) %>% 
#   summarise(n_count = round(n_distinct(placement_unique_id)/(mdhhs_los_overall_denom$n_count), digits = 2))
# 
# ## use gather for line plot
# mdhhs_los_overall_table <- mdhhs_los_overall_grouped %>%
#   gather(year, value, `n_count`) %>% 
#   dplyr::rename(los_bins = los_overall_mdhhs_only_grouped_bin) %>% 
#   mutate(facility = 'MDHHS')
# 
# ### Detention
# detention_los_overall_denom <- jj_assessments_placement_legal_status_clean %>% 
#     filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
#          placement_episode_does_count==1,
#          placement_episode_no==1,
#          !is.na(los_overall_detention_only_grouped_bin)==TRUE) %>% 
#   summarise(n_count = n_distinct(placement_unique_id))
# 
# detention_los_overall_grouped <- jj_assessments_placement_legal_status_clean %>% 
#     filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
#          placement_episode_does_count==1,
#          placement_episode_no==1,
#          !is.na(los_overall_detention_only_grouped_bin)) %>% 
#     group_by(los_overall_detention_only_grouped_bin) %>% 
#   summarise(n_count = round(n_distinct(placement_unique_id)/(detention_los_overall_denom$n_count), digits = 2))
# 
# ## use gather for line plot
# detention_los_overall_table <- detention_los_overall_grouped %>%
#   gather(year, value, `n_count`) %>% 
#   dplyr::rename(los_bins = los_overall_detention_only_grouped_bin) %>% 
#   mutate(facility = 'Detention')
# 
# mdhhs_los_overall_table_missing_row <- tribble(
#   ~`los_bins`,   ~`year`, ~`value`,    ~`facility`,                 
#   "Less than 1 Month", "n_count",as.numeric(0.00), "MDHHS") 
# 
# ## combine
# combined_los_overall_table <- rbind(cci_los_overall_table,mdhhs_los_overall_table,detention_los_overall_table,mdhhs_los_overall_table_missing_row) %>% 
#   mutate(facility = factor(facility,
#          levels = c("Detention","MDHHS", "CCI")))
#   
# ggplot(data = combined_los_overall_table,
#             mapping = aes(x = los_bins, y = value, fill = forcats::fct_rev(facility))) + 
#   geom_bar(position = "dodge", stat = "identity") +
#   scale_fill_manual(values = c("#007392","#0db4e4","#9ed4ef")) +
#   scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
#                                            max(.7))) +
#   scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
#     theme(strip.text.x = element_text(face = "bold"),
#           legend.position = "top",) +
#     labs(y = NULL, x = NULL,
#       caption = NULL,
#       title = NULL,
#       subtitle = NULL,
#       fill = NULL) +
#     coord_flip() +
#   guides(fill = guide_legend(reverse = TRUE)) + 
#   geom_label_repel(aes(label = scales::percent(as.numeric(value), accuracy = 1), group = forcats::fct_rev(facility)),
#                   position = position_dodge(width = .9),
#                   direction = 'x',
#                   hjust = 0.75,
#                   label.padding = 0.05,
#                   box.padding = 0.05,
#                   fill = "white",
#                   color = c("#007392","#007392","#007392","#007392","#007392","#007392",
#                             "#0db4e4","#0db4e4","#0db4e4","#0db4e4","#0db4e4","#9ed4ef",
#                             "#9ed4ef","#9ed4ef","#9ed4ef","#9ed4ef","#9ed4ef","#0db4e4"),
#                   segment.color = NA,
#                   fontface = "bold",
#                   na.rm = TRUE,
#                   show.legend = FALSE)

```

<br><br>

### Slide 19, Detention

Detention Length of Stay, Distribution within Placement Episodes (LOS added together within episode; e.g. total detention LOS for one placement episode may add the LOS for several unique detention placements), 2015-2018

Note: Placement episodes with only in home and/or detention/jail placements are excluded 
```{r echo=FALSE, warning=FALSE, message=FALSE}
### create grouped new los bins -- only five categories for this visual
jj_assessments_placement_legal_status_clean %<>%
  # group_by(placement_episode_unique_id) %>% 
  # mutate(los_overall_cci_only_grouped = sum(los_overall_cci_only, na.rm = TRUE)) %>% 
  # ungroup() %>% 
 mutate(los_overall_cci_only_grouped_bin = case_when(
    los_overall_cci_only<32 & los_overall_cci_only!=0 ~ 1,
    los_overall_cci_only>=32 & los_overall_cci_only<92 ~ 2,
    los_overall_cci_only>=92 & los_overall_cci_only<=275 ~ 3,
    los_overall_cci_only>=275 & los_overall_cci_only<=549 ~ 4,
    los_overall_cci_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_overall_cci_only_grouped_bin = factor(los_overall_cci_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values

jj_assessments_placement_legal_status_clean %<>%
  # group_by(placement_episode_unique_id) %>% 
  # mutate(los_overall_mdhhs_only_grouped = sum(los_overall_mdhhs_only, na.rm = TRUE)) %>% 
  # ungroup() %>% 
 mutate(los_overall_mdhhs_only_grouped_bin = case_when(
    los_overall_mdhhs_only<32 & los_overall_mdhhs_only!=0 ~ 1,
    los_overall_mdhhs_only>=32 & los_overall_mdhhs_only<92 ~ 2,
    los_overall_mdhhs_only>=92 & los_overall_mdhhs_only<=275 ~ 3,
    los_overall_mdhhs_only>=275 & los_overall_mdhhs_only<=549 ~ 4,
    los_overall_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_overall_mdhhs_only_grouped_bin = factor(los_overall_mdhhs_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values

jj_assessments_placement_legal_status_clean %<>%
  # group_by(placement_episode_unique_id) %>% 
  # mutate(los_overall_detention_only_grouped = sum(los_overall_detention_only, na.rm = TRUE)) %>% 
  # ungroup() %>% 
mutate(los_overall_detention_only_grouped_bin = case_when(
    los_overall_detention_only<3 & los_overall_detention_only!=0 ~ 1,
    los_overall_detention_only>=3 & los_overall_detention_only<7 ~ 2,
    los_overall_detention_only>=7 & los_overall_detention_only<15 ~ 3,
    los_overall_detention_only>=15 & los_overall_detention_only<=30 ~ 4,
    los_overall_detention_only>=30 & los_overall_detention_only<=90 ~ 5,
    los_overall_detention_only>90 ~ 6,
    TRUE ~ as.numeric(NA)),
    los_overall_detention_only_grouped_bin = factor(los_overall_detention_only_grouped_bin,
         levels = c(1,2,3,4,5,6),
         labels = c("1 to 3 Days", "3 to 7 Days", "7 to 14 Days","15 to 30 Days","30 to 90 Days","90 Days+"))) ### use factor function to assign labels to values

### CCI
cci_los_overall_denom <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_cci_only_grouped_bin)==TRUE) %>% 
  summarise(n_count = n_distinct(placement_unique_id))

cci_los_overall_grouped <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_cci_only_grouped_bin)) %>% 
    group_by(los_overall_cci_only_grouped_bin) %>% 
  summarise(n_count = round(n_distinct(placement_unique_id)/(cci_los_overall_denom$n_count), digits = 2))

## use gather for line plot
cci_los_overall_table <- cci_los_overall_grouped %>%
  gather(year, value, `n_count`) %>% 
  dplyr::rename(los_bins = los_overall_cci_only_grouped_bin) %>% 
  mutate(facility = 'CCI')

### MDHHS
mdhhs_los_overall_denom <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_mdhhs_only_grouped_bin)==TRUE) %>% 
  summarise(n_count = n_distinct(placement_unique_id))

mdhhs_los_overall_grouped <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_mdhhs_only_grouped_bin)) %>% 
    group_by(los_overall_mdhhs_only_grouped_bin) %>% 
  summarise(n_count = round(n_distinct(placement_unique_id)/(mdhhs_los_overall_denom$n_count), digits = 2))

## use gather for line plot
mdhhs_los_overall_table <- mdhhs_los_overall_grouped %>%
  gather(year, value, `n_count`) %>% 
  dplyr::rename(los_bins = los_overall_mdhhs_only_grouped_bin) %>% 
  mutate(facility = 'MDHHS')

### Detention
detention_los_overall_denom <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_detention_only_grouped_bin)==TRUE) %>% 
  summarise(n_count = n_distinct(placement_unique_id))

detention_los_overall_grouped <- jj_assessments_placement_legal_status_clean %>% 
    filter(placement_episode_start_year %in% c(2015,2016,2017,2018),
         placement_episode_does_count==1,
         placement_episode_no==1,
         !is.na(los_overall_detention_only_grouped_bin)) %>% 
    group_by(los_overall_detention_only_grouped_bin) %>% 
  summarise(n_count = round(n_distinct(placement_unique_id)/(detention_los_overall_denom$n_count), digits = 2))

## use gather for line plot
detention_los_overall_table <- detention_los_overall_grouped %>%
  gather(year, value, `n_count`) %>% 
  dplyr::rename(los_bins = los_overall_detention_only_grouped_bin) %>% 
  mutate(facility = 'Detention')

mdhhs_los_overall_table_missing_row <- tribble(
  ~`los_bins`,   ~`year`, ~`value`,    ~`facility`,                 
  "Less than 1 Month", "n_count",as.numeric(0.00), "MDHHS") 

## combine
combined_los_overall_table_detention_only <- rbind(cci_los_overall_table,mdhhs_los_overall_table,detention_los_overall_table,mdhhs_los_overall_table_missing_row) %>% 
  filter(facility=="Detention")
  
mdhhs_detention_los_bins <- ggplot(data = combined_los_overall_table_detention_only,
            mapping = aes(x = los_bins, y = value, fill = forcats::fct_rev(los_bins))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = rev(c("#7fc241","#d6df23","#007392","#eeed90","#0db4e4","#315c15"))) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
                                           max(.55))) +
  scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
    theme(strip.text.x = element_text(face = "bold"),
          legend.position = "top",
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = scales::percent(as.numeric(value), accuracy = 1), group = forcats::fct_rev(los_bins)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.1,
                  box.padding = 0.1,
                  fill = "white",
                  color = "gray40",
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

mdhhs_detention_los_bins

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_detention_los_bins.png", mdhhs_detention_los_bins, width = 8, height = 6)
```

<br><br>

### Formerly slide 19, now slide 30ish?, CCI and MDHHS LOS Distribution

CCI and MDHHS Length of Stay, Distribution within Placement Episodes (LOS added together within episode; e.g. total detention LOS for one placement episode may add the LOS for several unique detention placements), 2015-2018

Note: Placement episodes with only in home and/or detention/jail placements are excluded 
```{r echo=FALSE, warning=FALSE, message=FALSE}
jj_assessments_placement_legal_status_clean_has_cci_mdhhs <- jj_assessments_placement_legal_status_clean %>%
  filter(!is.na(place_no_of_earliest_cci_mdhhs)==TRUE,
         place_no_of_earliest_cci_mdhhs==placement_episode_no) %>% 
  mutate(first_place_type_cci_mdhhs = living_arrangement)


# ### create grouped new los bins -- only five categories for this visual
# jj_assessments_placement_legal_status_clean %<>%
#   # group_by(placement_episode_unique_id) %>% 
#   # mutate(los_overall_cci_only_grouped = sum(los_overall_cci_only, na.rm = TRUE)) %>% 
#   # ungroup() %>% 
#  mutate(los_overall_cci_only_grouped_bin = case_when(
#     los_overall_cci_only<32 & los_overall_cci_only!=0 ~ 1,
#     los_overall_cci_only>=32 & los_overall_cci_only<92 ~ 2,
#     los_overall_cci_only>=92 & los_overall_cci_only<=275 ~ 3,
#     los_overall_cci_only>=275 & los_overall_cci_only<=549 ~ 4,
#     los_overall_cci_only>549 ~ 5,
#     TRUE ~ as.numeric(NA)),
#     los_overall_cci_only_grouped_bin = factor(los_overall_cci_only_grouped_bin,
#          levels = c(1,2,3,4,5),
#          labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values
# 
# jj_assessments_placement_legal_status_clean %<>%
#   # group_by(placement_episode_unique_id) %>% 
#   # mutate(los_overall_mdhhs_only_grouped = sum(los_overall_mdhhs_only, na.rm = TRUE)) %>% 
#   # ungroup() %>% 
#  mutate(los_overall_mdhhs_only_grouped_bin = case_when(
#     los_overall_mdhhs_only<32 & los_overall_mdhhs_only!=0 ~ 1,
#     los_overall_mdhhs_only>=32 & los_overall_mdhhs_only<92 ~ 2,
#     los_overall_mdhhs_only>=92 & los_overall_mdhhs_only<=275 ~ 3,
#     los_overall_mdhhs_only>=275 & los_overall_mdhhs_only<=549 ~ 4,
#     los_overall_mdhhs_only>549 ~ 5,
#     TRUE ~ as.numeric(NA)),
#     los_overall_mdhhs_only_grouped_bin = factor(los_overall_mdhhs_only_grouped_bin,
#          levels = c(1,2,3,4,5),
#          labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values

# jj_assessments_placement_legal_status_clean_has_cci_mdhhs %<>%
#   # group_by(placement_episode_unique_id) %>% 
#   # mutate(los_overall_detention_only_grouped = sum(los_overall_detention_only, na.rm = TRUE)) %>% 
#   # ungroup() %>% 
# mutate(los_overall_detention_only_grouped_bin = case_when(
#     los_overall_detention_only<3 & los_overall_detention_only!=0 ~ 1,
#     los_overall_detention_only>=3 & los_overall_detention_only<7 ~ 2,
#     los_overall_detention_only>=7 & los_overall_detention_only<15 ~ 3,
#     los_overall_detention_only>=15 & los_overall_detention_only<=30 ~ 4,
#     los_overall_detention_only>=30 & los_overall_detention_only<=90 ~ 5,
#     los_overall_detention_only>90 ~ 6,
#     TRUE ~ as.numeric(NA)),
#     los_overall_detention_only_grouped_bin = factor(los_overall_detention_only_grouped_bin,
#          levels = c(1,2,3,4,5,6),
#          labels = c("1 to 3 Days", "3 to 7 Days", "7 to 14 Days","15 to 30 Days","30 to 90 Days","90 Days+"))) ### use factor function to assign labels to values

jj_assessments_placement_legal_status_clean_has_cci_mdhhs %<>%
  # group_by(placement_episode_unique_id) %>% 
  # mutate(los_overall_mdhhs_only_grouped = sum(los_overall_mdhhs_only, na.rm = TRUE)) %>% 
  # ungroup() %>% 
 mutate(los_overall_all_included_grouped_bin = case_when(
    los_overall_all_included<32 & los_overall_all_included!=0 ~ 1,
    los_overall_all_included>=32 & los_overall_all_included<92 ~ 2,
    los_overall_all_included>=92 & los_overall_all_included<=275 ~ 3,
    los_overall_all_included>=275 & los_overall_all_included<=549 ~ 4,
    los_overall_all_included>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_overall_all_included_grouped_bin = factor(los_overall_all_included_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to



### CCI
cci_los_overall_denom <- jj_assessments_placement_legal_status_clean_has_cci_mdhhs %>% 
    filter(placement_episode_start_year %in% c(2016,2017),
         !is.na(los_overall_all_included_grouped_bin)==TRUE,
         first_place_type_cci_mdhhs=="Child Caring Institution") %>% 
  summarise(n_count = n_distinct(placement_unique_id))

cci_los_overall_grouped <- jj_assessments_placement_legal_status_clean_has_cci_mdhhs %>% 
    filter(placement_episode_start_year %in% c(2016,2017),
         !is.na(los_overall_all_included_grouped_bin),
         first_place_type_cci_mdhhs=="Child Caring Institution") %>% 
    group_by(los_overall_all_included_grouped_bin) %>% 
  summarise(n_count = round(n_distinct(placement_unique_id)/(cci_los_overall_denom$n_count), digits = 2))

## use gather for line plot
cci_los_overall_table <- cci_los_overall_grouped %>%
  gather(year, value, `n_count`) %>% 
  dplyr::rename(los_bins = los_overall_all_included_grouped_bin) %>% 
  mutate(facility = 'CCI')

### MDHHS
mdhhs_los_overall_denom <- jj_assessments_placement_legal_status_clean_has_cci_mdhhs %>% 
    filter(placement_episode_start_year %in% c(2016,2017),
         !is.na(los_overall_all_included_grouped_bin)==TRUE,
         first_place_type_cci_mdhhs=="MDHHS Training School") %>% 
  summarise(n_count = n_distinct(placement_unique_id))

mdhhs_los_overall_grouped <- jj_assessments_placement_legal_status_clean_has_cci_mdhhs %>% 
    filter(placement_episode_start_year %in% c(2016,2017),
         !is.na(los_overall_all_included_grouped_bin),
         first_place_type_cci_mdhhs=="MDHHS Training School") %>% 
    group_by(los_overall_all_included_grouped_bin) %>% 
  summarise(n_count = round(n_distinct(placement_unique_id)/(mdhhs_los_overall_denom$n_count), digits = 2))

## use gather for line plot
mdhhs_los_overall_table <- mdhhs_los_overall_grouped %>%
  gather(year, value, `n_count`) %>% 
  dplyr::rename(los_bins = los_overall_all_included_grouped_bin) %>% 
  mutate(facility = 'MDHHS')


mdhhs_los_overall_table_missing_row <- tribble(
  ~`los_bins`,   ~`year`, ~`value`,    ~`facility`,                 
  "Less than 1 Month", "n_count",as.numeric(0.00), "MDHHS") 

## combine
combined_los_overall_table_detention_only <- rbind(cci_los_overall_table,mdhhs_los_overall_table,mdhhs_los_overall_table_missing_row) 
  
mdhhs_cci_mdhhs_los_bins_2016_2017 <- ggplot(data = combined_los_overall_table_detention_only,
            mapping = aes(x = los_bins, y = value, fill = forcats::fct_rev(los_bins))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = rev(c("#d6df23","#007392","#eeed90","#0db4e4","#315c15"))) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
                                           max(.65))) +
  scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
    theme(axis.text.x = element_text(size = 10, face="bold"),
       axis.ticks.length = unit(0, "cm"),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11,
                              margin=margin(r=10))) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
    facet_grid(forcats::fct_rev(facility) ~ ., scales="free_y", space="free_y", switch="y") +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = scales::percent(as.numeric(value), accuracy = 1), group = forcats::fct_rev(los_bins)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.1,
                  box.padding = 0.1,
                  fill = "white",
                  color = "gray40",
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

mdhhs_cci_mdhhs_los_bins_2016_2017

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_cci_mdhhs_los_bins_2016_2017.png", mdhhs_cci_mdhhs_los_bins_2016_2017, width = 8, height = 6)
```

<br><br>

### Slide 30, Median LOS -- MDHHS and CCI (total time within placement episode), 2015-2018
```{r echo=FALSE, warning=FALSE, message=FALSE}
jj_los_placement_episode_median <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_no==1,
         placement_episode_start_year%in%c(2015,2016,2017,2018),
         placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
  summarize(`Median Length of Stay, CCI Out-of-Home (Sample N)` = n_distinct(placement_episode_unique_id[!is.na(los_overall_cci_only)==TRUE]), 
            `Median Length of Stay, CCI Out-of-Home (Days)` = round(median(los_overall_cci_only, na.rm = TRUE), digits = 0),
            `Median Length of Stay, MDHHS Out-of-Home (Sample N)` = n_distinct(placement_episode_unique_id[!is.na(los_overall_mdhhs_only)==TRUE]),
            `Median Length of Stay, MDHHS Out-of-Home (Days)` = round(median(los_overall_mdhhs_only, na.rm = TRUE), digits = 0)) 

### use gather for plotting
jj_los_placement_episode_median %<>%
  gather(facility_type_measure, median, c(`Median Length of Stay, CCI Out-of-Home (Days)`,`Median Length of Stay, MDHHS Out-of-Home (Days)`)) %>% 
  mutate(facilty_type = ifelse(facility_type_measure=="Median Length of Stay, CCI Out-of-Home (Days)", "CCI Facility","MDHHS Facility"),
         sample_n = ifelse(facilty_type=="MDHHS Facility",`Median Length of Stay, MDHHS Out-of-Home (Sample N)`,`Median Length of Stay, CCI Out-of-Home (Sample N)`)) %>% 
  mutate(facilty_type_n = paste0(
      "<span style = 'font-size:16pt'>", facilty_type, "</span><br><br>",
      "<span style = 'font-size:12pt'><em>", "Placement Episodes (N): ", sample_n,"</em></span>"))

    #      %>%
    # mutate(rri_measure = factor(rri_measure,
    #                             levels = c("Unique Youth Placed, RRI (to white youth)","Unique Youth Placed, State Ward, RRI (to white youth)","Unique Youth Placed, Dual Ward, RRI (to white youth)")))

### plot
mdhhs_cci_mdhhs_los_median <- ggplot(data = jj_los_placement_episode_median,
            mapping = aes(x = facilty_type, y = median, fill = facilty_type_n)) +
  geom_bar(stat = "identity") +
    scale_fill_manual(values = c("#007392","#007392")) +
    scale_y_continuous(limits=c(min(0), max(500))) +
    scale_x_discrete(labels = scales::wrap_format(15), limits = rev) +
    theme(strip.text.x = element_text(face = "bold"),
          axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL) +
    coord_flip() +
  guides(color = guide_legend(reverse = TRUE), fill = FALSE) + 
  geom_label_repel(aes(label = paste0(median," Days")),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                   box.padding = 0.25,
                  fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

mdhhs_cci_mdhhs_los_median

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_cci_mdhhs_los_median.png", mdhhs_cci_mdhhs_los_median, width = 8, height = 6)
```

<br><br>

### Slide 30, State Ward/Dual Ward Breakdown, Placement Episodes Starting 2015-2020
```{r echo=FALSE, warning=FALSE, message=FALSE}
### total unique placement episodes (year is year that placement episode starts; many placements in 2015-2018 started prior to 2015) 

### create denominator for percentage grouped by legal_status
jj_assessments_placement_legal_status_clean_legal_status_denom <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_no==1,
         !is.na(legal_status_ward_flag)==TRUE,
         placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
  distinct(person_id,placement_episode_segment,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
  summarize(sample_n = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)]))

jj_placement_episode_count_legal_status <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_no==1,
         !is.na(legal_status_ward_flag)==TRUE,
         placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
  distinct(person_id,placement_episode_segment,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
  group_by(legal_status_ward_flag) %>% 
  summarize(sample_n = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)]),
            sample_percent = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)])/jj_assessments_placement_legal_status_clean_legal_status_denom$sample_n) %>% 
    dplyr::rename(legal_status = legal_status_ward_flag) 

### plot
mdhhs_state_ward_dual_ward_breakdown <- ggplot(data = jj_placement_episode_count_legal_status,
            mapping = aes(x = legal_status, y = sample_percent, fill = legal_status)) +
  geom_bar(stat = "identity") +
    scale_fill_manual(values = c("#007392","#007392")) +
    scale_y_continuous(label=scales::percent_format(accuracy = 1),
                       limits=c(min(0), 
                                max(1))) +
    scale_x_discrete(labels = scales::wrap_format(15), limits = rev) +
    theme(strip.text.x = element_text(face = "bold"),
          axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL) +
    coord_flip() +
  guides(color = guide_legend(reverse = TRUE), fill = FALSE) + 
  geom_label_repel(aes(label = scales::percent(sample_percent, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                   box.padding = 0.25,
                  fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

mdhhs_state_ward_dual_ward_breakdown

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_state_ward_dual_ward_breakdown.png", mdhhs_state_ward_dual_ward_breakdown, width = 8, height = 6)
```

<br><br>

### Slide 31, Distribution of placement episodes within a unique episode (dual wards only), 2015-2018
```{r echo=FALSE, warning=FALSE, message=FALSE}
### total unique placement episodes (year is year that placement episode starts; many placements in 2015-2020 started prior to 2015)
jj_legal_status_placements_per_episode_overall <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_no==1,
         placement_episode_ends_past_study==0,
         placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
  distinct(person_id,placement_episode_segment,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
   summarize(`State Ward (N)` = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018) & legal_status_ward_flag=="State Ward"]),
            `State Ward (%)` = round(n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018) & legal_status_ward_flag=="State Ward"])/`State Ward (N)`*100, digits = 1),
            `Dual Ward (N)` = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018) & legal_status_ward_flag=="Dual Ward"]),
            `Dual Ward (%)` = round(n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018) & legal_status_ward_flag=="Dual Ward"])/`Dual Ward (N)`*100, digits = 1)) %>% 
    dplyr::mutate(`Placements per Episode` = "Overall") 

### total unique placement episodes (year is year that placement episode starts; many placements in 2015-2020 started prior to 2015)
jj_legal_status_placements_per_episode <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_no==1,
         placement_episode_ends_past_study==0,
         placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
  distinct(person_id,placement_episode_segment, .keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
  group_by(placements_within_episode_bin) %>% 
   summarize(`State Ward` = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018) & legal_status_ward_flag=="State Ward"])/jj_legal_status_placements_per_episode_overall$`State Ward (N)`,
            `Dual Ward` = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018) & legal_status_ward_flag=="Dual Ward"])/jj_legal_status_placements_per_episode_overall$`Dual Ward (N)`) 

### create sample_n and sample_percent for dual and state wards -- for subtext under axis labels in visual
### total unique placement episodes (year is year that placement episode starts; many placements in 2015-2018 started prior to 2015) 

### create denominator for percentage grouped by legal_status
jj_assessments_placement_legal_status_clean_legal_status_denom <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_no==1,
         !is.na(legal_status_ward_flag)==TRUE,
         placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
  distinct(person_id,placement_episode_segment,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
  summarize(sample_n = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018)]))

jj_placement_episode_count_legal_status <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_no==1,
         !is.na(legal_status_ward_flag)==TRUE,
         placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
  distinct(person_id,placement_episode_segment,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
  group_by(legal_status_ward_flag) %>% 
  summarize(sample_n = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018)]),
            sample_percent = round(n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018)])/jj_assessments_placement_legal_status_clean_legal_status_denom$sample_n*100, digits = 1)) %>% 
    dplyr::rename(legal_status = legal_status_ward_flag) 

### use gather for plotting
jj_legal_status_placements_per_episode_dual_ward_only <- jj_legal_status_placements_per_episode %>%
  gather(legal_status, percent, c(`State Ward`,`Dual Ward`)) %>%
  left_join(jj_placement_episode_count_legal_status, by = "legal_status") %>% 
    mutate(legal_status_n = paste0(
      "<span style = 'font-size:16pt'>", legal_status, "</span><br><br>",
      "<span style = 'font-size:12pt'><em>", "Placement Episodes:", "</span><br>",
      "<span style = 'font-size:12pt'><em>","N: ",sample_n,"; ", sample_percent, "%","</em></span>")) %>% 
  filter(legal_status=="Dual Ward")

### plot
mdhhs_dual_ward_place_per_episode <- ggplot(data = jj_legal_status_placements_per_episode_dual_ward_only, aes(y = percent, x = placements_within_episode_bin, fill = forcats::fct_rev(placements_within_episode_bin))) + 
  geom_bar(stat = "identity", color = "gray80") +
  scale_x_discrete() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
  coord_flip() +
  geom_label_repel(aes(label = scales::percent(percent, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                   box.padding = 0.25,
                  fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

mdhhs_dual_ward_place_per_episode

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_dual_ward_place_per_episode.png", mdhhs_dual_ward_place_per_episode, width = 8, height = 6)
```

<br><br>

```{r eval=FALSE,echo=FALSE, warning=FALSE, message=FALSE}
### Formerly slide 31, Distribution of placement episodes within a unique episode (dual wards only), 2015-2018 -- OPTION 2

### plot
ggplot(data = jj_legal_status_placements_per_episode_dual_ward_only, aes(y = percent, x = legal_status, fill = forcats::fct_rev(placements_within_episode_bin))) + 
  geom_bar(stat = "identity", color = "gray80") +
  scale_x_discrete() +
  scale_y_continuous(labels = scales::percent) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,accuracy=.1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 4.5,
    fill = "white",
    colour = "black",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = rev(c("#00475d","#007392","#0db4e4","#9ed4ef","#d4e9f8"))) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
  labs(x = NULL, y = NULL,
       fill = "Individual Placements per Episode",
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        # axis.text.y = element_text(face = "bold", hjust = 1, size = 15),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  coord_flip()
```

<br><br>

### Formerly slide 31, Distribution of placement episodes within a unique episode (state wards only), 2015-2018 
```{r echo=FALSE, warning=FALSE, message=FALSE}
### use gather for plotting
jj_legal_status_placements_per_episode_state_ward_only <- jj_legal_status_placements_per_episode %>%
  gather(legal_status, percent, c(`State Ward`,`Dual Ward`)) %>%
  left_join(jj_placement_episode_count_legal_status, by = "legal_status") %>% 
    mutate(legal_status_n = paste0(
      "<span style = 'font-size:16pt'>", legal_status, "</span><br><br>",
      "<span style = 'font-size:12pt'><em>", "Placement Episodes:", "</span><br>",
      "<span style = 'font-size:12pt'><em>","N: ",sample_n,"; ", sample_percent, "%","</em></span>")) %>% 
  filter(legal_status=="State Ward")

### plot
mdhhs_state_ward_place_per_episode <- ggplot(data = jj_legal_status_placements_per_episode_state_ward_only, aes(y = percent, x = placements_within_episode_bin, fill = forcats::fct_rev(placements_within_episode_bin))) + 
  geom_bar(stat = "identity", color = "gray80") +
  scale_x_discrete() +
  scale_y_continuous(labels = scales::percent_format(accuracy=1)) +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
  coord_flip() +
  geom_label_repel(aes(label = scales::percent(percent, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                   box.padding = 0.25,
                  fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

mdhhs_state_ward_place_per_episode

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_state_ward_place_per_episode.png", mdhhs_state_ward_place_per_episode, width = 8, height = 6)
```

<br><br>

```{r eval=FALSE,include=FALSE,echo=FALSE, warning=FALSE, message=FALSE}
### Formerly slide 31, Distribution of placement episodes within a unique episode (state wards only), 2015-2018 -- OPTION 2


### plot
ggplot(data = jj_legal_status_placements_per_episode_state_ward_only, aes(y = percent, x = placements_within_episode_bin, fill = forcats::fct_rev(placements_within_episode_bin))) + 
  geom_bar(stat = "identity", color = "gray80") +
  scale_x_discrete() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,accuracy=.1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 4.5,
    colour = "black",
    fill = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = rev(c("#00475d","#007392","#0db4e4","#9ed4ef","#d4e9f8"))) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
  labs(x = NULL, y = NULL,
       fill = "Individual Placements per Episode",
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        # axis.text.y = element_text(face = "bold", hjust = 1, size = 15),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
  coord_flip()
```

<br><br>

### Slide 32, prior history of mdhhs placement, 2015-2020
```{r echo=FALSE, warning=FALSE, message=FALSE}
### create placements per episode bins
jj_assessments_placement_legal_status_clean %<>%
  mutate(prior_placement_episodes_bin = case_when(
    prior_placement_episodes==0 ~ 1,
    prior_placement_episodes==1 ~ 2,
    prior_placement_episodes>1 ~ 3,
    TRUE ~ as.numeric(NA)),
    prior_placement_episodes_bin = factor(prior_placement_episodes_bin,
         levels = c(1,2,3),
         labels = c("0", "1", "2+"))) ### use factor function to assign labels to values

### total unique placement episodes -- overall
### using only as denominator for percentages in jj_placement_episode_count_disp_risk_table
jj_placement_episode_history_overall <- jj_assessments_placement_legal_status_clean %>% 
  filter(!is.na(prior_placement_episodes_bin)==TRUE,
         !is.na(placement_episode_segment)==TRUE,
         placement_episode_does_count==1) %>% 
  summarize(`Unique Placement Episodes, State Ward` = n_distinct(placement_episode_unique_id[legal_status_ward_flag=="State Ward" & placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)]),
            `Unique Placement Episodes, Dual Ward` = n_distinct(placement_episode_unique_id[legal_status_ward_flag=="Dual Ward" & placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)])) 

### total unique placement episodes (year is year that placement episode starts; many placements in 2015-2020 started prior to 2015)
jj_placement_episode_history_table <- jj_assessments_placement_legal_status_clean %>% 
  filter(!is.na(prior_placement_episodes_bin)==TRUE,
         !is.na(placement_episode_segment)==TRUE,
         placement_episode_does_count==1) %>% 
  group_by(prior_placement_episodes_bin) %>% 
 summarize(
   # Unique Placement Episodes, State Ward (N)` = n_distinct(placement_episode_unique_id[legal_status_ward_flag=="State Ward" & placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)]),
           `State Ward` = n_distinct(placement_episode_unique_id[legal_status_ward_flag=="State Ward" & placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)])/jj_placement_episode_history_overall$`Unique Placement Episodes, State Ward`,
            # `Unique Placement Episodes, Dual Ward (N)` = n_distinct(placement_episode_unique_id[legal_status_ward_flag=="Dual Ward" & placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)]),
           `Dual Ward` = n_distinct(placement_episode_unique_id[legal_status_ward_flag=="Dual Ward" & placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)])/jj_placement_episode_history_overall$`Unique Placement Episodes, Dual Ward`) %>% 
  ungroup()

### use gather for plotting
jj_placement_episode_history_table %<>%
  gather(legal_status, percent, c(`State Ward`,`Dual Ward`))

### plot
mdhhs_state_ward_dual_ward_prior_history <- ggplot(data = jj_placement_episode_history_table,
            mapping = aes(x = prior_placement_episodes_bin, y = percent, fill = prior_placement_episodes_bin)) +
  geom_bar(stat = "identity", position = "dodge") +
    scale_fill_manual(values = c("#007392","#0db4e4","#9ed4ef")) +
    scale_y_continuous(label=scales::percent_format(accuracy = 1),
                       limits=c(min(0), 
                                max(.8))) +
    scale_x_discrete(labels = scales::wrap_format(15), limits = rev) +
    theme(axis.text.x = element_text(size = 10, face="bold"),
       axis.ticks.length = unit(0, "cm"),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11,
                              margin=margin(r=10))) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
    facet_grid(legal_status ~ ., scales="free_y", space="free_y", switch="y") +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = scales::percent(percent, accuracy = 1), group = prior_placement_episodes_bin),
                 position = position_dodge(.9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.25,
                  box.padding = 0.25,
                  fill = "white",
                  color = "gray40",
                   fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE) 

mdhhs_state_ward_dual_ward_prior_history

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_state_ward_dual_ward_prior_history.png", mdhhs_state_ward_dual_ward_prior_history, width = 8, height = 6)
```

<br><br>

### Slide 37, RRI disparities, placement episode disparities, 2015-2020

NOTE: I have not included American Indian youth in the visual because of their small sample size (N=68 across 5 years) and huge RRI (around 7 times as likely as White youth to be placed by MDHHS). I think we landed on noting this apparent disparity in text/out loud during the presentation but not using the specific number since we are concerned about drawing too precise of a quantitative conclusion from such a small cohort of youth

Create new category for legal status -- only state ward and any dual ward or initial legal status for study period; filter for legal status of first episode within study window: placement_episode_segment_episode_counts_only==1 & legal_status=="State Ward"

ADD CAPTION EXPLAINING LEGAL STATUS DECISION AND EXCLUSION OF AMERICAN INDIAN YOUTH FROM VIZ
```{r echo=FALSE,message=FALSE,warning=FALSE}
# NOTE: Wayne County entirely excluded from calculation (Soleil indicated that Wayne County provides their own services, rarely send youth to state (only in specific waiver cases))

### pull in ezapop population data without wayne county
### import ezapop race/ethnicity data for 10-17 y/o michigan residents for RRI calculation
df_ezapop_race_ethnicity_10_17_no_wayne <- readr::read_delim("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\ezapop_raw_data_file\\Michigan\\ezapop_10_17_race_eth_sex_mi_state_level_no_wayne.txt", delim = "|")

### create clean lookup table to join
df_ezapop_race_ethnicity_lookup_no_wayne <-  data.frame(race  = c("Black", "Hispanic", "American Indian/Alaskan Native", "Other", "White"),
                  `pop_10_17_no_wayne` = c(df_ezapop_race_ethnicity_10_17_no_wayne$not_hispanic_black, df_ezapop_race_ethnicity_10_17_no_wayne$hispanic_any_race, df_ezapop_race_ethnicity_10_17_no_wayne$not_hispanic_am_in_ak_native, "NA", df_ezapop_race_ethnicity_10_17_no_wayne$not_hispanic_white)
                  ) %>% 
  mutate(pop_10_17_no_wayne = as.numeric(pop_10_17_no_wayne))

### join lookup to analytic file
jj_assessments_placement_legal_status_clean_no_wayne <- left_join(jj_assessments_placement_legal_status_clean,df_ezapop_race_ethnicity_lookup_no_wayne, by = c("race_csg_4"="race")) %>% 
  filter(county_name!="Wayne")

### white, non-hispanic only for rri calculation
jj_placement_race_ethnicity_rri_table_white <- jj_assessments_placement_legal_status_clean_no_wayne %>% 
  filter(!is.na(race_csg_4)==TRUE,
         race_csg_4=="White") %>% 
  summarize(`Unique Youth Placed (N)` = n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1]),
            # `Unique Placements per 10k Youth` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000, digits = 1), 
             `Unique Youth Placed per 10k Youth (No Wayne)` = round(n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1])/mean(pop_10_17_no_wayne)*10000, digits = 1), 
            `Unique Youth Placed, RRI (to white youth)` = NA,
            `Unique Youth Placed, State Ward (N)` = n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1 & placement_episode_segment_episode_counts_only==1 & legal_status_ward_flag=="State Ward"]),
            # `Unique Placements per 10k Youth` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000, digits = 1), 
             `Unique Youth Placed per 10k Youth (No Wayne), State Ward` = round(n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1 & placement_episode_segment_episode_counts_only==1 & legal_status_ward_flag=="State Ward"])/mean(pop_10_17_no_wayne)*10000, digits = 1), 
            `Unique Youth Placed, State Ward, RRI (to white youth)` = NA,
                        `Unique Youth Placed, Dual Ward (N)` = n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1 & placement_episode_segment_episode_counts_only==1 & legal_status_ward_flag=="Dual Ward"]),
            # `Unique Placements per 10k Youth` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000, digits = 1), 
             `Unique Youth Placed per 10k Youth (No Wayne), Dual Ward` = round(n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1 & placement_episode_segment_episode_counts_only==1 & legal_status_ward_flag=="Dual Ward"])/mean(pop_10_17_no_wayne)*10000, digits = 1), 
            `Unique Youth Placed, Dual Ward, RRI (to white youth)` = NA,
            `Unique Placements (N)` = n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1]),
            # `Unique Placements per 10k Youth` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000, digits = 1), 
             `Unique Placements per 10k Youth (No Wayne)` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1])/mean(pop_10_17_no_wayne)*10000, digits = 1), 
            # `Unique Placements, RRI (to white youth)` = NA,
            `Unique Placements, RRI (to white youth)` = NA,
`Unique Placement Episodes (N)` = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020 & placement_episode_does_count==1)]),
# `Unique Placement Episodes per 10k Youth` = round(n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000,  digits = 1),
`Unique Placement Episodes per 10k Youth (No Wayne)` = round(n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020) & placement_episode_does_count==1])/mean(pop_10_17_no_wayne)*10000,  digits = 1),
            # `Unique Placement Episodes, RRI (to white youth)` = NA,
`Unique Placement Episodes, RRI (to white youth)` = NA) %>% 
  dplyr::mutate(`Race/Ethnicity` = "White")


####### total unique placement episodes (year is year that placement episode starts; many placements in 2015-2020 started prior to 2015)
jj_placement_race_ethnicity_rri_table <- jj_assessments_placement_legal_status_clean_no_wayne %>% 
  filter(!is.na(race_csg_4)==TRUE,
         race_csg_4 %in% c("Black","Hispanic","American Indian/Alaskan Native")) %>% 
  group_by(race_csg_4) %>% 
  summarize(`Unique Youth Placed (N)` = n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1]),
            # `Unique Placements per 10k Youth` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000, digits = 1), 
             `Unique Youth Placed per 10k Youth (No Wayne)` = round(n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1])/mean(pop_10_17_no_wayne)*10000, digits = 1), 
            # `Unique Placements, RRI (to white youth)` = round(`Unique Placements per 10k Youth`/jj_placement_race_ethnicity_rri_table_white$`Unique Placements per 10k Youth`, digits = 2),
            `Unique Youth Placed, RRI (to white youth)` = round(`Unique Youth Placed per 10k Youth (No Wayne)`/jj_placement_race_ethnicity_rri_table_white$`Unique Youth Placed per 10k Youth (No Wayne)`, digits = 2),
                        `Unique Youth Placed, State Ward (N)` = n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1 & placement_episode_segment_episode_counts_only==1 & legal_status_ward_flag=="State Ward"]),
            # `Unique Placements per 10k Youth` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000, digits = 1), 
             `Unique Youth Placed per 10k Youth (No Wayne), State Ward` = round(n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1 & placement_episode_segment_episode_counts_only==1 & legal_status_ward_flag=="State Ward"])/mean(pop_10_17_no_wayne)*10000, digits = 1), 
            `Unique Youth Placed, State Ward, RRI (to white youth)` = round(`Unique Youth Placed per 10k Youth (No Wayne), State Ward`/jj_placement_race_ethnicity_rri_table_white$`Unique Youth Placed per 10k Youth (No Wayne), State Ward`, digits = 2),
                        `Unique Youth Placed, Dual Ward (N)` = n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1 & placement_episode_segment_episode_counts_only==1 & legal_status_ward_flag=="Dual Ward"]),
            # `Unique Placements per 10k Youth` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000, digits = 1), 
             `Unique Youth Placed per 10k Youth (No Wayne), Dual Ward` = round(n_distinct(person_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1 & placement_episode_segment_episode_counts_only==1 & legal_status_ward_flag=="Dual Ward"])/mean(pop_10_17_no_wayne)*10000, digits = 1), 
            `Unique Youth Placed, Dual Ward, RRI (to white youth)` = round(`Unique Youth Placed per 10k Youth (No Wayne), Dual Ward`/jj_placement_race_ethnicity_rri_table_white$`Unique Youth Placed per 10k Youth (No Wayne), Dual Ward`, digits = 2),
            `Unique Placements (N)` = n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1]),
            # `Unique Placements per 10k Youth` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000, digits = 1), 
             `Unique Placements per 10k Youth (No Wayne)` = round(n_distinct(placement_unique_id[placement_begin_date_year%in%c(2015,2016,2017,2018,2019,2020) & placement_does_count==1])/mean(pop_10_17_no_wayne)*10000, digits = 1), 
            # `Unique Placements, RRI (to white youth)` = round(`Unique Placements per 10k Youth`/jj_placement_race_ethnicity_rri_table_white$`Unique Placements per 10k Youth`, digits = 2),
            `Unique Placements, RRI (to white youth)` = round(`Unique Placements per 10k Youth (No Wayne)`/jj_placement_race_ethnicity_rri_table_white$`Unique Placements per 10k Youth (No Wayne)`, digits = 2),
`Unique Placement Episodes (N)` = n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020 & placement_episode_does_count==1)]),
# `Unique Placement Episodes per 10k Youth` = round(n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020)])/mean(pop_10_17)*10000,  digits = 1),
`Unique Placement Episodes per 10k Youth (No Wayne)` = round(n_distinct(placement_episode_unique_id[placement_episode_start_year%in%c(2015,2016,2017,2018,2019,2020) & placement_episode_does_count==1])/mean(pop_10_17_no_wayne)*10000,  digits = 1),
            # `Unique Placement Episodes, RRI (to white youth)` = round(`Unique Placement Episodes per 10k Youth`/jj_placement_race_ethnicity_rri_table_white$`Unique Placement Episodes per 10k Youth`, digits = 2),
`Unique Placement Episodes, RRI (to white youth)` = round(`Unique Placement Episodes per 10k Youth (No Wayne)`/jj_placement_race_ethnicity_rri_table_white$`Unique Placement Episodes per 10k Youth (No Wayne)`, digits = 2)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_csg_4) 

### merge tables together
jj_placement_race_ethnicity_rri_plot <- rbind(jj_placement_race_ethnicity_rri_table,jj_placement_race_ethnicity_rri_table_white) %>% 
  filter(`Race/Ethnicity` %in% c("Black","Hispanic")) %>% ### filter out line for white youth -- is reference group for visualization below
  dplyr::select(`Race/Ethnicity`,`Unique Youth Placed, RRI (to white youth)`,`Unique Youth Placed, State Ward, RRI (to white youth)`,`Unique Youth Placed, Dual Ward, RRI (to white youth)`)

### use gather for plotting
jj_placement_race_ethnicity_rri_plot %<>%
  gather(rri_measure, rri, `Unique Youth Placed, RRI (to white youth)`:`Unique Youth Placed, Dual Ward, RRI (to white youth)`) %>%
    mutate(rri_measure = factor(rri_measure,
                                levels = c("Unique Youth Placed, RRI (to white youth)","Unique Youth Placed, State Ward, RRI (to white youth)","Unique Youth Placed, Dual Ward, RRI (to white youth)"))) %>% 
  mutate(rri_measure = case_when(
    rri_measure=="Unique Youth Placed, RRI (to white youth)" ~ "Overall",
    rri_measure=="Unique Youth Placed, State Ward, RRI (to white youth)" ~ "State Wards",
    rri_measure=="Unique Youth Placed, Dual Ward, RRI (to white youth)" ~ "Dual Wards",
    TRUE ~ as.numeric(NA)))

rri_labels <- c(`Unique Youth Placed, RRI (to white youth)` = "Youth Placed, Overall",
            `Unique Youth Placed, State Ward, RRI (to white youth)` = "Youth Placed, State Wards",
            `Unique Youth Placed, Dual Ward, RRI (to white youth)` = "Youth Placed, Dual Wards")

mdhhs_rri_overall_legal_status <- ggplot(data = jj_placement_race_ethnicity_rri_plot, aes(y = rri, x = rri_measure, fill = forcats::fct_rev(`Race/Ethnicity`))) + 
  geom_bar(stat = "identity", position = "dodge", color = "gray80") +
  geom_abline(slope=0, intercept=1,  col = "#000000", size = 1.5, linetype="dashed") +
  scale_x_discrete(labels = as_labeller(rri_labels), limits = rev) +
  scale_y_continuous(limits=c(min(0), 
                                           max(4.5))) +
  scale_fill_manual(values = c("#0db4e4","#007392")) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12),
        axis.ticks.length = unit(0, "cm")) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
 guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
  geom_label_repel(aes(label = format(round(as.numeric(rri), digits = 2), nsmall=2), group = forcats::fct_rev(`Race/Ethnicity`)),
                  position = position_dodge(.75),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.3,
                   box.padding = 0.15,
                  fill = "white",
                  color = "gray40",
                  fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE) +
  annotate("text", x = 3.52, y = 2.47, label = "This line represents White youth (reference group)", colour = "#000000", size = 3.5, fontface = 2)

mdhhs_rri_overall_legal_status

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_rri_overall_legal_status.png", mdhhs_rri_overall_legal_status, width = 8, height = 6)
```

<br><br>

### Additional Visual (slide #?): LOS disparities -- CCI/MDHHS disparities not statistically significant, but detention is for Black and White youth, 2015-2018
```{r echo=FALSE,message=FALSE,warning=FALSE}
### disable scientific notation
options(scipen=999)

#############################
### t-test between black and white youth for los
jj_los_mean_black_white_t_test <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_start_year%in%c(2015,2016,2017,2018),
         race_csg_4 %in% c("Black","White"),
          placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
    distinct(person_id,placement_episode_segment, .keep_all = TRUE) %>% 
  dplyr::select(race_csg_4,los_overall_all_included,los_overall_cci_only,los_overall_mdhhs_only,los_overall_detention_only,los_overall_in_home_only,los_overall_jail_only,los_overall_hospital_treatment_only) ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
  # group_by(race_csg_4) %>% 
  # summarize(`Mean Placement Episode Length (Days)` = round(mean(los_overall_all_included, na.rm = TRUE), digits = 0), 
  #           `Mean Placement Episode Length (Days), AWOL Excluded` = round(mean(los_overall_awol_excluded, na.rm = TRUE), digits = 0),
  #           `Mean Length of Stay, JJ Out-of-Home (Days)` = round(mean(los_overall_detention_cci_only, na.rm = TRUE), digits = 0),
  #           `Mean Length of Stay, Post Out-of-Home Supervision (Days)` = round(mean(los_overall_post_detention_cci_only, na.rm = TRUE), digits = 0)) %>% 
  #   dplyr::rename(`Race/Ethnicity` = race_csg_4)

### run t-tests for white/black, white/hispanic, and white/american indian
t_test_white_black_overall <- jj_los_mean_black_white_t_test %$% 
  t.test(los_overall_all_included ~ race_csg_4, var.equal = FALSE)

### p=0.3068
# t_test_white_black_overall

t_test_white_black_out_of_home_cci <- jj_los_mean_black_white_t_test %$% 
  t.test(los_overall_cci_only ~ race_csg_4, var.equal = FALSE)

# p=0.7294
# t_test_white_black_out_of_home_cci

t_test_white_black_out_of_home_mdhhs <- jj_los_mean_black_white_t_test %$% 
  t.test(los_overall_mdhhs_only ~ race_csg_4, var.equal = FALSE)

#0.8742
# t_test_white_black_out_of_home_mdhhs

t_test_white_black_out_of_home_detention <- jj_los_mean_black_white_t_test %$% 
  t.test(los_overall_detention_only ~ race_csg_4, var.equal = FALSE)

### p=0.000003181
# t_test_white_black_out_of_home_detention

t_test_white_black_out_of_home_detention <- jj_los_mean_black_white_t_test %$% 
  t.test(los_overall_jail_only ~ race_csg_4, var.equal = FALSE)

### p=0.1414
# t_test_white_black_out_of_home_detention

t_test_white_black_out_of_home_detention <- jj_los_mean_black_white_t_test %$% 
  t.test(los_overall_hospital_treatment_only ~ race_csg_4, var.equal = FALSE)

### p=0.33
# t_test_white_black_out_of_home_detention

#############################
### t-test between hispanic and white youth for los
jj_los_mean_hispanic_white_t_test <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_start_year%in%c(2015,2016,2017,2018),
         race_csg_4 %in% c("Hispanic","White"),
          placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
    distinct(person_id,placement_episode_segment, .keep_all = TRUE) %>% 
  dplyr::select(race_csg_4,los_overall_all_included,los_overall_cci_only,los_overall_mdhhs_only,los_overall_detention_only,los_overall_in_home_only,los_overall_jail_only,los_overall_hospital_treatment_only) ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
  # group_by(race_csg_4) %>% 
  # summarize(`Mean Placement Episode Length (Days)` = round(mean(los_overall_all_included, na.rm = TRUE), digits = 0), 
  #           `Mean Placement Episode Length (Days), AWOL Excluded` = round(mean(los_overall_awol_excluded, na.rm = TRUE), digits = 0),
  #           `Mean Length of Stay, JJ Out-of-Home (Days)` = round(mean(los_overall_detention_cci_only, na.rm = TRUE), digits = 0),
  #           `Mean Length of Stay, Post Out-of-Home Supervision (Days)` = round(mean(los_overall_post_detention_cci_only, na.rm = TRUE), digits = 0)) %>% 
  #   dplyr::rename(`Race/Ethnicity` = race_csg_4)

### run t-tests for white/hispanic
t_test_white_hispanic_overall <- jj_los_mean_hispanic_white_t_test %$% 
  t.test(los_overall_all_included ~ race_csg_4, var.equal = FALSE)

### p=0.3685
# t_test_white_hispanic_overall

t_test_white_hispanic_out_of_home <- jj_los_mean_hispanic_white_t_test %$% 
  t.test(los_overall_cci_only ~ race_csg_4, var.equal = FALSE)

### p=0.4183
# t_test_white_hispanic_out_of_home

t_test_white_hispanic_out_of_home <- jj_los_mean_hispanic_white_t_test %$% 
  t.test(los_overall_mdhhs_only ~ race_csg_4, var.equal = FALSE)

### p=0.8138
# t_test_white_hispanic_out_of_home

t_test_white_hispanic_out_of_home <- jj_los_mean_hispanic_white_t_test %$% 
  t.test(los_overall_detention_only ~ race_csg_4, var.equal = FALSE)

### p=0.08759
# t_test_white_hispanic_out_of_home

t_test_white_hispanic_out_of_home <- jj_los_mean_hispanic_white_t_test %$% 
  t.test(los_overall_jail_only ~ race_csg_4, var.equal = FALSE)

### p=0.6096
# t_test_white_hispanic_out_of_home

t_test_white_hispanic_out_of_home <- jj_los_mean_hispanic_white_t_test %$% 
  t.test(los_overall_hospital_treatment_only ~ race_csg_4, var.equal = FALSE)

### p=0.3602
# t_test_white_hispanic_out_of_home


#############################
### t-test between american indian and white youth for los
jj_los_mean_am_ind_white_t_test <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_start_year%in%c(2015,2016,2017,2018),
         race_csg_4 %in% c("American Indian/Alaskan Native","White"),
          placement_episode_does_count==1) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
    distinct(person_id,placement_episode_segment, .keep_all = TRUE) %>% 
  dplyr::select(race_csg_4,los_overall_all_included,los_overall_cci_only,los_overall_mdhhs_only,los_overall_detention_only,los_overall_in_home_only,los_overall_jail_only,los_overall_hospital_treatment_only) ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
  # group_by(race_csg_4) %>% 
  # summarize(`Mean Placement Episode Length (Days)` = round(mean(los_overall_all_included, na.rm = TRUE), digits = 0), 
  #           `Mean Placement Episode Length (Days), AWOL Excluded` = round(mean(los_overall_awol_excluded, na.rm = TRUE), digits = 0),
  #           `Mean Length of Stay, JJ Out-of-Home (Days)` = round(mean(los_overall_detention_cci_only, na.rm = TRUE), digits = 0),
  #           `Mean Length of Stay, Post Out-of-Home Supervision (Days)` = round(mean(los_overall_post_detention_cci_only, na.rm = TRUE), digits = 0)) %>% 
  #   dplyr::rename(`Race/Ethnicity` = race_csg_4)

### run t-tests for white/am_ind
t_test_white_am_ind_overall <- jj_los_mean_am_ind_white_t_test %$% 
  t.test(los_overall_all_included ~ race_csg_4, var.equal = FALSE)

### p=0.8954
# t_test_white_am_ind_overall

t_test_white_am_ind_out_of_home <- jj_los_mean_am_ind_white_t_test %$% 
  t.test(los_overall_cci_only ~ race_csg_4, var.equal = FALSE)

### p=0.5391
# t_test_white_am_ind_out_of_home

t_test_white_am_ind_out_of_home <- jj_los_mean_am_ind_white_t_test %$% 
  t.test(los_overall_mdhhs_only ~ race_csg_4, var.equal = FALSE)

### p=0.8555
# t_test_white_am_ind_out_of_home

t_test_white_am_ind_out_of_home <- jj_los_mean_am_ind_white_t_test %$% 
  t.test(los_overall_detention_only ~ race_csg_4, var.equal = FALSE)

### p=0.6772
# t_test_white_am_ind_out_of_home

t_test_white_am_ind_out_of_home <- jj_los_mean_am_ind_white_t_test %$% 
  t.test(los_overall_jail_only ~ race_csg_4, var.equal = FALSE)

### p=0.2207
# t_test_white_am_ind_out_of_home

t_test_white_am_ind_out_of_home <- jj_los_mean_am_ind_white_t_test %$% 
  t.test(los_overall_hospital_treatment_only ~ race_csg_4, var.equal = FALSE)

### p=0.8787
# t_test_white_am_ind_out_of_home

### compile p-values into df (i know there's a better way to do this)
jj_los_mean_race_eth_t_test_p_values <- tribble(
  ~`Race/Ethnicity`,   ~`Mean Placement Episode Length (p-value)`, ~`Statistically Significant Difference? (episode length compared to White youth)`,    ~`Mean Length of Stay, CCI Out-of-Home (p-value)`, ~`Statistically Significant Difference? (CCI out-of-home length compared to White youth)`, ~`Mean Length of Stay, MDHHS Out-of-Home (p-value)`, ~`Statistically Significant Difference? (MDHHS out-of-home length compared to White youth)`,    ~`Mean Length of Stay, Detention Out-of-Home (p-value)`, ~`Statistically Significant Difference? (Detention out-of-home length compared to White youth)`,  ~`Mean Length of Stay, Jail Out-of-Home (p-value)`, ~`Statistically Significant Difference? (Jail out-of-home length compared to White youth)`,  ~`Mean Length of Stay, Treatment/Hospital Out-of-Home (p-value)`, ~`Statistically Significant Difference? (Treatment/Hospital out-of-home length compared to White youth)`,                                               
  "American Indian/Alaskan Native", ".895","No", ".539", "No",".861","No",".855","No",".221","No",".879","No",
  "Black", ".306", "No", ".729", "No", ".874","No",".000","Yes",".141","No",".330","No",
  "Hispanic", ".368","No", ".418", "No",".813","No",".088","Approaching Significance",".609","No",".360","No",
  "White", "NA", "NA","NA", "NA","NA","NA","NA","NA","NA","NA","NA","NA") 

### create df to highlight statistical significance from t-test
jj_los_mean_race_eth_t_test_table <- jj_assessments_placement_legal_status_clean %>% 
  filter(placement_episode_start_year%in%c(2015,2016,2017,2018),
         race_csg_4 %in% c("American Indian/Alaskan Native","White","Black","Hispanic")) %>% ### because we are grouping episodes by initial legal status (thus only need first unique placement within each episode; must have legal status in first placement for now unless we change business rules)
    distinct(person_id,placement_episode_segment, .keep_all = TRUE) %>% 
  dplyr::select(race_csg_4,los_overall_all_included,los_overall_cci_only,los_overall_mdhhs_only,los_overall_detention_only,los_overall_in_home_only,los_overall_jail_only,los_overall_hospital_treatment_only) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode
  group_by(race_csg_4) %>%
  summarize(`Mean Placement Episode Length (Days)` = round(mean(los_overall_all_included, na.rm = TRUE), digits = 0),
            `CCI Facility` = round(mean(los_overall_cci_only, na.rm = TRUE), digits = 0),
            `MDHHS Facility` = round(mean(los_overall_mdhhs_only, na.rm = TRUE), digits = 0),
            `Detention*` = round(mean(los_overall_detention_only, na.rm = TRUE), digits = 0),
            `Mean Length of Stay, Jail Out-of-Home (Days)` = round(mean(los_overall_jail_only, na.rm = TRUE), digits = 0),
            `Mean Length of Stay, Treatment/Hospital Out-of-Home (Days)` = round(mean(los_overall_hospital_treatment_only, na.rm = TRUE), digits = 0)) %>%
    dplyr::rename(`Race/Ethnicity` = race_csg_4)

jj_los_mean_race_eth_t_test_table <- inner_join(jj_los_mean_race_eth_t_test_table,jj_los_mean_race_eth_t_test_p_values, by="Race/Ethnicity") %>% 
  dplyr::select(`Race/Ethnicity`,`CCI Facility`, `MDHHS Facility`,`Detention*`) %>% 
  filter(`Race/Ethnicity` %in% c("Black","White","Hispanic")) %>% 
  mutate(`Race/Ethnicity` = ifelse(`Race/Ethnicity`== "Black","Black*",`Race/Ethnicity`))


### use gather for plotting
jj_los_mean_race_eth_t_test_table %<>%
  gather(facility, average_los, `CCI Facility`:`Detention*`) %>%
  mutate(facility = factor(facility,
                                levels = c("Detention*","CCI Facility","MDHHS Facility"))) %>% 
  filter(facility=="Detention*")

# rri_labels <- c(`Unique Youth Placed, RRI (to white youth)` = "Youth Placed, Overall",
#             `Unique Youth Placed, State Ward, RRI (to white youth)` = "Youth Placed, State Wards",
#             `Unique Youth Placed, Dual Ward, RRI (to white youth)` = "Youth Placed, Dual Wards")

mdhhs_los_mean_facility_race_eth <- ggplot(data = jj_los_mean_race_eth_t_test_table, aes(y = average_los, x = forcats::fct_rev(`Race/Ethnicity`), fill = forcats::fct_rev(`Race/Ethnicity`))) + 
  geom_bar(stat = "identity", position = "dodge", color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(limits=c(min(0), 
                                           max(112))) +
  scale_fill_manual(values = c("#007392","#0db4e4","#9ed4ef")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme(axis.text.x = element_text(size = 10, face="bold"),
       axis.ticks.length = unit(0, "cm"),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11,
                              margin=margin(r=10))) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
    # facet_grid(facility ~ ., scales="free_y", space="free_y", switch="y") +
  geom_label_repel(aes(label = paste0(average_los," Days"), group = forcats::fct_rev(`Race/Ethnicity`)),
                  position = position_dodge(.9),
                  direction = 'x',
                  hjust = .75,
                  label.padding = 0.3,
                   box.padding = 0.15,
                  fill = "white",
                  color = "gray40",
                  fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE) 

mdhhs_los_mean_facility_race_eth

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\mdhhs_los_mean_detention_only_race_eth.png", mdhhs_los_mean_facility_race_eth, width = 8, height = 6)
```

<br><br>
