---
title: "tcs_county_data_placement_charge_county_level_viz"
author: "Andrew Byrum"
date: "3/3/2022"
output: html_document
---

#  {.tabset .tabset-fade .tabset-pills}
```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","tidylog","csgjcr","psych")
```

```{r include=FALSE}
## Preliminary Cleaning

 
### 1. Read in Pertinent TCS Files for Placement Analysis: 'cases', 'charges', 'dispositions', and 'placements'
### set sharepoint path using csgjcr::csg_sp_path function
sharepoint_tcs_data_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Raw/Courts/JIS/TCS")

### import cases
tcs_cases <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_Cases_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import charges
tcs_charges <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_Charges_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import dispositions
tcs_dispositions <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_DispositionsPerCharge_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import placements
tcs_placements <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_Placements_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import mandatory events (to explore legal status)
tcs_mandatory_events <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_MandatoryEvents_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))
```

```{r include=FALSE}
### 2. De-dup/figure out primary keys for 'cases', 'charges', 'dispositions', and 'placements' and merge together
 
######################################
#### cases
######################################

# de-dup cases file -- there is a very slight discrepancy in N size when de-duping by only juvenile_nbr and case_number as opposed to also including one or more of the above dates; keeping as juvenile_nbr and case_number makes most intuitive sense pending confirmation from JIS contacts (also de-duping by offense_dt as we may need this for later joins...)

tcs_cases_de_dup <- tcs_cases %>%
  filter(!is.na(juvenile_nbr)==TRUE,
         juvenile_nbr!=0, ### there are a handful of records where juvenile_nbr=0; appears to be data error as the records don't consistently share other identifying info like dates and county
         !is.na(case_number)==TRUE) %>% 
  dplyr::rename(case_id = case_number) %>%  ### there are a number of important primary keys which have different names across the files -- here case_id and case_number are the same ID (naming all 'case_id')
  distinct(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,adjudication_dt) %>% 
  mutate(year = as.numeric(year),
         case_year = as.numeric(year))

### 99% of dropped cases are due to 'caseload_action' -- multiple entries as different stages of case are entered 
```

```{r include=FALSE}
######################################
#### charges
######################################

# de-dup charges file -- using case_id (same as 'case_number' in tcs_cases and 'id' (which is "Unique ID for the record.")); no records dropped
# note: there are 1,288 records in the cases df that do not appear at all in the charges df; note from Laura and team: "no juvenile name number in data set – link to cases and use Juvenile Nbr, if needed; 1 to many charges can relate to a case."
# case_number identifies case and id uniquely identifies charge within case  
tcs_charges_de_dup <- tcs_charges %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(id)==TRUE) %>% 
  distinct(id,case_id,.keep_all = TRUE) %>% 
  mutate(current_charge_classification_clean = ifelse(str_starts(current_offense,"712A"),"Status",current_offense_classification),
         year = as.numeric(year),
         case_year = as.numeric(case_year)) ### recode status offense (from laura's team: "If you filter on CurrentOffense by 712A – that should give you the status offenses.")
```

```{r include=FALSE}
######################################
#### placements
######################################

# de-dup placements file -- using case_id (same as 'case_number' in tcs_cases and 'id' (which is "Unique ID for the record.")); no records dropped 
# looks like there are some pure dups
tcs_placements_de_dup <- tcs_placements %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(name_nbr)==TRUE,
         order_type=="PCN") %>% ### from laura and team: "Would recommend using the PCN events and not use ORD ("ordered to transport"/temporary record).  Courts should be using PCN ("placement change notice") events."
  dplyr::rename(juvenile_nbr= name_nbr) %>% ### there are a number of important primary keys which have different names across the files -- here name_nbr and juvenile_nbr are the same ID (naming all 'juvenile_nbr')
  mutate(placement_los = time_length(difftime(place_end_date, place_begin_date), unit = 'days')) %>% 
  arrange(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,place_begin_date,place_type,-placement_los) %>% ### when all primary keys align, including placement start date, we are de-duping by keeping placement with longer LOS -- so arrange by primary keys and then placement LOS in descending order
  distinct(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,place_begin_date,place_type,.keep_all = TRUE) %>% ### 54 dups dropped
 mutate(unique_placement_id = paste0(juvenile_nbr,case_id,place_begin_date,place_type,place_end_date),
         unique_case_id = paste0(juvenile_nbr,case_id,case_year,case_type),
         unique_youth_id = paste0(court_type,year,tc_sreport_court_jcl,juvenile_nbr),
         year = as.numeric(year),
         case_year = as.numeric(year)) %>% ### create unique IDs for later counts or de-dups -- at placement, case, and youth level
  ungroup()
```

```{r include=FALSE}
######################################
#### tcs_mandatory_events
######################################
mandatory_events_violation <- c("VIOLATION OF CONSENT CALENDAR"
,"VIOLATION OF CONSENT CALENDAR/DIVERSION"
,"VIOLATION OF PROBATION"
,"PROBATION REVOKED"
,"PROBATION VIOLATION HEARING"
,"PROBATION VIOLATION SENTENCE")

tcs_mandatory_events_de_dup <- tcs_mandatory_events %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(id)==TRUE) %>% 
  distinct(case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,.keep_all = TRUE) %>% 
  mutate(violation_hearing_flag = ifelse(event_desc %in% mandatory_events_violation,1,0),
         # year = as.numeric(year),
         case_year = as.numeric(case_year)) %>%  ### recode status offense (from laura's team: "If you filter on CurrentOffense by 712A – that should give you the status offenses.")
  filter(violation_hearing_flag==1) %>% 
  dplyr::select(case_id,court_type,tc_sreport_court_jcl,case_year,case_type,violation_hearing_flag)
  
```

```{r include=FALSE}
### 3. Start Cleaning w/ Placements (this will serve as base file -- as we interested only in those for whom there is placement data)

# Here are our groupings for placement type:
placement_detention <- c("Calhoun County Juvenile Home","DETENTION","I-Child Vill Det (Not VC Disp)","NON-SECURE DETENTION","OTHER COUNTY DETENTION","Regional Detention Center","SECURE DETENTION")

placement_residential_non_mdhhs <- c("I-Boot Camp","I-CFY Ranch","I-Child Vill Residential","I-Child Vill Secure","I-Private Placement","Independent Placement","INSTITUTIONAL/RESIDENTIAL CARE","PRIVATE AGENCY/INSTITUTION","RESIDENTIAL PLACEMENT","CALHOUN TREATMENT CENTER","Residential Treatment Program")

placement_in_home_aftercare <- c("Aftercare/CV","Bond w/Father","Bond w/Mother","Boot Camp Aftercare","CFY Independent Living","Consent Probation/Father","Consent Probation/Mother","Consent Probation/Other","Consent Probation/Parents","Crossroads For Youth Aftercare","CUS","F01","Father","GDN","Guardian","Home of Guardian-Crt Supervsn","Home of Guardian-DHS Sprv.","Home of Guardian-FIA Supervsn","Home of Parent-Crt Supervision","Home of Parent-DHS Supervision","Home of Parent-FIA Supervision","Home of Parent-No Supervision","Home of parent CRT Supervision","Home of Relative-CRT Supervisi","HOME OF RELATIVE-CRT SUPERVSN","Home of Relative-FIA Supervisi","Home of Relative-FIA Supervsn","I-Child Vill Fam Based Reentry","I-Custodian","Intensive Probation/Father","Intensive Probation/Mother","Intensive Probation/Other","Intensive Probation/Parents","Intensive Reentry Parents","Intensive Reentry Program","Intensive Reentry/Father","Intensive Reentry/Mother","Intensive Reentry/Other","M01","Own Home (Both Parents)","Own Home/Father","Own Home/Mother","PARENTS","PLACED WITH PARENT-CRT SPRV","PLACED WITH PARENT-DHS SPRV","PLACED WITH RELATIVE-CRT SPRV","Probation/Father","Bond w/Parent", "Probation/Mother","Probation/Other","Probation/Parents","PTS","REL","Relative","Relative Placement","Unrelated Unlicensed Home","CFY Day Stud","CFY Work Ed Day St")

placement_mdhhs <- c("DEPARTMENT OF HUMAN SERVICES","DSS","Family Independence Agency","I-Department of Human Services","I-DHHS-150/Del")

placement_awol <- c("Absent without Leave","Order Take Into Custody")

placement_jail <- c("I-Oakland County Jail","Jail")

placement_foster_shelter <- c("Foster Care-Court Supervision","Foster Care-FIA Supervision","PLACED IN FOSTER CARE-DHS SPRV","PLACED IN FOSTER CARE-CRT SPRV","Shelter Home")
```

```{r include=FALSE}
#Create clean placement categories 

tcs_placements_de_dup %<>%
  mutate(place_type_clean = 
           case_when(
             place_type_desc %in% placement_detention ~ 1,
             place_type_desc %in% placement_residential_non_mdhhs ~ 2,
             place_type_desc %in% placement_mdhhs ~ 3,
             place_type_desc %in% placement_jail ~ 4,
             place_type_desc %in% placement_awol ~ 5,
             place_type_desc %in% placement_in_home_aftercare ~ 6,
             place_type_desc %in% placement_foster_shelter ~ 7,
             TRUE ~ as.numeric(NA)),
         place_type_clean = factor(place_type_clean,
         levels = c(1,2,3,4,5,6,7),
         labels = c("Detention","Residential","MDHHS","Jail","AWOL","In Home/Aftercare","Foster Care/Shelter Home"))) %>% ### use factor function to assign labels to values
  ungroup() %>% 
  mutate(place_year = year(ymd(place_begin_date))) ### create year of placement to use instead of year that case was filed -- to align with Becky's Kalamazoo data when used and to be consistent throughout
```

```{r include=FALSE}
### Join `Cases` to `Placements` to obtain adjudication date for parsing placements into pre- and post-adjudication groups (to analyze w/ most serious charge and most serious adjudicated charge, respectively)

### we don't successfully join for 62 placement records out of 10,325 total (0.6%; 99.4% match rate here)
tcs_placements_cases_de_dup <- left_join(tcs_placements_de_dup,tcs_cases_de_dup,by=c("juvenile_nbr","case_id","court_type","year","tc_sreport_court_jcl","case_year","case_type"))
```

```{r include=FALSE}
### Join `Cases` to `Placements` to obtain adjudication date for parsing placements into pre- and post-adjudication groups (to analyze w/ most serious charge and most serious adjudicated charge, respectively)

# ### we don't successfully join for 62 placement records out of 10,325 total (0.6%; 99.4% match rate here)
# tcs_placements_cases_de_dup_events <- left_join(tcs_placements_cases_de_dup,tcs_mandatory_events_de_dup,by=c("case_id","court_type","tc_sreport_court_jcl","case_year","case_type")) %>% 
#   group_by(unique_placement_id) %>% 
#   mutate(violation_hearing_flag = max(violation_hearing_flag)) %>% 
#   ungroup()
```

```{r include=FALSE}
### Join `Charges` to `Placements` to analyze placements counts and LOS by most severe charge (adjudicated charge)

### we don't successfully join for 885 placement records out of 10,325 total (8.5%; 91.5% match rate here) 
### we also add duplicates -- as more than one charge may link to an individual placement (we will eventually de-dup by most severe adjudicated charge associated with a placement)
### for this analysis, we need charge data so merging via inner_join to keep only records with both placement and charge data
tcs_placements_charges_de_dup <- inner_join(tcs_placements_cases_de_dup,tcs_charges_de_dup,by=c("case_id","court_type","year","tc_sreport_court_jcl","case_year","case_type")) %>% 
  mutate(adjudication_dt = ymd(adjudication_dt),
         place_begin_date = ymd(place_begin_date),
         dispo_date = ymd(mdy(dispo_date)),
         dispo_adj_latest_date = ymd(dispo_date),
         unique_placement_los = time_length(difftime(dispo_date, adjudication_dt), unit = 'days'),
         dispo_adj_latest_date = ifelse(is.na(dispo_adj_latest_date)==TRUE,adjudication_dt,dispo_adj_latest_date)) %>% 
         # dispo_adj_latest_date = ifelse(dispo_adj_latest_date>=adjudication_dt,dispo_adj_latest_date,adjudication_dt),
         # dispo_adj_latest_date = ifelse(is.na(dispo_adj_latest_date)==TRUE,dispo_date,dispo_adj_latest_date)) %>%  ### alger county appears to only use 'dispo date', not 'adjudication date') %>% 
  filter(!is.na(dispo_date)==TRUE) %>% 
  mutate(before_adjudication_flag = ifelse(place_begin_date<dispo_date,1,0),
         after_adjudication_flag = ifelse(place_begin_date>=dispo_date,1,0)) 

# %>% 
#   select(case_file_dt.x,place_begin_date,adjudication_dt,dispo_date,sentence_date,offense_date,unique_placement_los,dispo_adj_latest_date,before_adjudication_flag,after_adjudication_flag)
```

```{r include=FALSE}
### Flag charges with adjudication before de-duping by placement/charge

# (NOT COUNTING THE FOLLOWING AS DISPOSITION: CHANGE VENUE/TRANSFER, CONSENT CALENDAR PLAN, CONSENT CALENDAR PROBATION, , DISMISS INCOMPETENT, DISMISSED, DISMISSED INCOMPETENT,DIVERTED, FOUND GUILTY, FOUND NOT COMPETENT, INACTIVE INCOMPETENT, NOT AUTHORIZED, NOT CHARGED, NOT FOUND W/IN PROVISION CODE, NOT GUILTY, REMAND, TRANSFER, TRADITIONAL WAIVER,DESIGNATED GRANTED)

charge_adjudicated <- c("ADMITTED ALLEGATIONS","FOUND GUILTY","FOUND WITHIN PROVISION OF CODE","GUILTY","NOLO CONTENDERE")

### keep only charges with adjudication
tcs_placements_charges_de_dup %<>% 
  mutate(charge_adjudicated_flag = ifelse(charge_disposition %in% charge_adjudicated,1,0)) %>% 
  # filter(charge_disposition %in% charge_adjudicated) %>%
  mutate(original_offense = str_to_lower(original_offense),
         original_offense = str_replace_all(original_offense,"[:punct:]", ""),
         current_offense = str_to_lower(current_offense),
         current_offense = str_replace_all(current_offense,"[:punct:]", "")) ### remove all punctuation from current_offense and make all lower case -- for merge with current_offense from Emily's lookup table
```

```{r include=FALSE}
### Read in PACC code lookup table that Emily created

### set sharepoint path using csgjcr::csg_sp_path function
sharepoint_pacc_lookup_data_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Converted/JDW/")

### import pacc lookup -- jdw -- current offense
jdw_charge_pacc_code_lookup_current <- readr::read_csv(
  file.path(
    sharepoint_pacc_lookup_data_path, "JDWOffCodes_sheet_1_csv.csv")) %>% 
  clean_names() %>% 
  dplyr::rename(category = category,
                offcode_combined = offcode_combined,
                off_level = off_level,
                severity = severity) %>% 
  mutate(current_offense = str_to_lower(offcode_combined),
         current_offense = str_replace_all(current_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
  distinct(current_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements

### import pacc lookup -- msp -- current offense
msp_charge_pacc_code_lookup_current <- readr::read_csv(
  file.path(
    sharepoint_pacc_lookup_data_path, "JDWOffCodes_sheet_2_csv.csv")) %>% 
  clean_names() %>% 
  rename(offcode_combined = disposedcode,
         off_level = desposeddegreefelonymisdeme,
         category = off_cat,
         severity = severity) %>% 
  select(-disposeddescription) %>% 
  mutate(current_offense = str_to_lower(offcode_combined),
         current_offense = str_replace_all(current_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
  distinct(current_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements

### stack msp and jdw lookups
jdw_msp_charge_pacc_code_current_lookup <- rbind(jdw_charge_pacc_code_lookup_current,msp_charge_pacc_code_lookup_current) %>% 
  distinct(current_offense,.keep_all=TRUE)
```

```{r include=FALSE}
# ### import pacc lookup -- jdw -- original offense
# jdw_charge_pacc_code_lookup_original <- readr::read_csv(
#   file.path(
#     sharepoint_pacc_lookup_data_path, "JDWOffCodes_as_csv_abyrum.csv")) %>% 
#   clean_names() %>% 
#   dplyr::rename(category_original = category,
#                 offcode_combined_original = offcode_combined,
#                 off_level_original = off_level,
#                 severity_original = severity) %>% 
#   mutate(original_offense = str_to_lower(offcode_combined_original),
#          original_offense = str_replace_all(original_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
#   distinct(original_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements
# 
# ### import pacc lookup -- msp -- original offense
# msp_charge_pacc_code_lookup_original <- readr::read_csv(
#   file.path(
#     sharepoint_pacc_lookup_data_path, "MSPOffCodes_as_csv_abyrum.csv")) %>% 
#   clean_names() %>% 
#   rename(offcode_combined_original = disposedcode,
#          off_level_original = desposeddegreefelonymisdeme,
#          category_original = off_cat,
#          severity_original = severity) %>% 
#   select(-disposeddescription) %>% 
#   mutate(original_offense = str_to_lower(offcode_combined_original),
#          original_offense = str_replace_all(original_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
#   distinct(original_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements
# 
# ### stack msp and jdw lookups
# jdw_msp_charge_pacc_code_original_lookup <- rbind(jdw_charge_pacc_code_lookup_original,msp_charge_pacc_code_lookup_original) %>% 
#   distinct(original_offense,.keep_all=TRUE)
```

```{r include=FALSE}
### Join jdw_charge_pacc_code_lookup to tcs_placements_charges_de_dup


### no corresponding pacc lookup values for 189 records (189/13955; 1.4%) -- current offense
tcs_placements_charges_de_dup_pacc <- left_join(tcs_placements_charges_de_dup,jdw_msp_charge_pacc_code_current_lookup,by="current_offense") 


# tcs_placements_charges_de_dup_pacc_missing <- tcs_placements_charges_de_dup_pacc %>% 
#   filter(is.na(category)==TRUE) %>% 
#     dplyr::select(unique_placement_id,case_id,tc_sreport_court_jcl,place_type,place_type_desc,place_type_clean,case_year,county.x,current_offense,current_description,place_begin_date,place_end_date,dispo_date,adjudication_dt)
# ### NOT USING ORIGINAL OFFENSE -- 2400+ RECORDS HAVE 'PENDING' WHICH OBVIOUSLY DOESN'T MATCH AND LEAVES US WITH TOO MUCH MISSINGNESS HERE
# tcs_placements_charges_de_dup_pacc <- left_join(tcs_placements_charges_de_dup_pacc,jdw_msp_charge_pacc_code_original_lookup,by="original_offense") 
```

```{r include=FALSE}
#Recode several missing offenses based on Emily's notes:

recode_to_status <- c("712a2d4","722755","ord code 26267")

recode_to_misd_non_person <- c("7503675","7505354a1","ord code 2649","ord code 26492","ord code 2651","ord code 2654","7527971a","9999999904","local orddisorderly")

recode_to_misd_person <- c("75081a1")

recode_to_felony_person <- c("roassault police")
```

```{r include=FALSE}
### De-dup by `placement` and `case` -- create flag to designate the most serious charge associated with that unique `placement`/`case`

# From TCS code book: Current Offense Classification - C/Civil Infraction, F/Felony, M/Misdemeanor, S/Statute, H/High Misdemeanor, O/Other, V/Civil-Other, R/Ordinance, Z/Notice for Advisories

### pre-adjudication
tcs_placements_charges_de_dup_pacc_pre_adj <- tcs_placements_charges_de_dup_pacc %>%
  filter(before_adjudication_flag==1) %>% 
  mutate(current_charge_classification_clean_numeric = case_when(
    (off_level == "F" & category == "Person") | current_offense%in%recode_to_felony_person ~ 1,
    off_level == "F" & category != "Person" ~ 2,
    (off_level == "M" & category == "Person") | current_offense%in%recode_to_misd_person ~ 3,
    (off_level == "M" & category != "Person") | current_offense%in%recode_to_misd_non_person ~ 4,
    off_level == "S" | current_offense%in%recode_to_status ~ 5,
    off_level %in% c("I","X") ~ 6,
    TRUE ~ as.numeric(NA)),
    current_charge_classification_clean_factor = factor(current_charge_classification_clean_numeric,
         levels = c(1,2,3,4,5,6),
         labels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status","Other/Unknown"))) %>% ### use factor function to assign labels to values)
  arrange(unique_placement_id,current_charge_classification_clean_numeric) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) ### now we are back to original cleaned N

### post-adjudication
# tcs_placements_charges_de_dup_pacc_post_adj <- tcs_placements_charges_de_dup_pacc %>%
#   filter(after_adjudication_flag==1,
#          charge_adjudicated_flag==1) %>% 
#   mutate(current_charge_classification_clean_numeric = case_when(
#     off_level == "F" &  category == "Person" ~ 1,
#     off_level == "F" &  category != "Person" ~ 2,
#     off_level == "M" &  category == "Person" ~ 3,
#     off_level == "M" &  category != "Person" ~ 4,
#     off_level == "S" ~ 5,
#     off_level %in% c("I","X") ~ 6,
#     TRUE ~ as.numeric(NA)),
#     current_charge_classification_clean_factor = factor(current_charge_classification_clean_numeric,
#          levels = c(1,2,3,4,5,6),
#          labels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status","Other/Unknown"))) %>% ### use factor function to assign labels to values)
#   arrange(unique_placement_id,current_charge_classification_clean_numeric) %>% 
#   distinct(unique_placement_id, .keep_all=TRUE) %>%  ### now we are back to original cleaned N
#   mutate(violation_hearing_flag = ifelse(is.na(violation_hearing_flag)==TRUE,0,violation_hearing_flag))
```

<br>

## Detention/Offense Visuals

```{r include=FALSE}
### set theme and font size
theme_set(theme_minimal())

### disable scientific notation for viz
options(scipen=999)

### full jj blue palette for reference -- NEED NEW PALETTE
jj_pal <- c("#00475d","#007392","#0db4e4","#9ed4ef","#d4e9f8")

new_pal_five <- c("#d6df23","#007392","#eeed90","#0db4e4","#315c15")

new_pal_six <- c("#7fc241","#d6df23","#007392","#eeed90","#0db4e4","#315c15")

new_pal_blue_two <- c("#007392","#0db4e4")

new_pal_blue_two_other <- c("#007392","#d6df23")
```

<br>

### **Detention by Offense, Pre-Disposition**

<br>

#### PRE-DISPOSITION DETENTION: % of detentions by most serious offense, 2016-2020

Note: There is substantial variation by county. And there are only 8 counties included as Mackinac doesn't distinguish detention from residential in placement coding so they are excluded throughout

```{r echo=FALSE,message=FALSE,warning=FALSE}
### recode offense category into felony, misd, and status
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(current_charge_classification_clean_factor_grouped = case_when(
    current_charge_classification_clean_factor == "Felony, Person" | current_charge_classification_clean_factor == "Felony, Non-Person"  ~ 1,
    current_charge_classification_clean_factor == "Misdemeanor, Person" | current_charge_classification_clean_factor == "Misdemeanor, Non-Person"  ~ 2,
    current_charge_classification_clean_factor == "Status"  ~ 3,
    current_charge_classification_clean_factor == "Other/Unknown"  ~ 4,
    TRUE ~ as.numeric(NA)),
    current_charge_classification_clean_factor_grouped = factor(current_charge_classification_clean_factor_grouped,
         levels = c(1,2,3,4),
         labels = c("Felony","Misdemeanor","Status","Other/Unknown")))


tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  # group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  # complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0))
  # mutate(county_anonymous = paste0("County ", row_number())) %>% 
  # filter(current_charge_classification_clean_factor_grouped=="Status")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention,
            mapping = aes(x = reorder(current_charge_classification_clean_factor_grouped, `Detention (%)`), y = `Detention (%)`, fill = current_charge_classification_clean_factor_grouped)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.75))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12),
        axis.text.x = element_blank(),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Detention (%)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)


# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\tcs_detention_placement_rate_county_incl_kalamazoo.png", tcs_detention_placement_rate_county_incl_kalamazoo, width = 8, height = 6)
```


```{r include=FALSE, eval=FALSE,message=FALSE,warning=FALSE}
# <br><br>
# 
# #### PRE-DISPOSITION DETENTION: % of detentions for which most serious charge is a misdemeanor offense, 2016-2020
# 
# BY COUNTY FOR INTERNAL DISCUSSION (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)
                                   

tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) %>% 
  filter(current_charge_classification_clean_factor_grouped=="Misdemeanor")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention,
            mapping = aes(x = reorder(county_anonymous, `Detention (%)`), y = `Detention (%)`, fill = current_charge_classification_clean_factor_grouped), group = county_anonymous) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(1))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 2.25, y = .8, label = "Each bar represents the % of detentions\nfor misdemeanor offenses within one county", colour = "#00475d", size = 4) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12),
        axis.text.x = element_blank(),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Detention (%)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)


# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\tcs_detention_placement_rate_county_incl_kalamazoo.png", tcs_detention_placement_rate_county_incl_kalamazoo, width = 8, height = 6)
```

<br><br>

#### PRE-DISPOSITION DETENTION: detentions by most serious charge (%) and year of placement, 2016-2020

Note: There is substantial variation by county. And there are only 8 counties included as Mackinac doesn't distinguish detention from residential in placement coding so they are excluded throughout

```{r echo=FALSE,message=FALSE,warning=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(place_year) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(place_year,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$place_year==place_year]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(place_year,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  # mutate(county_anonymous = paste0("County ", row_number())) %>% 
  group_by(place_year) %>% 
  # mutate(felony_percent = `Detention (%)`[current_charge_classification_clean_factor_grouped=="Felony"]) %>% 
  filter(current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  ungroup()

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention, aes(y = `Detention (%)`, x = reorder(place_year,-place_year), fill = forcats::fct_rev(current_charge_classification_clean_factor_grouped))) + 
  geom_bar(stat = "identity", color = "gray80") +
  # scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = rev(c("#007392","#0db4e4","#9ed4ef"))) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
    geom_label(
    aes(
      y = `Detention (%)`,
      label = scales::percent(`Detention (%)`,accuracy=1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 5,
    colour = "black",
    fill = "white",
    show.legend = FALSE
  ) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = "Each bar represents one year.\n'Other/Unknown' offenses excluded (<1% of sample)",
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12),
        axis.text.x = element_blank(),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\Iowa Revocation Reduction\\Work Products\\Presentations\\r_viz\\supervision_status_by_district_2020.png", supervision_status_by_district_2020, width = 9, height = 6.5) 
```

<br><br>

### **Length of Stay, Pre-Disposition**

```{r include=FALSE,message=FALSE,warning=FALSE}

### Calculate length of stay and create LOS buckets, PRE-ADJUDICATION

### calculate length of stay in two different ways:
# los with everything counted 
# los split into placement type buckets -- making sure to recode '0' as NA so as to not bring down mean LOS when youth was never actually placed somewhere
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  group_by(unique_case_id) %>% ### group by case
  mutate(case_first_place_date = min(place_begin_date),
         case_last_place_date = max(place_end_date)) %>%
  ungroup() %>% 
  mutate(unique_placement_los = time_length(difftime(place_end_date, place_begin_date), unit = 'days'),
         los_unique_placement_detention_only = ifelse(place_type_clean=="Detention",unique_placement_los,NA),
         los_unique_placement_residential_non_mdhhs_only = ifelse(place_type_clean=="Residential",unique_placement_los,NA),
         los_unique_placement_mdhhs_only = ifelse(place_type_clean=="MDHHS",unique_placement_los,NA)) %>% 
  group_by(unique_case_id) %>% 
  mutate(los_case_overall_all_included = sum(unique_placement_los),
         los_case_overall_all_included = ifelse(los_case_overall_all_included==0,NA,los_case_overall_all_included),
         los_overall_detention_only = sum(los_unique_placement_detention_only),
         los_overall_detention_only = ifelse(los_overall_detention_only==0,NA,los_overall_detention_only),
         los_overall_residential_only = sum(los_unique_placement_residential_non_mdhhs_only),
         los_overall_residential_only = ifelse(los_overall_residential_only==0,NA,los_overall_residential_only),
         los_overall_mdhhs_only = sum(los_unique_placement_mdhhs_only),
         los_overall_mdhhs_only = ifelse(los_overall_mdhhs_only==0,NA,los_overall_mdhhs_only)) %>% 
  ungroup()

### create grouped los bins for detention
### mirror becky's approach with the kalamazoo analysis
### recode LOS_placement (1/3=1 "1-3 days") (4/7=2 "4-7 days") (8/14=3 "8-14 days") (15/30=4 "15-30 days") (31/90=5 "1-3 months") (91/max=6 ">3 months"), gen (placement_buckets)
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(los_unique_placement_detention_only_grouped_bin = case_when(
    los_unique_placement_detention_only<3 | los_unique_placement_detention_only==0 ~ 1,
    los_unique_placement_detention_only>=3 & los_unique_placement_detention_only<7 ~ 2,
    los_unique_placement_detention_only>=7 & los_unique_placement_detention_only<15 ~ 3,
    los_unique_placement_detention_only>=15 & los_unique_placement_detention_only<=30 ~ 4,
    los_unique_placement_detention_only>=30 & los_unique_placement_detention_only<=90 ~ 5,
    los_unique_placement_detention_only>90 ~ 6,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_detention_only_grouped_bin = factor(los_unique_placement_detention_only_grouped_bin,
         levels = c(1,2,3,4,5,6),
         labels = c("1 to 3 Days", "3 to 7 Days", "7 to 14 Days","15 to 30 Days","30 to 90 Days","90 Days+"))) ### use factor function to assign labels to values

### create grouped los bins for residential placement
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(los_unique_placement_residential_only_grouped_bin = case_when(
    los_unique_placement_residential_non_mdhhs_only<32 & los_unique_placement_residential_non_mdhhs_only!=0 ~ 1,
    los_unique_placement_residential_non_mdhhs_only>=32 & los_unique_placement_residential_non_mdhhs_only<92 ~ 2,
    los_unique_placement_residential_non_mdhhs_only>=92 & los_unique_placement_residential_non_mdhhs_only<=275 ~ 3,
    los_unique_placement_residential_non_mdhhs_only>=275 & los_unique_placement_residential_non_mdhhs_only<=549 ~ 4,
    los_unique_placement_residential_non_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_residential_only_grouped_bin = factor(los_unique_placement_residential_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values

### create grouped los bins for mdhhs placement
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(los_unique_placement_mdhhs_only_grouped_bin = case_when(
    los_unique_placement_mdhhs_only<32 & los_unique_placement_mdhhs_only!=0 ~ 1,
    los_unique_placement_mdhhs_only>=32 & los_unique_placement_mdhhs_only<92 ~ 2,
    los_unique_placement_mdhhs_only>=92 & los_unique_placement_mdhhs_only<=275 ~ 3,
    los_unique_placement_mdhhs_only>=275 & los_unique_placement_mdhhs_only<=549 ~ 4,
    los_unique_placement_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_mdhhs_only_grouped_bin = factor(los_unique_placement_mdhhs_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values


## use gather for line plot
# detention_los_overall_table <- detention_los_overall_grouped %>%
#   gather(year, value, `n_count`:`percent_within_bin`) %>% 
#   dplyr::rename(los_bins = los_unique_placement_detention_only_grouped_bin) %>% 
#   mutate(facility = 'Detention')
# 
# mdhhs_los_overall_table_missing_row <- tribble(
#   ~`los_bins`,   ~`year`, ~`value`,    ~`facility`,                 
#   "Less than 1 Month", "n_count",as.numeric(0.00), "MDHHS") 

## combine
# combined_los_overall_table_detention_only <- rbind(detention_los_overall_table,mdhhs_los_overall_table_missing_row) %>% 
#   filter(facility=="Detention")
  
# ggplot(data = detention_los_overall_grouped,
#             mapping = aes(x = los_unique_placement_detention_only_grouped_bin, y = percent_within_bin, fill = forcats::fct_rev(current_charge_classification_clean_factor_grouped))) + 
#   geom_bar(position = "dodge", stat = "identity") +
#   scale_fill_manual(values = rev(c("#007392","#0db4e4","#9ed4ef"))) +
#   scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
#                                            max(.75))) +
#   scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
#     theme(strip.text.x = element_text(face = "bold"),
#           legend.position = "top",
#         axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
#     labs(y = NULL, x = NULL,
#       caption = NULL,
#       title = NULL,
#       subtitle = NULL,
#       fill = NULL) +
#     coord_flip() +
#  guides(fill = guide_legend(reverse = TRUE,
#                              title.position = "top",
#                              label.position = "bottom",
#                              keywidth = 3,
#                              nrow = 1)) +
#   geom_label_repel(aes(label = scales::percent(as.numeric(percent_within_bin), accuracy = 1), group = forcats::fct_rev(current_charge_classification_clean_factor_grouped)),
#                   position = position_dodge(width = .9),
#                   direction = 'x',
#                   hjust = 0.75,
#                   label.padding = 0.1,
#                   box.padding = 0.1,
#                   fill = "white",
#                   color = "gray40",
#                   segment.color = NA,
#                   fontface = "bold",
#                   na.rm = TRUE,
#                   show.legend = FALSE)
```

<br><br>

#### PRE-DISPOSITION DETENTION: detention length of stay binned, 2016-2019 (ALL COUNTIES INCLUDED ASIDE FROM Mackinac & FELONY, MISDEMEANOR, AND STATUS OFFENSES GROUPED TOGETHER)

Overall Median: 14 days

```{r echo=FALSE,message=FALSE,warning=FALSE}
### 14 days as median
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only, na.rm = TRUE)

detention_los_overall_grouped <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
       filter(place_year%in%c(2016,2017,2018,2019),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown",
#          
#          ) %>%
#   dplyr::select(unique_placement_id,case_id,tc_sreport_court_jcl,place_type,place_type_desc,place_type_clean,case_year,county.x,current_charge_classification_clean_factor_grouped,current_offense,current_description,los_unique_placement_detention_only_grouped_bin,place_begin_date,place_end_date,dispo_date,adjudication_dt)
# 
# 
# ,
         !is.na(los_unique_placement_detention_only_grouped_bin)==TRUE) %>% 
  # dplyr::group_by(los_unique_placement_detention_only_grouped_bin) %>% 
  mutate(n_count = round(n_distinct(unique_placement_id), digits = 2)) %>% 
  # dplyr::ungroup() %>% 
  dplyr::group_by(los_unique_placement_detention_only_grouped_bin,n_count) %>% 
  dplyr::summarise(n_unique = n_distinct(unique_placement_id),
                   percent_within_bin = round(n_distinct(unique_placement_id)/n_count, digits = 2)) %>% 
  dplyr::ungroup() %>% 
  distinct(.,.keep_all=TRUE)


ggplot(data = detention_los_overall_grouped,
            mapping = aes(x = los_unique_placement_detention_only_grouped_bin, y = percent_within_bin, fill = forcats::fct_rev(los_unique_placement_detention_only_grouped_bin))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = rev(c("#7fc241","#d6df23","#007392","#eeed90","#0db4e4","#315c15"))) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
                                           max(.35))) +
  scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
 theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) + 
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
 guides(fill = FALSE) +
  # facet_grid(current_charge_classification_clean_factor_grouped ~ ., scales="free_y", space="free_y", switch="y") +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent_within_bin), accuracy = 1)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.1,
                  box.padding = 0.1,
                  fill = "white",
                  color = "gray40",
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)
```

<br><br>


## LOS By Offense/Oakland Separated

<br>

#### PRE-DISPOSITION DETENTION: detention length of stay by most serious charge (%), grouped by LOS bin, 2016-2019

Note: There is substantial variation by county. And there are only 8 counties included as Mackinac doesn't distinguish detention from residential in placement coding so they are excluded throughout

Medians (all counties including Oakland): 16 days for felony, 14 days for misdemeanor, 21 days for status

Medians (all counties excluding Oakland): 13 days for felony, 10 days for misdemeanor, 7.5 days for status

Medians (Oakland only): 43 days for felony, 32 days for misdemeanor, 37 days for status

```{r echo=FALSE,message=FALSE,warning=FALSE}
### Detention
detention_los_overall_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
    filter(place_year%in%c(2016,2017,2018,2019),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown",
         !is.na(los_unique_placement_detention_only_grouped_bin)==TRUE) %>% 
  summarise(n_count = n_distinct(unique_placement_id))

detention_los_overall_grouped <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
       filter(place_year%in%c(2016,2017,2018,2019),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown",
         !is.na(los_unique_placement_detention_only_grouped_bin)==TRUE) %>% 
  dplyr::group_by(los_unique_placement_detention_only_grouped_bin) %>% 
  mutate(n_count = round(n_distinct(unique_placement_id), digits = 2)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(current_charge_classification_clean_factor_grouped,los_unique_placement_detention_only_grouped_bin,n_count) %>% 
  dplyr::summarise(n_unique = n_distinct(unique_placement_id),
                   percent_within_bin = round(n_distinct(unique_placement_id)/n_count, digits = 2)) %>% 
  dplyr::ungroup() %>% 
  distinct(.,.keep_all=TRUE)

ggplot(data = detention_los_overall_grouped,
            mapping = aes(x = current_charge_classification_clean_factor_grouped, y = percent_within_bin, fill = forcats::fct_rev(current_charge_classification_clean_factor_grouped))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = rev(c("#007392","#0db4e4","#9ed4ef"))) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
                                           max(.75))) +
  scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
    theme(axis.text.x = element_text(size = 10, face="bold"),
       axis.ticks.length = unit(0, "cm"),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11,
                              margin=margin(r=10))) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
 guides(fill = FALSE) +
  facet_grid(los_unique_placement_detention_only_grouped_bin ~ ., scales="free_y", space="free_y", switch="y") +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent_within_bin), accuracy = 1), group = forcats::fct_rev(current_charge_classification_clean_factor_grouped)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.1,
                  box.padding = 0.1,
                  fill = "white",
                  color = "gray40",
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)
```

<br><br>

#### PRE-DISPOSITION DETENTION: detention length of stay by most serious charge (%), grouped by offense, 2016-2019 (ALL COUNTIES INCLUDED)

Medians (all counties including Oakland): 16 days for felony, 14 days for misdemeanor, 21 days for status

Medians (all counties excluding Oakland): 13 days for felony, 10 days for misdemeanor, 7.5 days for status

Medians (Oakland only): 43 days for felony, 32 days for misdemeanor, 37 days for status


```{r echo=FALSE,message=FALSE,warning=FALSE}
### calculate medians by offense severity

# ### 16 days for felony
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only[tcs_placements_charges_de_dup_pacc_pre_adj$current_charge_classification_clean_factor_grouped=="Felony"], na.rm = TRUE)
# 
# ### 14 days for misdemeanor
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only[tcs_placements_charges_de_dup_pacc_pre_adj$current_charge_classification_clean_factor_grouped=="Misdemeanor"], na.rm = TRUE)
# 
# ### 21 days for status
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only[tcs_placements_charges_de_dup_pacc_pre_adj$current_charge_classification_clean_factor_grouped=="Status"], na.rm = TRUE)

detention_los_overall_grouped <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
       filter(place_year%in%c(2016,2017,2018,2019),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown",
#          
#          ) %>%
#   dplyr::select(unique_placement_id,case_id,tc_sreport_court_jcl,place_type,place_type_desc,place_type_clean,case_year,county.x,current_charge_classification_clean_factor_grouped,current_offense,current_description,los_unique_placement_detention_only_grouped_bin,place_begin_date,place_end_date,dispo_date,adjudication_dt)
# 
# 
# ,
         !is.na(los_unique_placement_detention_only_grouped_bin)==TRUE) %>% 
  dplyr::group_by(current_charge_classification_clean_factor_grouped) %>% 
  mutate(n_count = round(n_distinct(unique_placement_id), digits = 2)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(current_charge_classification_clean_factor_grouped,los_unique_placement_detention_only_grouped_bin,n_count) %>% 
  dplyr::summarise(n_unique = n_distinct(unique_placement_id),
                   percent_within_bin = round(n_distinct(unique_placement_id)/n_count, digits = 2)) %>% 
  dplyr::ungroup() %>% 
  distinct(.,.keep_all=TRUE)


ggplot(data = detention_los_overall_grouped,
            mapping = aes(x = los_unique_placement_detention_only_grouped_bin, y = percent_within_bin, fill = forcats::fct_rev(los_unique_placement_detention_only_grouped_bin))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = rev(c("#7fc241","#d6df23","#007392","#eeed90","#0db4e4","#315c15"))) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
                                           max(.45))) +
  scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
    theme(axis.text.x = element_text(size = 10, face="bold"),
       axis.ticks.length = unit(0, "cm"),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11,
                              margin=margin(r=10))) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
 guides(fill = FALSE) +
  facet_grid(current_charge_classification_clean_factor_grouped ~ ., scales="free_y", space="free_y", switch="y") +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent_within_bin), accuracy = 1), group = forcats::fct_rev(current_charge_classification_clean_factor_grouped)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.1,
                  box.padding = 0.1,
                  fill = "white",
                  color = "gray40",
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)
```

<br><br>

#### PRE-DISPOSITION DETENTION: detention length of stay by most serious charge (%), grouped by offense, 2016-2019 (EXCLUDING OAKLAND COUNTY)

STATUS OFFENSE N: 27

```{r echo=FALSE,message=FALSE,warning=FALSE}
### calculate medians by offense severity

# ### 16 days for felony
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only[tcs_placements_charges_de_dup_pacc_pre_adj$current_charge_classification_clean_factor_grouped=="Felony"], na.rm = TRUE)
# 
# ### 14 days for misdemeanor
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only[tcs_placements_charges_de_dup_pacc_pre_adj$current_charge_classification_clean_factor_grouped=="Misdemeanor"], na.rm = TRUE)
# 
# ### 21 days for status
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only[tcs_placements_charges_de_dup_pacc_pre_adj$current_charge_classification_clean_factor_grouped=="Status"], na.rm = TRUE)

detention_los_overall_grouped <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
       filter(place_year%in%c(2016,2017,2018,2019),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         county.x!="OAKLAND",
         current_charge_classification_clean_factor_grouped!="Other/Unknown",
#          
#          ) %>%
#   dplyr::select(unique_placement_id,case_id,tc_sreport_court_jcl,place_type,place_type_desc,place_type_clean,case_year,county.x,current_charge_classification_clean_factor_grouped,current_offense,current_description,los_unique_placement_detention_only_grouped_bin,place_begin_date,place_end_date,dispo_date,adjudication_dt)
# 
# 
# ,
         !is.na(los_unique_placement_detention_only_grouped_bin)==TRUE) %>% 
  dplyr::group_by(current_charge_classification_clean_factor_grouped) %>% 
  mutate(n_count = round(n_distinct(unique_placement_id), digits = 2)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(current_charge_classification_clean_factor_grouped,los_unique_placement_detention_only_grouped_bin,n_count) %>% 
  dplyr::summarise(n_unique = n_distinct(unique_placement_id),
                   percent_within_bin = round(n_distinct(unique_placement_id)/n_count, digits = 2)) %>% 
  dplyr::ungroup() %>% 
  distinct(.,.keep_all=TRUE)


ggplot(data = detention_los_overall_grouped,
            mapping = aes(x = los_unique_placement_detention_only_grouped_bin, y = percent_within_bin, fill = forcats::fct_rev(los_unique_placement_detention_only_grouped_bin))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = rev(c("#7fc241","#d6df23","#007392","#eeed90","#0db4e4","#315c15"))) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
                                           max(.45))) +
  scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
    theme(axis.text.x = element_text(size = 10, face="bold"),
       axis.ticks.length = unit(0, "cm"),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11,
                              margin=margin(r=10))) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
 guides(fill = FALSE) +
  facet_grid(current_charge_classification_clean_factor_grouped ~ ., scales="free_y", space="free_y", switch="y") +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent_within_bin), accuracy = 1), group = forcats::fct_rev(current_charge_classification_clean_factor_grouped)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.1,
                  box.padding = 0.1,
                  fill = "white",
                  color = "gray40",
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)
```

<br><br>

#### PRE-DISPOSITION DETENTION: detention length of stay by most serious charge (%), grouped by offense, 2016-2019 (OAKLAND ONLY)

STATUS OFFENSE N: 59

```{r echo=FALSE,message=FALSE,warning=FALSE}
### calculate medians by offense severity

# ### 16 days for felony
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only[tcs_placements_charges_de_dup_pacc_pre_adj$current_charge_classification_clean_factor_grouped=="Felony"], na.rm = TRUE)
# 
# ### 14 days for misdemeanor
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only[tcs_placements_charges_de_dup_pacc_pre_adj$current_charge_classification_clean_factor_grouped=="Misdemeanor"], na.rm = TRUE)
# 
# ### 21 days for status
# median(tcs_placements_charges_de_dup_pacc_pre_adj$los_unique_placement_detention_only[tcs_placements_charges_de_dup_pacc_pre_adj$current_charge_classification_clean_factor_grouped=="Status"], na.rm = TRUE)

detention_los_overall_grouped <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
       filter(place_year%in%c(2016,2017,2018,2019),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         county.x=="OAKLAND",
         current_charge_classification_clean_factor_grouped!="Other/Unknown",
#          
#          ) %>%
#   dplyr::select(unique_placement_id,case_id,tc_sreport_court_jcl,place_type,place_type_desc,place_type_clean,case_year,county.x,current_charge_classification_clean_factor_grouped,current_offense,current_description,los_unique_placement_detention_only_grouped_bin,place_begin_date,place_end_date,dispo_date,adjudication_dt)
# 
# 
# ,
         !is.na(los_unique_placement_detention_only_grouped_bin)==TRUE) %>% 
  dplyr::group_by(current_charge_classification_clean_factor_grouped) %>% 
  mutate(n_count = round(n_distinct(unique_placement_id), digits = 2)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(current_charge_classification_clean_factor_grouped,los_unique_placement_detention_only_grouped_bin,n_count) %>% 
  dplyr::summarise(n_unique = n_distinct(unique_placement_id),
                   percent_within_bin = round(n_distinct(unique_placement_id)/n_count, digits = 2)) %>% 
  dplyr::ungroup() %>% 
  distinct(.,.keep_all=TRUE)


ggplot(data = detention_los_overall_grouped,
            mapping = aes(x = los_unique_placement_detention_only_grouped_bin, y = percent_within_bin, fill = forcats::fct_rev(los_unique_placement_detention_only_grouped_bin))) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = rev(c("#7fc241","#d6df23","#007392","#eeed90","#0db4e4","#315c15"))) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits=c(min(0), 
                                           max(.6))) +
  scale_x_discrete(labels = scales::wrap_format(18),limits = rev) +
    theme(axis.text.x = element_text(size = 10, face="bold"),
       axis.ticks.length = unit(0, "cm"),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11,
                              margin=margin(r=10))) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
 guides(fill = FALSE) +
  facet_grid(current_charge_classification_clean_factor_grouped ~ ., scales="free_y", space="free_y", switch="y") +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent_within_bin), accuracy = 1), group = forcats::fct_rev(current_charge_classification_clean_factor_grouped)),
                  position = position_dodge(width = .9),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.1,
                  box.padding = 0.1,
                  fill = "white",
                  color = "gray40",
                  segment.color = NA,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)
```

<br><br>


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#### **Post-Disposition**

# <br>
# 
# #### POST-DISPOSITION DETENTION: % of detentions by most serious offense, 2016-2020
# 
# SUBSTANTIAL VARIATION BY COUNTY (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)
                                 
### recode offense category into felony, misd, and status
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  mutate(current_charge_classification_clean_factor_grouped = case_when(
    current_charge_classification_clean_factor == "Felony, Person" | current_charge_classification_clean_factor == "Felony, Non-Person"  ~ 1,
    current_charge_classification_clean_factor == "Misdemeanor, Person" | current_charge_classification_clean_factor == "Misdemeanor, Non-Person"  ~ 2,
    current_charge_classification_clean_factor == "Status"  ~ 3,
    current_charge_classification_clean_factor == "Other/Unknown"  ~ 4,
    TRUE ~ as.numeric(NA)),
    current_charge_classification_clean_factor_grouped = factor(current_charge_classification_clean_factor_grouped,
         levels = c(1,2,3,4),
         labels = c("Felony","Misdemeanor","Status","Other/Unknown")))


tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  # group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_post_detention <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`,
            `Detention (N) w/ hearing` = n_distinct(unique_placement_id[place_type_clean=="Detention" & violation_hearing_flag==1]), 
            `Detention (%) w/ hearing` = n_distinct(unique_placement_id[place_type_clean=="Detention" & violation_hearing_flag==1])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  # complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0))
  # mutate(county_anonymous = paste0("County ", row_number())) %>% 
  # filter(current_charge_classification_clean_factor_grouped=="Status")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_post_detention,
            mapping = aes(x = reorder(current_charge_classification_clean_factor_grouped, `Detention (%)`), y = `Detention (%)`, fill = current_charge_classification_clean_factor_grouped)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.75))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        # axis.text.y=element_blank(),
        # axis.ticks.y=element_blank(),
        plot.caption = element_text(hjust = 0.5)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Detention (%)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)


# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\tcs_detention_placement_rate_county_incl_kalamazoo.png", tcs_detention_placement_rate_county_incl_kalamazoo, width = 8, height = 6)
```



```{r include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}
# <br><br>
# 
# #### POST-DISPOSITION DETENTION: % of detentions for which most serious charge is a misdemeanor offense, 2016-2020
# 
# BY COUNTY FOR INTERNAL DISCUSSION (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)
                                   
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(county.x,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) %>% 
  filter(current_charge_classification_clean_factor_grouped=="Misdemeanor")

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_pre_detention,
            mapping = aes(x = reorder(county_anonymous, `Detention (%)`), y = `Detention (%)`, fill = current_charge_classification_clean_factor_grouped), group = county_anonymous) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(1))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 1.15, y = .8, label = "Each bar represents the % of detentions\nfor misdemeanor offenses within one county", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.caption = element_text(hjust = 0.5)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Detention (%)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)


# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\mdhhs_tcs_ppt_02_17\\tcs_detention_placement_rate_county_incl_kalamazoo.png", tcs_detention_placement_rate_county_incl_kalamazoo, width = 8, height = 6)
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}

# <br><br>
# 
# #### POST-DISPOSITION DETENTION: detentions by most serious charge (%) and year of placement, 2016-2020
# 
# SUBSTANTIAL VARIATION BY COUNTY (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)
                                 
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(place_year) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_post_detention <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE,
         current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(place_year,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$place_year==place_year]) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`)) %>% 
  complete(place_year,current_charge_classification_clean_factor_grouped) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  # mutate(county_anonymous = paste0("County ", row_number())) %>% 
  group_by(place_year) %>% 
  # mutate(felony_percent = `Detention (%)`[current_charge_classification_clean_factor_grouped=="Felony"]) %>% 
  filter(current_charge_classification_clean_factor_grouped!="Other/Unknown") %>% 
  ungroup()

### plot
ggplot(data = tcs_placements_charges_de_dup_ind_place_grouped_post_detention, aes(y = `Detention (%)`, x = reorder(place_year,-place_year), fill = forcats::fct_rev(current_charge_classification_clean_factor_grouped))) + 
  geom_bar(stat = "identity", color = "gray80") +
  # scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = rev(c("#007392","#0db4e4","#9ed4ef"))) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
    geom_label(
    aes(
      y = `Detention (%)`,
      label = scales::percent(`Detention (%)`,accuracy=1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 5,
    colour = "black",
    show.legend = FALSE
  ) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = "Each bar represents one year.\n'Other/Unknown' offenses excluded (<1% of sample)",
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

# ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\Iowa Revocation Reduction\\Work Products\\Presentations\\r_viz\\supervision_status_by_district_2020.png", supervision_status_by_district_2020, width = 9, height = 6.5) 
```

<br><br>

## County-level Descriptives, Tables

Note: All %'s are within county in the following tables.

<br>

#### **Pre-Disposition**

<br>

#### PRE-DISPOSITION DETENTION: Individual Placements by Charge Classification: Counts and Percentages, 2016-2020

BY COUNTY FOR INTERNAL DISCUSSION (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)

```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = round(n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]*100, digits = 1)) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`))

### print table via kableextra
kable(tcs_placements_charges_de_dup_ind_place_grouped_pre_detention, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```


```{r eval=FALSE,include=FALSE,warning=FALSE, message=FALSE}
### PRE-ADJUDICATION Median LOS by Charge -- Detention, 2016-2018 (individual placements)

tcs_placements_charges_median_los_detention_pre <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(case_year%in%c(2016,2017,2018),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean=="Detention") %>% ### only looking at earlier years because we don't want to artificially deflate the median
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (Sample N)` = n_distinct(unique_placement_id[!is.na(los_unique_placement_detention_only)==TRUE & los_unique_placement_detention_only>-1]),
            `Detention (Days)` = round(median(los_unique_placement_detention_only[los_unique_placement_detention_only>-1], na.rm = TRUE), digits = 0)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_median_los_detention_pre, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
# #### **Post-Disposition**
# 
# <br>
# 
# #### POST-DISPOSITION: Individual Placements by Charge Classification: Counts and Percentages, 2016-2020
# 
# BY COUNTY FOR INTERNAL DISCUSSION (only 8 counties here; mackinac doesn't distinguish detention from residential in placement coding)
                                   
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  group_by(county.x) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_post_detention <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor_grouped)==TRUE,
         place_type_clean%in%c("Detention"),
         !is.na(county.x)==TRUE) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(county.x,current_charge_classification_clean_factor_grouped) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = round(n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`[tcs_placements_charges_de_dup_denom$county.x==county.x]*100, digits = 1)) %>% 
  ungroup() %>% 
  filter(!is.na(`Detention (%)`))

### print table via kableextra
kable(tcs_placements_charges_de_dup_ind_place_grouped_post_detention, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

## Next Steps

<br>

**Next Steps**

* How to treat substantial county-level variation, particularly around detention of youth with status offenses? Especially with LOS analysis and outsized impact of Oakland county.

<br><br>
