---
title: "jj_mi_mdhhs_ccf"
author: "Andrew Byrum"
date: "November 2021"
output: 
    html_document:
        df_print: paged
        toc: true
        toc_float: true
---

**CCF data points:** 

* County
* Month
* Section (type of placement; family foster care, institutional care, and independent living are considered *out-of-home* while basic grant and in home are considered *in home* -- however, youth placed out of home can still receive programming labelled as in-home)
* Subsection (description of section; only populated for family foster care and some institutional care records -- for family foster care, include 'A. Court or Tribal Supervised', 'B. Private Agency - In-State', and 'C. Private Agency - Out-Of-State' and for institutional care, includes either 'A. Another County's Institution (Court or MDHHS)' or missing data/blanks)
* Heading (features programming details for in home sections -- however, there is not consistency is coding/naming conventions)
* Total children (unique by youth and placement; two placements for one child would count twice towards 'total children')
* Monthly children (unique youth placed within a given month -- by county, section, subsection)
* Days care provided: reliability TBD
* Adjusted reimbursed amount: amount/claim on which MDHHS bases 50% reimbursement (i.e. it's double what MDHHS actually paid) -- except...

<br>

**What's possible with CCF data for FY 2020 (prior data has mix of abuse/neglect cases and jj cases):**

* Within fiscal year: total children by section/subsection by county by month

* Unique children by month by placement

* 50%

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","tidylog","distill","formattable")
```

```{r include=FALSE}
### import ccf fy 2016
ccf_fy2016 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2016_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2016")

### import ccf fy 2017
ccf_fy2017 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2017_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2017")

### import ccf fy 2018
ccf_fy2018 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2018_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2018")

### import ccf fy 2019
ccf_fy2019 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2019_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2019")

### import ccf fy 2020
ccf_fy2020 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2020_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2020")

### stack all ccf files -- columns all align
df_ccf_stacked_2016_2020 <- rbind(ccf_fy2016,ccf_fy2017,ccf_fy2018,ccf_fy2019,ccf_fy2020) %>% 
  group_by_all() %>% 
  mutate(dup_count = n()) %>% 
  ungroup() %>% 
  distinct(., .keep_all = TRUE) %>% ################### I'M TEMPORARILY DE-DUPING HERE ON PURE DUPLICATES (DUPS ACROSS ALL COLUMNS); THIS MAY CHANGE DEPENDING ON WHAT TEDDY SAYS, HOWEVER 
  mutate(heading_total_flag = ifelse(str_detect(heading,"(?i)total"),1,0)) %>% ### flag rows where 'heading' has 'total' in it
  filter(section != "Totals",
         heading_total_flag==0) ### Teddy said to ignore 'Totals' sections; also removing all headings with 'total' -- these appear to simply tally up youth counts and reimbursement totals for the month by section? Confirm with Teddy. 
```

```{r include=FALSE,message=FALSE,warning=FALSE}
df_ccf_stacked_2020_only_cleaned <- df_ccf_stacked_2016_2020 %>%
  filter(ccf_fy=="2020") %>% ### just using 2020 for now -- double checking 2019 with Teddy
  mutate(out_of_home_flag = ifelse(section %in% c("Family Foster Care","Independent Living","Institutional Care","Court Operated Facility","County/Court Operated Facilities"), 1,0)) %>%  ### flag out-of-home facilities based on call with Teddy' -- he didn't mentioned either Court Operated Facility or County/Court Operated Facilities explicitly but instead included as part of institutional care so I still included (also are clearly out-of-home placements)
  mutate(section_clean = ifelse(section %in% c("Court Operated Facility","County/Court Operated Facilities"),"Institutional Care", section),
         section_clean = ifelse(section == "In-Home Care","In Home", section_clean))

```

## Tables

### CCF Total Adjusted Reimbursement Amount by Section, FY 2020 
```{r echo=FALSE,message=FALSE,warning=FALSE}
df_ccf_stacked_2020_total_amounts <- df_ccf_stacked_2020_only_cleaned %>% 
  group_by(section_clean) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

df_ccf_stacked_2020_total_amounts_overall <- df_ccf_stacked_2020_only_cleaned %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  mutate("CCF Section" = "Overall")

### combine tables for kable
df_ccf_stacked_2020_total_amounts_table <- rbind(df_ccf_stacked_2020_total_amounts,df_ccf_stacked_2020_total_amounts_overall)

### print table via kableextra
kable(df_ccf_stacked_2020_total_amounts_table[c(1,3,2,4,5,6),], format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") %>% 
  row_spec(6, bold = TRUE) %>% 
  pack_rows("In Home*", 1, 2, label_row_css = "background-color: #666; color: #fff;") %>% 
  pack_rows("Out of Home", 3, 5, label_row_css = "background-color: #666; color: #fff;") %>% 
  pack_rows("", 6, 6, label_row_css = "background-color: #666; color: #fff;") %>% 
  footnote(symbol = "In-home programming is also available, in some situations, to youth in out-of-home placements")
```

<br><br>

### CCF Total Adjusted Reimbursement Amount by Section and Subsection, FY 2020 

Note: Most subsection data, 70%, are missing across sections (most populated subsections appear to be for family foster care)
```{r echo=FALSE,message=FALSE,warning=FALSE}
### recode NA as "Missing" for analysis of subsection as we want to report out everything including the NAs
df_ccf_stacked_2020_only_cleaned_subsection_recode <- df_ccf_stacked_2020_only_cleaned %>% 
  mutate(subsection = ifelse(is.na(subsection)==TRUE, "Missing", subsection))

### basic grant, overall
df_ccf_basic_grant_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Basic Grant") %>% 
  group_by(section_clean) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

### basic grant, by subsection
df_ccf_basic_grant_subsection <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Basic Grant") %>% 
  group_by(subsection) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = subsection)

### combine tables 
df_ccf_basic_grant_final <- rbind(df_ccf_basic_grant_overall,df_ccf_basic_grant_subsection)

### in home, overall
df_ccf_in_home_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="In Home") %>% 
  group_by(section_clean) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

### in home, by subsection
df_ccf_in_home_subsection <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="In Home") %>% 
  group_by(subsection) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = subsection)

### combine tables 
df_ccf_in_home_final <- rbind(df_ccf_in_home_overall,df_ccf_in_home_subsection)

### family foster care, overall
df_ccf_foster_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Family Foster Care") %>% 
  group_by(section_clean) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

### family foster care, by subsection
df_ccf_foster_subsection <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Family Foster Care") %>% 
  group_by(subsection) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = subsection)

### combine tables 
df_ccf_foster_final <- rbind(df_ccf_foster_overall,df_ccf_foster_subsection)

### institutional care, overall
df_ccf_institution_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Institutional Care") %>% 
  group_by(section_clean) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

### institutional care, by subsection
df_ccf_institution_subsection <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Institutional Care") %>% 
  group_by(subsection) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = subsection)

### combine tables 
df_ccf_institution_final <- rbind(df_ccf_institution_overall,df_ccf_institution_subsection)

### independent living, overall
df_ccf_independent_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Independent Living") %>% 
  group_by(section_clean) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

### independent living, by subsection
df_ccf_independent_subsection <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Independent Living") %>% 
  group_by(subsection) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = subsection)

### combine tables 
df_ccf_independent_final <- rbind(df_ccf_independent_overall,df_ccf_independent_subsection)


### overall 
df_ccf_stacked_2020_total_amounts_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  mutate("CCF Section" = "Overall")

### combine tables for kable
df_ccf_stacked_2020_subsection_table <- rbind(df_ccf_basic_grant_final,df_ccf_in_home_final,df_ccf_foster_final,df_ccf_institution_final,df_ccf_independent_final,df_ccf_stacked_2020_total_amounts_overall)

### print table via kableextra
kable(df_ccf_stacked_2020_subsection_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") %>% 
  row_spec(15, bold = TRUE) %>% 
  pack_rows("In Home*", 1, 4, label_row_css = "background-color: #666; color: #fff;") %>% 
  pack_rows("Out of Home", 5, 14, label_row_css = "background-color: #666; color: #fff;") %>% 
  pack_rows("", 15, 15, label_row_css = "background-color: #666; color: #fff;") %>% 
  footnote(symbol = "In-home programming is also available, in some situations, to youth in out-of-home placements") %>% 
  add_indent(c(2,4,6,7,8,9,11,12,14))
```

<br><br>

### Raw 'Heading'/Programming Categories for 'In-Home' Programming 

Note: 'In-Home' programming is the only CCF section for which there is near-complete data. However, as you can see, there is not consistency is coding/naming conventions.
```{r echo=FALSE,message=FALSE,warning=FALSE}
### in home, by heading
df_ccf_in_home_heading <- df_ccf_stacked_2020_only_cleaned %>% 
  filter(section_clean=="In Home") %>% 
  group_by(heading) %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Heading/Programming" = heading)

### in home, by heading
df_ccf_in_home_overall <- df_ccf_stacked_2020_only_cleaned %>% 
  filter(section_clean=="In Home") %>% 
  summarize(total_adj_reimburse_amount = scales::dollar(sum(adjusted_reimbursed_amt)),
            unique_children_placements = sum(total_children[ccf_month_code=="SEPTEMBER"]), ### the ccf fiscal year ends in september so we should use the september count
            total_children_placements_month_not_unique = sum(monthly_children),
            total_adj_reimburse_per_unique_youth_placement = scales::dollar(sum(adjusted_reimbursed_amt)/unique_children_placements),
            total_adj_reimburse_per_total_youth_month_placements = scales::dollar(sum(adjusted_reimbursed_amt)/total_children_placements_month_not_unique)) %>% 
  ungroup() %>% 
  dplyr::mutate("CCF Heading/Programming" = "Overall")

### combine tables 
df_ccf_in_home_heading_table <- rbind(df_ccf_in_home_heading,df_ccf_in_home_overall)

### print table via kableextra
kable(df_ccf_in_home_heading_table, format.args = list(big.mark = ","), align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") %>% 
  row_spec(287, bold = TRUE)
```

<br><br>

### CCF Out-of-Home Adjusted Reimbursement Amount by Month, FY 2020 (covid impact?) (only looking at monthly totals for out-of-home financial data -- Teddy said that some in-home programming doesn't charge on a monthly basis, but instead on an annual basis. in the data, this appears as just one lump sum in one month while the other 11 months show $0)
```{r echo=FALSE,message=FALSE,warning=FALSE}
df_ccf_stacked_2020_total_amounts_month <- df_ccf_stacked_2020_only_cleaned %>% 
  filter(out_of_home_flag==1) %>% 
  group_by(section_clean) %>% 
  summarize(`October 2019` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="OCTOBER"])),
            `November 2019` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="NOVEMBER"])),
            `December 2019` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="DECEMBER"])),
            `January 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="JANUARY"])),
            `February 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="FEBRUARY"])),
            `March 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="MARCH"])),
            `April 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="APRIL"])),
            `May 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="MAY"])),
            `June 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="JUNE"])),
            `July 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="JULY"])),
            `August 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="AUGUST"])),
            `September 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="SEPTEMBER"]))) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

df_ccf_stacked_2020_total_amounts_month_overall <- df_ccf_stacked_2020_only_cleaned %>% 
  filter(out_of_home_flag==1) %>% 
  summarize(`October 2019` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="OCTOBER"])),
            `November 2019` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="NOVEMBER"])),
            `December 2019` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="DECEMBER"])),
            `January 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="JANUARY"])),
            `February 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="FEBRUARY"])),
            `March 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="MARCH"])),
            `April 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="APRIL"])),
            `May 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="MAY"])),
            `June 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="JUNE"])),
            `July 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="JULY"])),
            `August 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="AUGUST"])),
            `September 2020` = scales::dollar(sum(adjusted_reimbursed_amt[ccf_month_code=="SEPTEMBER"]))) %>% 
  mutate("CCF Section" = "Overall")

### combine tables for kable
df_ccf_stacked_2020_total_amounts_month_table <- rbind(df_ccf_stacked_2020_total_amounts_month,df_ccf_stacked_2020_total_amounts_month_overall)

### print table via kableextra
kable(df_ccf_stacked_2020_total_amounts_month_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") %>% 
  row_spec(4, bold = TRUE)
```

<br><br>

## Maps 
```{r include=FALSE}
### pull census/acs data via tidycensus package

### set census api key via tidycensus package
### this allows us to pull census/acs data via the tidycensus package
tidycensus::census_api_key("1ba246a0db6cfbd596219470af425fe932cf064b", install = TRUE, overwrite = TRUE)
readRenviron("~/.Renviron")

### read in county-level cdc/acs juvenile population estimates, split by race/ethnicity and sex, for base juvenile population rate calculations
mi_age_10_17_sex_race_final <- readr::read_delim("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Ezapop\\ezapop_10_17_race_eth_sex_mi.txt" , delim = "|")

### pull other acs/census data for additional context/mapping, if wanted

### overall population
mi_overall_pop <- tidycensus::get_acs(geography = "County",
                                              state = "MI",
                                              variables = "B01003_001",
                                              geometry = FALSE) %>%
  clean_names() %>%
  dplyr::select(geoid,name,estimate) %>%
  dplyr::rename(estimate_total_pop = estimate)

### weighted estimate of percentage of census tracts residents living below federal poverty threshold
mi_poverty_status <- tidycensus::get_acs(geography = "County", 
                                              state = "MI",
                                              variables = "S1701_C03_001", 
                                              geometry = FALSE) %>% 
  clean_names() %>% 
  dplyr::select(geoid,estimate) %>% 
  dplyr::rename(estimate_below_poverty = estimate)

### weighted estimate of income
mi_median_income <- tidycensus::get_acs(geography = "County", 
                                             state = "MI",
                                             variables = "S1901_C01_012", 
                                             geometry = FALSE) %>% 
  clean_names() %>% 
  dplyr::select(geoid,estimate) %>% 
  dplyr::rename(estimate_income = estimate)


### weighted estimate of percentage of race from 2010 census; couldn't find overall race estimates from 2018 ACS
### pulled estimated counts and constructed percent estimate
### these are the ids of race variables that we want to pull 
race_vars <- c(estimate_white = "P005003",
               estimate_black = "P005004",
               estimate_asian = "P005006",
               estimate_hispanic = "P004003")

mi_race_2010 <- tidycensus::get_decennial(geography = "County", 
                                               state = "MI",
                                               variables = race_vars,
                                               summary_var = "P001001",
                                               geometry = FALSE) %>% 
  clean_names() %>% 
  mutate(estimate = (value/summary_value)*100) ###create percent estimate from estimated counts

### pivot race file to be wide and unique by census tract 
mi_race_2010 %<>%
  dplyr::select(geoid,variable,estimate) %>% 
  spread(variable,estimate, fill = NA) 
```

```{r include=FALSE}
### join all acs variables together in one file 
mi_acs_census_county <- left_join(mi_poverty_status, mi_median_income, by="geoid")

mi_acs_census_county <- left_join(mi_acs_census_county, mi_overall_pop, by="geoid")

mi_acs_census_county <- left_join(mi_acs_census_county, mi_race_2010, by="geoid")
```

```{r include=FALSE}
### read in county-level iowa data to create county,state, geoid crosswalk with acs/census data 
### this is the official iowa county shapefile, obtained here: https://www.census.gov/geographies/mapping-files/time-series/geo/tiger-line-file.html 
### this is not used for mapping, however, hence we remove geography below; it's just a crosswalk across county name, geoid, and county fip code
mi_geo_county <- read_sf("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\Geospatial_Mapping\\US County Geo Data\\tl_2019_us_county\\tl_2019_us_county.shp") %>%
  clean_names() %>% 
  filter(statefp=="26") %>% ### filter on michigan using state fips code (26)
  dplyr::select(geoid, county_name_short=name, county_fip=countyfp) 

### convert to dataframe and remove geometry -- this will not be 
mi_geo_county <- as.data.frame(mi_geo_county) %>%
    dplyr::select(-(geometry))

```

```{r include=FALSE}
### CCF Total Adjusted Reimbursement Amount by section and county, FY 2020 
df_ccf_stacked_2020_total_amounts_map <- df_ccf_stacked_2020_only_cleaned %>% 
  group_by(agency_name) %>% 
  summarize(total_adj_reimburse_per_total_youth_month_placements_basic_grant = scales::dollar(sum(adjusted_reimbursed_amt[section_clean=="Basic Grant"])/sum(monthly_children[section_clean=="Basic Grant"])),
            total_adj_reimburse_per_total_youth_month_placements_in_home = scales::dollar(sum(adjusted_reimbursed_amt[section_clean=="In Home"])/sum(monthly_children[section_clean=="In Home"])),
            total_adj_reimburse_per_total_youth_month_placements_family_foster_care = scales::dollar(sum(adjusted_reimbursed_amt[section_clean=="Family Foster Care"])/sum(monthly_children[section_clean=="Family Foster Care"])),
            total_adj_reimburse_per_total_youth_month_placements_inst_care = scales::dollar(sum(adjusted_reimbursed_amt[section_clean=="Institutional Care"])/sum(monthly_children[section_clean=="Institutional Care"])),
            total_adj_reimburse_per_total_youth_month_placements_ind_living = scales::dollar(sum(adjusted_reimbursed_amt[section_clean=="Independent Living"])/sum(monthly_children[section_clean=="Independent Living"]))) %>% 
  ungroup() %>% 
  dplyr::rename(county_name_short = agency_name)
```

```{r include=FALSE}
### merge county code/geoid crosswalk to acs data
mi_acs_census_county_crosswalk <- inner_join(mi_acs_census_county,mi_geo_county,by = "geoid")

### county-level estimates

### clean up acs/census estimates for eventual use as map labels
mi_acs_census_county_crosswalk_full <- mi_acs_census_county_crosswalk %>% 
    group_by(county_name_short) %>% 
    summarize(estimate_total_pop = sum(estimate_total_pop, na.rm=TRUE),
              estimate_below_poverty_mean = round(mean(estimate_below_poverty, na.rm=TRUE),digits = 1),
              estimate_income_median = round(mean(estimate_income, na.rm=TRUE),digits = 1),
              estimate_asian_mean = round(mean(estimate_asian, na.rm=TRUE),digits = 1),
              estimate_black_mean = round(mean(estimate_black, na.rm=TRUE),digits = 1),
              estimate_hispanic_mean = round(mean(estimate_hispanic, na.rm=TRUE),digits = 1),
              estimate_white_mean = round(mean(estimate_white, na.rm=TRUE),digits = 1)) %>% 
    ungroup() 

### calculate rates using population estimates by county from 2019 American Community Survey
mi_acs_census_county_no_geo_rates <- mi_acs_census_county_crosswalk_full %>% 
  left_join(df_ccf_stacked_2020_total_amounts_map, by = "county_name_short") 
```

```{r include=FALSE}
# options(java.parameters = "- Xmx1024m")

### read in iowa county-level shape file    
mi_county_shape <- read_sf("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\Geospatial_Mapping\\US County Geo Data\\tl_2019_us_county\\tl_2019_us_county.shp") %>%
  clean_names() %>% 
  filter(statefp=="26") %>% 
  dplyr::rename(county_name_short=name, 
                county_fip=countyfp)


### merge county shapefile to acs, census, and iowa data to attach geography and render the file map-able
mi_acs_census_county_geo <- merge(mi_county_shape, mi_acs_census_county_no_geo_rates, by = "county_name_short") 
```

```{r include=FALSE}
### define color palletes for each layer in all interactive maps

### define pallete for pre_to_post_supervision_count_change at district level
pal_percent_supervision_rate_change_district <- colorQuantile(palette = c("#00475d","#007392","#0db4e4","#9ed4ef"), domain = mi_acs_census_county_geo$pre_to_post_supervision_count_change, n = 4, reverse = TRUE) ### use reverse to invert colors 

### define pallete for pre_to_post_covid_rate_change at district level
pal_percent_revocation_rate_change_district <- colorQuantile(palette = c("#00475d","#007392","#0db4e4","#9ed4ef"), domain = mi_acs_census_county_geo$pre_to_post_covid_rate_change, n = 4, reverse = TRUE) ### use reverse to invert colors 

### define pallete for pre_to_post_supervision_count_change at county level
pal_percent_supervision_rate_change_county <- colorQuantile(palette = c("#00475d","#007392","#0db4e4","#9ed4ef"), domain = mi_acs_census_county_geo$pre_to_post_supervision_count_change, n = 3, reverse = TRUE) ### use reverse to invert colors 

### define pallete for pre_to_post_covid_rate_change at county level
pal_percent_revocation_rate_change_county <- colorQuantile(palette = c("#00475d","#007392","#0db4e4","#9ed4ef"), domain = mi_acs_census_county_geo$pre_to_post_covid_rate_change, n = 4, reverse = TRUE) ### use reverse to invert colors 
```


### Interactive Map 

<br>

#### % Change in Supervisions Started and Revocation Rate by Judicial District 

This map plots change in active supervision cases and revocation rate (revocations per active supervision cases) per month from 2019 (March 2019 to February 2020) to 2020 (March 2020 to June 2021). Toggle between the two layers using the buttons in the top right corner. 

You can also hover over each district to learn more--including the exact change in supervision caseload and revocation rate, the overall district population size, as well as the poverty rate, and overall race/ethnicity breakdown.

<br>

```{r echo=FALSE, warning=FALSE, message=FALSE}
### create label that will pop-up when user hovers over each county; call this label for each polygon layer added because we want this to appear with each layer
label_acs_census_county_popup <- paste0('<strong>',"District ", mi_acs_census_county_geo$judicial_district,'</strong>',"<br/>", "<br/>", 
                                        '<strong>',"% Change in Supervision Cases and Revocation Rates (2019-2020)",'</strong>',"<br/>",
                                         "District Supervision Cases: ", format(round(mi_acs_census_county_geo$pre_to_post_supervision_count_change, digits=0), big.mark=",", scientific=FALSE),"%","<br/>", "<br/>",
                                         "District Revocation Rate: ", format(round(mi_acs_census_county_geo$pre_to_post_covid_rate_change, digits=0), big.mark=",", scientific=FALSE),"%","<br/>", "<br/>",
                    '<strong>',"Population, SES, and Race/Ethnicity Data (from 2019 ACS)",'</strong>',"<br/>",
                                        "Overall Population: ",format(round(mi_acs_census_county_geo$estimate_total_pop, digits=0), big.mark=",", scientific=FALSE),"<br/>",
                                        "Poverty Rate: ",mi_acs_census_county_geo$estimate_below_poverty_mean,"%","<br/>",
                                        "Asian Population: ",mi_acs_census_county_geo$estimate_asian_mean,"%","<br/>",
                                        "Black Population: ",mi_acs_census_county_geo$estimate_black_mean,"%","<br/>",
                                        "Hispanic Population: ",mi_acs_census_county_geo$estimate_hispanic_mean,"%","<br/>",
                                        "White Population: ",mi_acs_census_county_geo$estimate_white_mean,"%") %>%
  lapply(htmltools::HTML)

### create legend labels for all mapped layers
label_supervision_rate <- c("-53.1% to -24.8%","-24.8% to 9.9%","9.9% to 17.4%","17.4%+","NA")

label_revocation_rate <- c("-56.5% to -49.3%","-49.3% to -44.6%","-44.6% to -28.9%","-28.9%+","NA")

### map with leaflet 
mi_acs_census_county_geo %>%
    sf::st_transform(crs = "+init=epsg:4326") %>%
    leaflet(height = 600, width = 900) %>%
  addProviderTiles(provider = "CartoDB.Positron",
                   options = providerTileOptions(minZoom = 7, maxZoom = 9)) %>%
  addPolylines(color = "Black",
               stroke = FALSE,
               opacity = .01,
               weight = .01) %>%
  addPolygons(weight = 1,
              color = "Black",
              fillColor = ~ pal_percent_supervision_rate_change_district(mi_acs_census_county_geo$pre_to_post_supervision_count_change),
                fillOpacity = 0.7,
                label = ~ label_acs_census_county_popup,
                labelOptions = labelOptions(direction = "auto"),
               highlightOptions  = highlightOptions(
                opacity = 1, 
                weight = 2, 
                fillOpacity = 1,
                bringToFront = TRUE, 
                sendToBack = FALSE),
              group = "% Change in Active District Supervision Cases") %>%
    addPolygons(weight = 1,
              color = "Black",
              fillColor = ~ pal_percent_revocation_rate_change_district(mi_acs_census_county_geo$pre_to_post_covid_rate_change),
                fillOpacity = 0.7,
                label = ~ label_acs_census_county_popup,
                labelOptions = labelOptions(direction = "auto"),
               highlightOptions  = highlightOptions(
                opacity = 1,
                weight = 2,
                fillOpacity = 1,
                bringToFront = TRUE,
                sendToBack = FALSE),
              group = "% Change in District Revocation Rate") %>%
    addPolylines(data = mi_acs_census_county_geo,
                 color = "Black",
               opacity = .5,
               weight = .5) %>%
    addLegend("topleft",
              pal = pal_percent_supervision_rate_change_district,
              values = ~ mi_acs_census_county_geo$pre_to_post_supervision_count_change,
              group = "% Change in Active District Supervision Cases",
              title = "% Change in Active District Supervision Cases",
              opacity = 2,
              labFormat = function(type, cuts, p) {paste0(label_supervision_rate)}) %>% 
  addLegend("topleft",
          pal = pal_percent_revocation_rate_change_district,
          values = ~ mi_acs_census_county_geo$pre_to_post_covid_rate_change,
          group = "% Change in District Revocation Rate",
          title = "% Change in District Revocation Rate",
          opacity = 2,
          labFormat = function(type, cuts, p) {paste0(label_revocation_rate)}) %>%
addLayersControl(
  baseGroups = c("% Change in Active District Supervision Cases","% Change in District Revocation Rate"),
  position = "topright",
  options = layersControlOptions(collapsed = FALSE)) %>%
  htmlwidgets::onRender("
    function(el, x) {
      var updateLegend = function () {
          var selectedGroup = document.querySelectorAll('input:checked')[0].nextSibling.innerText.substr(1);

          document.querySelectorAll('.legend').forEach(a => a.hidden=true);
          document.querySelectorAll('.legend').forEach(l => {
            if (l.children[0].children[0].innerText == selectedGroup) l.hidden=false;
          });
      };
      updateLegend();
      this.on('baselayerchange', e => updateLegend());
    }") ### the javascript specified after htmlwidgets attaches each legend to the selected layer; this is quite temperamental. Doesn't work with multiple interactive maps and doesn't work with tabs if isn't in first tab
```

<br><br>

### Static Map

<br>

```{r include=FALSE}
### set constants for static plots (this may need to change in final rmd)
default_font_color <- "#4e4d47"
default_font_family <- "Arial"

### define options for saving plots
knitr::opts_chunk$set(
    out.width = "115%",
    dpi = 500,
    fig.width = 10,
    fig.height = 7.5,
    strip.white = T,
    dev = "png")
```

```{r include=FALSE}
### create static map theme (based on https://timogrossenbacher.ch/2019/04/bivariate-maps-with-ggplot2-and-sf/)
theme_map <- function(...) {
  theme_minimal() +
  theme(
    text = element_text(family = default_font_family,
                        color = default_font_color),
    # remove all axes
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    # add a subtle grid
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # borders and margins
    plot.margin = unit(c(.5, .5, .2, .5), "cm"),
    panel.border = element_blank(),
    panel.spacing = unit(c(-.1, 0.2, .2, 0.2), "cm"),
    # titles
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 9, hjust = 0,
                               color = default_font_color),
    plot.title = element_text(size = 15, hjust = 0.5,
                              color = default_font_color),
    plot.subtitle = element_text(size = 10, hjust = 0.5,
                                 color = default_font_color,
                                 margin = margin(b = -0.1,
                                                 t = -0.1,
                                                 l = 2,
                                                 unit = "cm"),
                                 debug = F),
    # captions
    plot.caption = element_text(size = 7,
                                hjust = .5,
                                margin = margin(t = 0.2,
                                                b = 0,
                                                unit = "cm"),
                                color = "#939184"),
    ...
  )
}
```


#### % Change in Revocation Rate by Judicial District, 2019-2020

This map plots change in revocation rate (revocations per active supervision cases) per month from 2019 (March 2019 to February 2020) to 2020 (March 2020 to June 2021)

```{r echo=FALSE, warning=FALSE}
### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- mi_acs_census_county_geo %>%
  pull(pre_to_post_covid_rate_change) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_revocation_rate <- c("-28.9%+","-44.6% to -28.9%","-49.3% to -44.6%","-56.5% to -49.3%")

### create a new variable with the specified quantiles
mi_acs_census_county_geo %<>%
  mutate(pre_to_post_covid_rate_change_quartile = cut(-pre_to_post_covid_rate_change,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_revocation_rate,
                               include.lowest = T)) 

### map via ggplot 
ggplot(
  # define main data source
  data = mi_acs_census_county_geo
) +
  # use the "alpha hack" (as the "fill" aesthetic is already taken)
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  # use thin white stroke for municipality borders
  geom_sf(
    mapping = aes(
      fill = pre_to_post_covid_rate_change_quartile
      ),
    color = "white",
    size = 0.1
  ) +
 scale_fill_manual(
    values = c("#00475d","#007392","#0db4e4","#9ed4ef"),
    name = "% Change in Rate",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use thicker white stroke for borders
  geom_sf(
    data = iowa_acs_census_district_geo,
    fill = "transparent",
    color = "white",
    size = 1.25
  )  +
  geom_sf(
    data = iowa_county_shape,
    fill = "transparent",
    color = "white",
    size = 0.3
  )  +
  # add titles
  labs(x = NULL,
       y = NULL,
       title = "% Change in Revocation Rate",
         subtitle = "2019 to 2020") +
  # add theme
  theme_map()
```

<br><br>

## Questions/Notes

* Duplicate entries interpretation? For example:
```{r echo=FALSE,message=FALSE,warning=FALSE}
### stack all ccf files -- columns all align
df_ccf_stacked_2016_2020_dup_example <- rbind(ccf_fy2016,ccf_fy2017,ccf_fy2018,ccf_fy2019,ccf_fy2020) %>% 
  get_dupes() %>% 
  filter(agency_name=="Alcona County",
         ccf_month_code== "MARCH",
         ccf_fy=="2016") %>% 
  arrange(section,subsection,heading)
  
### print table via kableextra
kable(df_ccf_stacked_2016_2020_dup_example, format.args = list(big.mark = ","), align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") 
```

* Follow-up on % of in-home programming that could be funded outside of CCF. Either way, need to keep in mind that in-home costs may not represent actual programming costs but instead the amount contributed by the CCF (according to Teddy, other funding may include: scao, community mental health/cmh, and other grants)

* Follow-up on usability of 2019 data for separated jj and a/n placement data -- given difficulty of generalizing from 2020

* Re-code "Court Operated Facility" and "County/Court Operated Facilities" as institutional care? Only a few counties appear to code these in 'section'? Same for "In-Home Care" and "In Home"?

* Removed all headings with 'total' -- these appear to simply tally up youth counts and reimbursement totals for the month by section? Confirm with Teddy. 

* Confirm fiscal year interpretation (CCF FY 2020: October 2019 to September 2020?)

* Two state jj facilities (Bay Pines and Shawono Center) not included in out-of-home placements -- Kelly confirmed Teddy's take on this, but subsection category for out-of-county placement is called "A. Another County's Institution (Court or MDHHS)"?

* Days care provided: is this reliable? i see numbers larger than the days in a given month

* Most subsection data, 70%, are missing across sections (most populated subsections appear to be for family foster care)

* Reminder of exception to 50% reimbursement rule? 

<br>