---
title: "tcs_county_data_placement_charge_only_output"
author: "Andrew Byrum"
date: "2/24/2022"
output: html_document
---

# {.tabset .tabset-fade .tabset-pills}
```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","tidylog","csgjcr","psych")
````


```{r include=FALSE}
### set sharepoint path using csgjcr::csg_sp_path function
sharepoint_tcs_data_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Raw/Courts/JIS/TCS")

### import cases
tcs_cases <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_Cases_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import charges
tcs_charges <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_Charges_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import dispositions
tcs_dispositions <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_DispositionsPerCharge_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import placements
tcs_placements <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_Placements_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

### import mandatory events (to explore legal status)
tcs_mandatory_events <- read_xlsx(
  file.path(
    sharepoint_tcs_data_path, "TCS_MandatoryEvents_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))
```

```{r include=FALSE}
######################################
#### cases
######################################

# de-dup cases file -- there is a very slight discrepancy in N size when de-duping by only juvenile_nbr and case_number as opposed to also including one or more of the above dates; keeping as juvenile_nbr and case_number makes most intuitive sense pending confirmation from JIS contacts (also de-duping by offense_dt as we may need this for later joins...)
tcs_cases_de_dup <- tcs_cases %>%
  filter(!is.na(juvenile_nbr)==TRUE,
         juvenile_nbr!=0, ### there are a handful of records where juvenile_nbr=0; appears to be data error as the records don't consistently share other identifying info like dates and county
         !is.na(case_number)==TRUE) %>% 
  dplyr::rename(case_id = case_number) %>%  ### there are a number of important primary keys which have different names across the files -- here case_id and case_number are the same ID (naming all 'case_id')
  distinct(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,adjudication_dt) %>% 
  mutate(year = as.numeric(year),
         case_year = as.numeric(year))

### 99% of dropped cases are due to 'caseload_action' -- multiple entries as different stages of case are entered 
```


```{r include=FALSE}
######################################
#### charges
######################################

# de-dup charges file -- using case_id (same as 'case_number' in tcs_cases and 'id' (which is "Unique ID for the record.")); no records dropped
# note: there are 1,288 records in the cases df that do not appear at all in the charges df; note from Laura and team: "no juvenile name number in data set – link to cases and use Juvenile Nbr, if needed; 1 to many charges can relate to a case."
# case_number identifies case and id uniquely identifies charge within case  
tcs_charges_de_dup <- tcs_charges %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(id)==TRUE) %>% 
  distinct(id,case_id,.keep_all = TRUE) %>% 
  mutate(current_charge_classification_clean = ifelse(str_starts(current_offense,"712A"),"Status",current_offense_classification),
         year = as.numeric(year),
         case_year = as.numeric(case_year)) ### recode status offense (from laura's team: "If you filter on CurrentOffense by 712A – that should give you the status offenses.")
```


```{r include=FALSE}
######################################
#### placements
######################################

# de-dup placements file -- using case_id (same as 'case_number' in tcs_cases and 'id' (which is "Unique ID for the record.")); no records dropped 
# looks like there are some pure dups
tcs_placements_de_dup <- tcs_placements %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(name_nbr)==TRUE,
         order_type=="PCN") %>% ### from laura and team: "Would recommend using the PCN events and not use ORD ("ordered to transport"/temporary record).  Courts should be using PCN ("placement change notice") events."
  dplyr::rename(juvenile_nbr= name_nbr) %>% ### there are a number of important primary keys which have different names across the files -- here name_nbr and juvenile_nbr are the same ID (naming all 'juvenile_nbr')
  mutate(placement_los = time_length(difftime(place_end_date, place_begin_date), unit = 'days')) %>% 
  arrange(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,place_begin_date,place_type,-placement_los) %>% ### when all primary keys align, including placement start date, we are de-duping by keeping placement with longer LOS -- so arrange by primary keys and then placement LOS in descending order
  distinct(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,place_begin_date,place_type,.keep_all = TRUE) %>% ### 54 dups dropped
 mutate(unique_placement_id = paste0(juvenile_nbr,case_id,place_begin_date,place_type,place_end_date),
         unique_case_id = paste0(juvenile_nbr,case_id,case_year,case_type),
         unique_youth_id = paste0(court_type,year,tc_sreport_court_jcl,juvenile_nbr),
         year = as.numeric(year),
         case_year = as.numeric(year)) %>% ### create unique IDs for later counts or de-dups -- at placement, case, and youth level
  ungroup()
```


```{r include=FALSE}
placement_detention <- c("Calhoun County Juvenile Home","DETENTION","I-Child Vill Det (Not VC Disp)","NON-SECURE DETENTION","OTHER COUNTY DETENTION","Regional Detention Center","SECURE DETENTION")

placement_residential_non_mdhhs <- c("I-Boot Camp","I-CFY Ranch","I-Child Vill Residential","I-Child Vill Secure","I-Private Placement","Independent Placement","INSTITUTIONAL/RESIDENTIAL CARE","PRIVATE AGENCY/INSTITUTION","RESIDENTIAL PLACEMENT","CALHOUN TREATMENT CENTER","Residential Treatment Program")

placement_in_home_aftercare <- c("Aftercare/CV","Bond w/Father","Bond w/Mother","Boot Camp Aftercare","CFY Independent Living","Consent Probation/Father","Consent Probation/Mother","Consent Probation/Other","Consent Probation/Parents","Crossroads For Youth Aftercare","CUS","F01","Father","GDN","Guardian","Home of Guardian-Crt Supervsn","Home of Guardian-DHS Sprv.","Home of Guardian-FIA Supervsn","Home of Parent-Crt Supervision","Home of Parent-DHS Supervision","Home of Parent-FIA Supervision","Home of Parent-No Supervision","Home of parent CRT Supervision","Home of Relative-CRT Supervisi","HOME OF RELATIVE-CRT SUPERVSN","Home of Relative-FIA Supervisi","Home of Relative-FIA Supervsn","I-Child Vill Fam Based Reentry","I-Custodian","Intensive Probation/Father","Intensive Probation/Mother","Intensive Probation/Other","Intensive Probation/Parents","Intensive Reentry Parents","Intensive Reentry Program","Intensive Reentry/Father","Intensive Reentry/Mother","Intensive Reentry/Other","M01","Own Home (Both Parents)","Own Home/Father","Own Home/Mother","PARENTS","PLACED WITH PARENT-CRT SPRV","PLACED WITH PARENT-DHS SPRV","PLACED WITH RELATIVE-CRT SPRV","Probation/Father","Bond w/Parent", "Probation/Mother","Probation/Other","Probation/Parents","PTS","REL","Relative","Relative Placement","Unrelated Unlicensed Home","CFY Day Stud","CFY Work Ed Day St")

placement_mdhhs <- c("DEPARTMENT OF HUMAN SERVICES","DSS","Family Independence Agency","I-Department of Human Services","I-DHHS-150/Del")

placement_awol <- c("Absent without Leave","Order Take Into Custody")

placement_jail <- c("I-Oakland County Jail","Jail")

placement_foster_shelter <- c("Foster Care-Court Supervision","Foster Care-FIA Supervision","PLACED IN FOSTER CARE-DHS SPRV","PLACED IN FOSTER CARE-CRT SPRV","Shelter Home")
```


```{r include=FALSE}
tcs_placements_de_dup %<>%
  mutate(place_type_clean = 
           case_when(
             place_type_desc %in% placement_detention ~ 1,
             place_type_desc %in% placement_residential_non_mdhhs ~ 2,
             place_type_desc %in% placement_mdhhs ~ 3,
             place_type_desc %in% placement_jail ~ 4,
             place_type_desc %in% placement_awol ~ 5,
             place_type_desc %in% placement_in_home_aftercare ~ 6,
             place_type_desc %in% placement_foster_shelter ~ 7,
             TRUE ~ as.numeric(NA)),
         place_type_clean = factor(place_type_clean,
         levels = c(1,2,3,4,5,6,7),
         labels = c("Detention","Residential","MDHHS","Jail","AWOL","In Home/Aftercare","Foster Care/Shelter Home"))) %>% ### use factor function to assign labels to values
  ungroup() %>%  
  mutate(place_year = year(ymd(place_begin_date))) ### create year of placement to use instead of year that case was filed -- to align with Becky's Kalamazoo data when used and to be consistent throughout
```


```{r include=FALSE}
### we don't successfully join for 62 placement records out of 10,325 total (0.6%; 99.4% match rate here)
tcs_placements_cases_de_dup <- left_join(tcs_placements_de_dup,by=c("juvenile_nbr","case_id","court_type","year","tc_sreport_court_jcl","case_year","case_type"))
```


```{r include=FALSE}
### we don't successfully join for 885 placement records out of 10,325 total (8.5%; 91.5% match rate here) 
### we also add duplicates -- as more than one charge may link to an individual placement (we will eventually de-dup by most severe adjudicated charge associated with a placement)
### for this analysis, we need charge data so merging via inner_join to keep only records with both placement and charge data
tcs_placements_charges_de_dup <- inner_join(tcs_cases_de_dup,tcs_charges_de_dup,by=c("case_id","court_type","year","tc_sreport_court_jcl","case_year","case_type")) %>% 
  mutate(adjudication_dt = ymd(adjudication_dt),
         place_begin_date = ymd(place_begin_date)) %>% 
  mutate(before_adjudication_flag = ifelse(place_begin_date<adjudication_dt,1,0),
         after_adjudication_flag = ifelse(place_begin_date>=adjudication_dt,1,0))
```


```{r include=FALSE}
### coding here based on guidance from emily and becky
charge_adjudicated <- c("ADMITTED ALLEGATIONS","FOUND GUILTY","FOUND WITHIN PROVISION OF CODE","GUILTY","NOLO CONTENDERE")


### create flag for charges with adjudication
tcs_placements_charges_de_dup %<>% 
  mutate(charge_adjudicated_flag = ifelse(charge_disposition %in% charge_adjudicated,1,0)) %>% 
  # filter(charge_disposition %in% charge_adjudicated) %>%
  mutate(current_offense = str_to_lower(current_offense),
         current_offense = str_replace_all(current_offense,"[:punct:]", "")) ### remove all punctuation from current_offense and make all lower case -- for merge with current_offense from Emily's lookup table
```


```{r include=FALSE}
### set sharepoint path using csgjcr::csg_sp_path function
sharepoint_pacc_lookup_data_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Converted/JDW/")

### import pacc lookup -- jdw
jdw_charge_pacc_code_lookup <- readr::read_csv(
  file.path(
    sharepoint_pacc_lookup_data_path, "JDWOffCodes_as_csv_abyrum.csv")) %>% 
  clean_names() %>% 
  mutate(current_offense = str_to_lower(offcode_combined),
         current_offense = str_replace_all(current_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
  distinct(current_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements

### import pacc lookup -- msp
msp_charge_pacc_code_lookup <- readr::read_csv(
  file.path(
    sharepoint_pacc_lookup_data_path, "MSPOffCodes_as_csv_abyrum.csv")) %>% 
  clean_names() %>% 
  rename(offcode_combined = disposedcode,
         off_level = desposeddegreefelonymisdeme,
         category = off_cat) %>% 
  select(-disposeddescription) %>% 
  mutate(current_offense = str_to_lower(offcode_combined),
         current_offense = str_replace_all(current_offense,"[:punct:]", "")) %>%  ### remove all punctuation from offcode_combined and make all lower case -- current_offense field has minimal punctuation (will remove all punctuation, as well)
  distinct(current_offense,.keep_all=TRUE) ### some duplicate offenses based on multiple entries with varying punctuation placements

### stack msp and jdw lookups
jdw_msp_charge_pacc_code_lookup <- rbind(jdw_charge_pacc_code_lookup,msp_charge_pacc_code_lookup) %>% 
  distinct(current_offense,.keep_all=TRUE)
```


```{r include=FALSE}
### no corresponding pacc lookup values for 189 records (189/13955; 1.4%)
tcs_placements_charges_de_dup_pacc <- left_join(tcs_placements_charges_de_dup,jdw_msp_charge_pacc_code_lookup,by="current_offense") 
```


```{r include=FALSE}
recode_to_status <- c("712a2d4","722755","ord code 26267")

recode_to_misd_non_person <- c("7503675","7505354a1","ord code 2649","ord code 26492","ord code 2651","ord code 2654","7527971a","9999999904","local orddisorderly")

recode_to_misd_person <- c("75081a1")

recode_to_felony_person <- c("roassault police")
```


```{r include=FALSE}
# From TCS code book: Current Offense Classification - C/Civil Infraction, F/Felony, M/Misdemeanor, S/Statute, H/High Misdemeanor, O/Other, V/Civil-Other, R/Ordinance, Z/Notice for Advisories

### pre-adjudication
tcs_placements_charges_de_dup_pacc_pre_adj <- tcs_placements_charges_de_dup_pacc %>%
  filter(before_adjudication_flag==1) %>%
  mutate(current_charge_classification_clean_numeric = case_when(
    (off_level == "F" & category == "Person") | current_offense%in%recode_to_felony_person ~ 1,
    off_level == "F" & category != "Person" ~ 2,
    (off_level == "M" & category == "Person") | current_offense%in%recode_to_misd_person ~ 3,
    (off_level == "M" & category != "Person") | current_offense%in%recode_to_misd_non_person ~ 4,
    off_level == "S" | current_offense%in%recode_to_status ~ 5,
    off_level %in% c("I","X") ~ 6,
    TRUE ~ as.numeric(NA)),
    current_charge_classification_clean_factor = factor(current_charge_classification_clean_numeric,
         levels = c(1,2,3,4,5,6),
         labels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status","Other/Unknown"))) %>% ### use factor function to assign labels to values)
  arrange(unique_placement_id,current_charge_classification_clean_numeric) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) ### now we are back to original cleaned N

### post-adjudication
tcs_placements_charges_de_dup_pacc_post_adj <- tcs_placements_charges_de_dup_pacc %>%
  filter(after_adjudication_flag==1,
         charge_adjudicated_flag==1) %>% 
  mutate(current_charge_classification_clean_numeric = case_when(
    off_level == "F" &  category == "Person" ~ 1,
    off_level == "F" &  category != "Person" ~ 2,
    off_level == "M" &  category == "Person" ~ 3,
    off_level == "M" &  category != "Person" ~ 4,
    off_level == "S" ~ 5,
    off_level %in% c("I","X") ~ 6,
    TRUE ~ as.numeric(NA)),
    current_charge_classification_clean_factor = factor(current_charge_classification_clean_numeric,
         levels = c(1,2,3,4,5,6),
         labels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status","Other/Unknown"))) %>% ### use factor function to assign labels to values)
  arrange(unique_placement_id,current_charge_classification_clean_numeric) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) ### now we are back to original cleaned N
```


```{r include=FALSE}
table(tcs_placements_charges_de_dup$charge_disposition, useNA = 'always')
```


## Preliminary Descriptives 

<br>

### PRE-ADJUDICATION DETENTION: Individual Placements by Charge Classification: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention")) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"])) 

tcs_placements_charges_de_dup_ind_place_grouped_pre_detention <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention")) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = round(n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`*100, digits = 1)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_de_dup_ind_place_grouped_pre_detention, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

### POST-ADJUDICATION: Median and Mean Time between Disposition Date and Placement Start Date, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_de_dup_pacc_post_adj_disp_place_diff <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(!is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention","Residential","MDHHS")) %>% 
  # select(juvenile_nbr,case_id,court_type,year,tc_sreport_court_jcl,case_year,case_type,adjudication_dt,dispo_date,current_charge_classification_clean_factor,place_begin_date,place_end_date,place_type_clean) %>%
  mutate(dispo_date = mdy(dispo_date)) %>% 
  mutate(dispo_placement_diff = time_length(difftime(place_begin_date,dispo_date), unit = 'days')) %>% 
  filter(dispo_placement_diff>=0) ### remove negative time differences which is likely a coding error (n=1)

tcs_placements_charges_dispo_to_placement_median_lag <- tcs_placements_charges_de_dup_pacc_post_adj_disp_place_diff %>% 
  filter(case_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE) %>% ### only looking at earlier years because we don't want to artificially deflate the median
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (Median Days)` = round(median(dispo_placement_diff[place_type_clean=="Detention"], na.rm = TRUE), digits = 0),
            `Detention (Mean Days)` = round(mean(dispo_placement_diff[place_type_clean=="Detention"], na.rm = TRUE), digits = 0),
            `Residential (Median Days)` = round(median(dispo_placement_diff[place_type_clean=="Residential"], na.rm = TRUE), digits = 0), 
            `Residential (Mean Days)` = round(mean(dispo_placement_diff[place_type_clean=="Residential"], na.rm = TRUE), digits = 0), 

            `MDHHS (Median Days)` = round(median(dispo_placement_diff[place_type_clean=="MDHHS"], na.rm = TRUE), digits = 0),
            `MDHHS (Mean Days)` = round(mean(dispo_placement_diff[place_type_clean=="MDHHS"], na.rm = TRUE), digits = 0)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_dispo_to_placement_median_lag, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

### POST-ADJUDICATION: Individual Placements by Charge Classification: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention","Residential","MDHHS")) %>% 
  summarise(`Sample N, Detention` = n_distinct(unique_placement_id[place_type_clean=="Detention"]),
            `Sample N, Residential` = n_distinct(unique_placement_id[place_type_clean=="Residential"]),
            `Sample N, MDHHS` = n_distinct(unique_placement_id[place_type_clean=="MDHHS"])) 

tcs_placements_charges_de_dup_ind_place_grouped_post <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(place_year%in%c(2016,2017,2018,2019,2020),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean%in%c("Detention","Residential","MDHHS")) %>% 
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (N)` = n_distinct(unique_placement_id[place_type_clean=="Detention"]), 
            `Detention (%)` = round(n_distinct(unique_placement_id[place_type_clean=="Detention"])/tcs_placements_charges_de_dup_denom$`Sample N, Detention`*100, digits = 1),
            `Residential (N)` = n_distinct(unique_placement_id[place_type_clean=="Residential"]), 
            `Residential (%)` = round(n_distinct(unique_placement_id[place_type_clean=="Residential"])/tcs_placements_charges_de_dup_denom$`Sample N, Residential`*100, digits = 1),
            `MDHHS (N)` = n_distinct(unique_placement_id[place_type_clean=="MDHHS"]), 
            `MDHHS (%)` = round(n_distinct(unique_placement_id[place_type_clean=="MDHHS"])/tcs_placements_charges_de_dup_denom$`Sample N, MDHHS`*100, digits = 1)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_de_dup_ind_place_grouped_post, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 



```

<br><br>

```{r eval=FALSE,include=FALSE}
tcs_placements_charges_de_dup_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(case_year%in%c(2016,2017,2018,2019,2020)) %>% 
  summarise(`Sample N` = n_distinct(case_id)) 

tcs_placements_charges_off_level_missing <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(case_year%in%c(2016,2017,2018,2019,2020)) %>% 
  distinct(case_id, .keep_all=TRUE) %>% 
  group_by(current_offense,current_description,current_charge_classification_clean_factor) %>% 
  summarise(`N` = n_distinct(case_id), 
            `%` = round(n_distinct(case_id)/tcs_placements_charges_de_dup_denom$`Sample N`*100, digits = 1)) %>% 
  ungroup() %>% 
  dplyr::select(current_offense_code_clean = current_offense,current_offense_description=current_description,current_offense_classification_clean=current_charge_classification_clean_factor,`N`,`%`)

### print table via kableextra
kable(tcs_placements_charges_off_level_missing, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 


### write out

### set sharepoint path using csgjcr::csg_sp_path function
sharepoint_tcs_data_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Raw/Codebooks/TCS/")

### import cases
openxlsx::write.xlsx(tcs_placements_charges_off_level_missing,
  file.path(
    sharepoint_tcs_data_path, "tcs_offense_codes.xlsx"))
  
```


### PRE-ADJUDICATION DETENTION: Individual Placements by Charge Classification and Year: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
### create detention table by charge -- this is denominator for percentages
detention_charge_over_time_table_denom <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Detention"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `2016` = n_distinct(unique_placement_id[place_year==2016]),
            `2017` = n_distinct(unique_placement_id[place_year==2017]),
            `2018` = n_distinct(unique_placement_id[place_year==2018]),
            `2019` = n_distinct(unique_placement_id[place_year==2019]),
            `2020` = n_distinct(unique_placement_id[place_year==2020])) 

### create detention table by charge
detention_charge_over_time_table_pre <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Detention"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `All Cases (%)` = round(n_distinct(unique_placement_id)/detention_charge_over_time_table_denom$`All Cases (N)`*100,digits=1),
            `2016 (N)` = n_distinct(unique_placement_id[place_year==2016]),
            `2016 (%)` = round(n_distinct(unique_placement_id[place_year==2016])/detention_charge_over_time_table_denom$`2016`*100,digits=1),
            `2017 (N)` = n_distinct(unique_placement_id[place_year==2017]),
            `2017 (%)` = round(n_distinct(unique_placement_id[place_year==2017])/detention_charge_over_time_table_denom$`2017`*100,digits=1),
            `2018 (N)` = n_distinct(unique_placement_id[place_year==2018]),
            `2018 (%)` = round(n_distinct(unique_placement_id[place_year==2018])/detention_charge_over_time_table_denom$`2018`*100,digits=1),
            `2019 (N)` = n_distinct(unique_placement_id[place_year==2019]),
            `2019 (%)` = round(n_distinct(unique_placement_id[place_year==2019])/detention_charge_over_time_table_denom$`2019`*100,digits=1),
            `2020 (N)` = n_distinct(unique_placement_id[place_year==2020]),
            `2020 (%)` = round(n_distinct(unique_placement_id[place_year==2020])/detention_charge_over_time_table_denom$`2020`*100,digits=1)) %>% 
  ungroup() 

### print table via kableextra
kable(detention_charge_over_time_table_pre, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

### POST-ADJUDICATION DETENTION: Individual Placements by Charge Classification and Year: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
### create detention table by charge -- this is denominator for percentages
detention_charge_over_time_table_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Detention"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `2016` = n_distinct(unique_placement_id[place_year==2016]),
            `2017` = n_distinct(unique_placement_id[place_year==2017]),
            `2018` = n_distinct(unique_placement_id[place_year==2018]),
            `2019` = n_distinct(unique_placement_id[place_year==2019]),
            `2020` = n_distinct(unique_placement_id[place_year==2020])) 

### create detention table by charge
detention_charge_over_time_table_post <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Detention"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `All Cases (%)` = round(n_distinct(unique_placement_id)/detention_charge_over_time_table_denom$`All Cases (N)`*100,digits=1),
            `2016 (N)` = n_distinct(unique_placement_id[place_year==2016]),
            `2016 (%)` = round(n_distinct(unique_placement_id[place_year==2016])/detention_charge_over_time_table_denom$`2016`*100,digits=1),
            `2017 (N)` = n_distinct(unique_placement_id[place_year==2017]),
            `2017 (%)` = round(n_distinct(unique_placement_id[place_year==2017])/detention_charge_over_time_table_denom$`2017`*100,digits=1),
            `2018 (N)` = n_distinct(unique_placement_id[place_year==2018]),
            `2018 (%)` = round(n_distinct(unique_placement_id[place_year==2018])/detention_charge_over_time_table_denom$`2018`*100,digits=1),
            `2019 (N)` = n_distinct(unique_placement_id[place_year==2019]),
            `2019 (%)` = round(n_distinct(unique_placement_id[place_year==2019])/detention_charge_over_time_table_denom$`2019`*100,digits=1),
            `2020 (N)` = n_distinct(unique_placement_id[place_year==2020]),
            `2020 (%)` = round(n_distinct(unique_placement_id[place_year==2020])/detention_charge_over_time_table_denom$`2020`*100,digits=1)) %>% 
  ungroup() 

### print table via kableextra
kable(detention_charge_over_time_table_post, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

### POST-ADJUDICATION Residential/MDHHS -- Individual Placements by Charge Classification and Year: Counts and Percentages, 2016-2020
```{r echo=FALSE,warning=FALSE, message=FALSE}
### create Residential/MDHHS table by charge -- this is denominator for percentages
residential_mdhhs_charge_over_time_table_denom <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Residential","MDHHS"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `2016` = n_distinct(unique_placement_id[place_year==2016]),
            `2017` = n_distinct(unique_placement_id[place_year==2017]),
            `2018` = n_distinct(unique_placement_id[place_year==2018]),
            `2019` = n_distinct(unique_placement_id[place_year==2019]),
            `2020` = n_distinct(unique_placement_id[place_year==2020])) 

### create Residential/MDHHS table by charge
residential_mdhhs_charge_over_time_table_post <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
 filter(place_year%in%c(2016,2017,2018,2019,2020),
         place_type_clean %in% c("Residential","MDHHS"),
        !is.na(current_charge_classification_clean_factor)==TRUE) %>%
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`All Cases (N)` = n_distinct(unique_placement_id),
            `All Cases (%)` = round(n_distinct(unique_placement_id)/residential_mdhhs_charge_over_time_table_denom$`All Cases (N)`*100,digits=1),
            `2016 (N)` = n_distinct(unique_placement_id[place_year==2016]),
            `2016 (%)` = round(n_distinct(unique_placement_id[place_year==2016])/residential_mdhhs_charge_over_time_table_denom$`2016`*100,digits=1),
            `2017 (N)` = n_distinct(unique_placement_id[place_year==2017]),
            `2017 (%)` = round(n_distinct(unique_placement_id[place_year==2017])/residential_mdhhs_charge_over_time_table_denom$`2017`*100,digits=1),
            `2018 (N)` = n_distinct(unique_placement_id[place_year==2018]),
            `2018 (%)` = round(n_distinct(unique_placement_id[place_year==2018])/residential_mdhhs_charge_over_time_table_denom$`2018`*100,digits=1),
            `2019 (N)` = n_distinct(unique_placement_id[place_year==2019]),
            `2019 (%)` = round(n_distinct(unique_placement_id[place_year==2019])/residential_mdhhs_charge_over_time_table_denom$`2019`*100,digits=1),
            `2020 (N)` = n_distinct(unique_placement_id[place_year==2020]),
            `2020 (%)` = round(n_distinct(unique_placement_id[place_year==2020])/residential_mdhhs_charge_over_time_table_denom$`2020`*100,digits=1)) %>% 
  ungroup() 

### print table via kableextra
kable(residential_mdhhs_charge_over_time_table_post, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

```{r include=FALSE}

### Calculate length of stay and create LOS buckets, PRE-ADJUDICATION

### calculate length of stay in two different ways:
# los with everything counted 
# los split into placement type buckets -- making sure to recode '0' as NA so as to not bring down mean LOS when youth was never actually placed somewhere
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  group_by(unique_case_id) %>% ### group by case
  mutate(case_first_place_date = min(place_begin_date),
         case_last_place_date = max(place_end_date)) %>%
  ungroup() %>% 
  mutate(unique_placement_los = time_length(difftime(place_end_date, place_begin_date), unit = 'days'),
         los_unique_placement_detention_only = ifelse(place_type_clean=="Detention",unique_placement_los,NA),
         los_unique_placement_residential_non_mdhhs_only = ifelse(place_type_clean=="Residential",unique_placement_los,NA),
         los_unique_placement_mdhhs_only = ifelse(place_type_clean=="MDHHS",unique_placement_los,NA)) %>% 
  group_by(unique_case_id) %>% 
  mutate(los_case_overall_all_included = sum(unique_placement_los),
         los_case_overall_all_included = ifelse(los_case_overall_all_included==0,NA,los_case_overall_all_included),
         los_overall_detention_only = sum(los_unique_placement_detention_only),
         los_overall_detention_only = ifelse(los_overall_detention_only==0,NA,los_overall_detention_only),
         los_overall_residential_only = sum(los_unique_placement_residential_non_mdhhs_only),
         los_overall_residential_only = ifelse(los_overall_residential_only==0,NA,los_overall_residential_only),
         los_overall_mdhhs_only = sum(los_unique_placement_mdhhs_only),
         los_overall_mdhhs_only = ifelse(los_overall_mdhhs_only==0,NA,los_overall_mdhhs_only)) %>% 
  ungroup()

### create grouped los bins for detention
### mirror becky's approach with the kalamazoo analysis
### recode LOS_placement (1/3=1 "1-3 days") (4/7=2 "4-7 days") (8/14=3 "8-14 days") (15/30=4 "15-30 days") (31/90=5 "1-3 months") (91/max=6 ">3 months"), gen (placement_buckets)
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(los_unique_placement_detention_only_grouped_bin = case_when(
    los_unique_placement_detention_only<3 & los_unique_placement_detention_only!=0 ~ 1,
    los_unique_placement_detention_only>=3 & los_unique_placement_detention_only<7 ~ 2,
    los_unique_placement_detention_only>=7 & los_unique_placement_detention_only<15 ~ 3,
    los_unique_placement_detention_only>=15 & los_unique_placement_detention_only<=30 ~ 4,
    los_unique_placement_detention_only>=30 & los_unique_placement_detention_only<=90 ~ 5,
    los_unique_placement_detention_only>90 ~ 6,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_detention_only_grouped_bin = factor(los_unique_placement_detention_only_grouped_bin,
         levels = c(1,2,3,4,5,6),
         labels = c("1 to 3 Days", "3 to 7 Days", "7 to 14 Days","15 to 30 Days","30 to 90 Days","90 Days+"))) ### use factor function to assign labels to values

### create grouped los bins for residential placement
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(los_unique_placement_residential_only_grouped_bin = case_when(
    los_unique_placement_residential_non_mdhhs_only<32 & los_unique_placement_residential_non_mdhhs_only!=0 ~ 1,
    los_unique_placement_residential_non_mdhhs_only>=32 & los_unique_placement_residential_non_mdhhs_only<92 ~ 2,
    los_unique_placement_residential_non_mdhhs_only>=92 & los_unique_placement_residential_non_mdhhs_only<=275 ~ 3,
    los_unique_placement_residential_non_mdhhs_only>=275 & los_unique_placement_residential_non_mdhhs_only<=549 ~ 4,
    los_unique_placement_residential_non_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_residential_only_grouped_bin = factor(los_unique_placement_residential_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values

### create grouped los bins for mdhhs placement
tcs_placements_charges_de_dup_pacc_pre_adj %<>%
  mutate(los_unique_placement_mdhhs_only_grouped_bin = case_when(
    los_unique_placement_mdhhs_only<32 & los_unique_placement_mdhhs_only!=0 ~ 1,
    los_unique_placement_mdhhs_only>=32 & los_unique_placement_mdhhs_only<92 ~ 2,
    los_unique_placement_mdhhs_only>=92 & los_unique_placement_mdhhs_only<=275 ~ 3,
    los_unique_placement_mdhhs_only>=275 & los_unique_placement_mdhhs_only<=549 ~ 4,
    los_unique_placement_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_mdhhs_only_grouped_bin = factor(los_unique_placement_mdhhs_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values
```


```{r include=FALSE}
### Calculate length of stay and create LOS buckets, POST-ADJUDICATION


### calculate length of stay in two different ways:
# los with everything counted 
# los split into placement type buckets -- making sure to recode '0' as NA so as to not bring down mean LOS when youth was never actually placed somewhere
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  group_by(unique_case_id) %>% ### group by case
  mutate(case_first_place_date = min(place_begin_date),
         case_last_place_date = max(place_end_date)) %>%
  ungroup() %>% 
  mutate(unique_placement_los = time_length(difftime(place_end_date, place_begin_date), unit = 'days'),
         los_unique_placement_detention_only = ifelse(place_type_clean=="Detention",unique_placement_los,NA),
         los_unique_placement_residential_non_mdhhs_only = ifelse(place_type_clean=="Residential",unique_placement_los,NA),
         los_unique_placement_mdhhs_only = ifelse(place_type_clean=="MDHHS",unique_placement_los,NA)) %>% 
  group_by(unique_case_id) %>% 
  mutate(los_case_overall_all_included = sum(unique_placement_los),
         los_case_overall_all_included = ifelse(los_case_overall_all_included==0,NA,los_case_overall_all_included),
         los_overall_detention_only = sum(los_unique_placement_detention_only),
         los_overall_detention_only = ifelse(los_overall_detention_only==0,NA,los_overall_detention_only),
         los_overall_residential_only = sum(los_unique_placement_residential_non_mdhhs_only),
         los_overall_residential_only = ifelse(los_overall_residential_only==0,NA,los_overall_residential_only),
         los_overall_mdhhs_only = sum(los_unique_placement_mdhhs_only),
         los_overall_mdhhs_only = ifelse(los_overall_mdhhs_only==0,NA,los_overall_mdhhs_only)) %>% 
  ungroup()

### create grouped los bins for detention
### mirror becky's approach with the kalamazoo analysis
### recode LOS_placement (1/3=1 "1-3 days") (4/7=2 "4-7 days") (8/14=3 "8-14 days") (15/30=4 "15-30 days") (31/90=5 "1-3 months") (91/max=6 ">3 months"), gen (placement_buckets)
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  mutate(los_unique_placement_detention_only_grouped_bin = case_when(
    los_unique_placement_detention_only<3 & los_unique_placement_detention_only!=0 ~ 1,
    los_unique_placement_detention_only>=3 & los_unique_placement_detention_only<7 ~ 2,
    los_unique_placement_detention_only>=7 & los_unique_placement_detention_only<15 ~ 3,
    los_unique_placement_detention_only>=15 & los_unique_placement_detention_only<=30 ~ 4,
    los_unique_placement_detention_only>=30 & los_unique_placement_detention_only<=90 ~ 5,
    los_unique_placement_detention_only>90 ~ 6,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_detention_only_grouped_bin = factor(los_unique_placement_detention_only_grouped_bin,
         levels = c(1,2,3,4,5,6),
         labels = c("1 to 3 Days", "3 to 7 Days", "7 to 14 Days","15 to 30 Days","30 to 90 Days","90 Days+"))) ### use factor function to assign labels to values

### create grouped los bins for residential placement
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  mutate(los_unique_placement_residential_only_grouped_bin = case_when(
    los_unique_placement_residential_non_mdhhs_only<32 & los_unique_placement_residential_non_mdhhs_only!=0 ~ 1,
    los_unique_placement_residential_non_mdhhs_only>=32 & los_unique_placement_residential_non_mdhhs_only<92 ~ 2,
    los_unique_placement_residential_non_mdhhs_only>=92 & los_unique_placement_residential_non_mdhhs_only<=275 ~ 3,
    los_unique_placement_residential_non_mdhhs_only>=275 & los_unique_placement_residential_non_mdhhs_only<=549 ~ 4,
    los_unique_placement_residential_non_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_residential_only_grouped_bin = factor(los_unique_placement_residential_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values

### create grouped los bins for mdhhs placement
tcs_placements_charges_de_dup_pacc_post_adj %<>%
  mutate(los_unique_placement_mdhhs_only_grouped_bin = case_when(
    los_unique_placement_mdhhs_only<32 & los_unique_placement_mdhhs_only!=0 ~ 1,
    los_unique_placement_mdhhs_only>=32 & los_unique_placement_mdhhs_only<92 ~ 2,
    los_unique_placement_mdhhs_only>=92 & los_unique_placement_mdhhs_only<=275 ~ 3,
    los_unique_placement_mdhhs_only>=275 & los_unique_placement_mdhhs_only<=549 ~ 4,
    los_unique_placement_mdhhs_only>549 ~ 5,
    TRUE ~ as.numeric(NA)),
    los_unique_placement_mdhhs_only_grouped_bin = factor(los_unique_placement_mdhhs_only_grouped_bin,
         levels = c(1,2,3,4,5),
         labels = c("Less than 1 Month", "1 to 3 Months","3 to 9 Months","9 to 18 Months","18 Months+"))) ### use factor function to assign labels to values
```

### PRE-ADJUDICATION Median LOS by Charge -- Detention, 2016-2018 (individual placements)
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_median_los_detention_pre <- tcs_placements_charges_de_dup_pacc_pre_adj %>% 
  filter(case_year%in%c(2016,2017,2018),
         !is.na(current_charge_classification_clean_factor)==TRUE,
         place_type_clean=="Detention") %>% ### only looking at earlier years because we don't want to artificially deflate the median
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (Sample N)` = n_distinct(unique_placement_id[!is.na(los_unique_placement_detention_only)==TRUE & los_unique_placement_detention_only>-1]),
            `Detention (Days)` = round(median(los_unique_placement_detention_only[los_unique_placement_detention_only>-1], na.rm = TRUE), digits = 0)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_median_los_detention_pre, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 

```

<br><br>

### POST-ADJUDICATION Median LOS by Charge -- Detention, Residential, and Treatment, 2016-2018 (individual placements)
```{r echo=FALSE,warning=FALSE, message=FALSE}
tcs_placements_charges_median_los_all_post <- tcs_placements_charges_de_dup_pacc_post_adj %>% 
  filter(case_year%in%c(2016,2017,2018),
         !is.na(current_charge_classification_clean_factor)==TRUE) %>% ### only looking at earlier years because we don't want to artificially deflate the median
  distinct(unique_placement_id, .keep_all=TRUE) %>% 
  group_by(current_charge_classification_clean_factor) %>% 
  summarise(`Detention (Sample N)` = n_distinct(unique_placement_id[!is.na(los_unique_placement_detention_only)==TRUE & los_unique_placement_detention_only>-1]),
            `Detention (Days)` = round(median(los_unique_placement_detention_only[los_unique_placement_detention_only>-1], na.rm = TRUE), digits = 0), 
            `Residential (Sample N)` = n_distinct(unique_placement_id[!is.na(los_unique_placement_residential_non_mdhhs_only)==TRUE]),
            `Residential (Days)` = round(median(los_unique_placement_residential_non_mdhhs_only, na.rm = TRUE), digits = 0), 
            `MDHHS (Sample N)` = n_distinct(unique_placement_id[!is.na(los_unique_placement_mdhhs_only)==TRUE]),
            `MDHHS (Days)` = round(median(los_unique_placement_mdhhs_only, na.rm = TRUE), digits = 0)) %>% 
  ungroup()

### print table via kableextra
kable(tcs_placements_charges_median_los_all_post, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br><br>

## Questions out to SCAO

*Preliminary Decisions to Confirm*

•	Our goal is to analyze the TCS placement data by charge type, specifically the most serious charge for which a youth is adjudicated per case:

Currently we are joining the charges data file to the placement data file by merging on the following fields based on your previous advice: ‘CourtType’, ‘Year’, ‘TCSReportCourtJCL’, ‘CaseYear’, ‘CaseID’, and ‘CaseType’

We are selecting the most serious charge for which a youth is adjudicated per case using the ‘current_offense_classification’ field – and selecting the most serious classification within a single case

*Questions*

•	What is the difference between ‘current offense’ and ‘original offense’?

•	It appears as though the charges data file is unique by the field, ‘ID’, along with ‘CaseID’. Is this a unique identifier of each charge? The data dictionary notes that this field is the "Unique ID for the record"

•	What is the best way to determine if a youth was or was not adjudicated for a particular charge? The fields, ‘charge_disposition’ and ‘charge_disp_code’ appear to indicate this. Is that correct? And if so, is there a codebook available for ‘charge_disp_code’ to help us determine if a youth was adjudicated or not for a given charge?

Here are the codes I am seeing in the data: AAL, CCP, CHV, DGT, DINC, DIS, DIV, DVT, FNC, FPC, GTD, GTY, INA, INAC, INAR, NAP, NCH, NFPC, NGTY, NOC, PLG, RMD, TRS, TTC, TWAV

<br><br>
