---
title: "MDHHS CCF Data, FY 2021"
author: "Andrew Byrum"
date: "12/3/2021"
output: 
    html_document:
        df_print: paged
        toc: true
        toc_float: true
---

<br>

**CCF data points:** 

* County
* Month
* Section (type of placement; family foster care, institutional care, and independent living are considered *out-of-home* while basic grant and in home are considered *in home* -- however, youth placed out of home can still receive programming labelled as in-home); unlike other sections, basic grant is 100% reimbursed, up to $15k/FY per county that qualifies by population (for counties with fewer than 75k people; currently 56 counties and 2 tribes have BGs)
* Subsection (description of section; only populated for family foster care and some institutional care records -- for family foster care, include 'A. Court or Tribal Supervised', 'B. Private Agency - In-State', and 'C. Private Agency - Out-Of-State' and for institutional care, includes either 'A. Another County's Institution (Court or MDHHS)' or missing data/blanks)
* Heading (features programming details for in home sections -- however, there is not consistency is coding/naming conventions)
* Total children (unique by youth and placement; two placements for one child would count twice towards 'total children')
* Monthly children (unique placements within a given month -- by county, section, subsection)
* Days care provided
* Adjusted reimbursed amount: amount/claim on which MDHHS bases 50% reimbursement (i.e. it's double what MDHHS actually paid) -- except for basic grants


**Business rules**

* Combined in home and basic grant (the reimbursement amount is different for each, however, so may need to separate if we're calculating what the state actually pays)
* Removing September 2021 from FY 2021 analysis -- a handful of counties have not yet finalized their September claims so the analysis is from October 2020 through August 2021 to standardize the time frame across all 83 counties
* Note: adjusted reimbursement amount reflects claim from county, not actual state reimbursement (which is 50% of county's claim, aside from basic grant claims) -- which figure do we want to present? 
* Combined facility operating costs and per diem placement costs for institutional care (in 2020, MDHHS started requiring counties to separate them into two sections -- institutional care per diem costs and 'County/Court Operated Facilities' which are institutional care operating costs)
* The metric used in the maps, adjusted reimbursement claim per placement/month, is the total fiscal year reimbursement claim per total fiscal year 'monthly children' or claimed placements a month. So one youth placed once for the entire fiscal year would be 11 placements/month (since we're excluding September) -- I've initially decided on this as opposed to unique placements for the entire year (which in the prior example would just be 1) because it better captures length of stay (but by no means perfectly captures it). 'Days care provided' is only available for out-of-home placements so that can't be used for comparisons of in-home and out-of-home expense. We may want to change this if reimbursement claim per placements/month seems too convoluted to easily talk through, though


**Notes on FY 2021 data**

* Teddy/Kelly feel confident that the file only reflects JJ claims, not Abuse/Neglect claims as well
* They are also confident that there no are significant delayed claims reflected in FY 2021 (i.e. FY 2019 or FY 2020 claims that appear in the FY 2021 data)
* A small number of exceptions are likely to exist for both points, but are quite rare and small enough to not meaningfully shift data/findings

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","tidylog","distill","formattable","ragg")
```

```{r include=FALSE}
### import ccf fy 2016
ccf_fy2016 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2016_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2016")

### import ccf fy 2017
ccf_fy2017 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2017_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2017")

### import ccf fy 2018
ccf_fy2018 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2018_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2018")

### import ccf fy 2019
ccf_fy2019 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2019_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2019")

### import ccf fy 2020
ccf_fy2020 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2020_DataOuput-11232021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2020")

### import ccf fy 2020
ccf_fy2021 <- openxlsx::read.xlsx("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Raw\\MDHHS\\Financial\\ccf_data_for_r\\FY2021_DataOuput-12032021.xlsx", sheet = "Export Worksheet") %>% 
  clean_names() %>% 
  mutate(ccf_fy = "2021")

### stack all ccf files -- columns all align
df_ccf_stacked_2016_2021 <- rbind(ccf_fy2016,ccf_fy2017,ccf_fy2018,ccf_fy2019,ccf_fy2020,ccf_fy2021) %>% 
  group_by_all() %>% 
  mutate(dup_count = n()) %>% 
  ungroup() %>% 
  distinct(., .keep_all = TRUE) %>% ################### I'M TEMPORARILY DE-DUPING HERE ON PURE DUPLICATES (DUPS ACROSS ALL COLUMNS); THIS MAY CHANGE DEPENDING ON WHAT TEDDY SAYS, HOWEVER 
  mutate(heading_total_flag = ifelse(str_detect(heading,"(?i)total"),1,0)) %>% ### flag rows where 'heading' has 'total' in it
  filter(section != "Totals",
         heading_total_flag==0) ### Teddy said to ignore 'Totals' sections; also removing all headings with 'total' -- these appear to simply tally up youth counts and reimbursement totals for the month by section? Confirm with Teddy. 
```

```{r include=FALSE,message=FALSE,warning=FALSE}
df_ccf_stacked_2021_only_cleaned <- df_ccf_stacked_2016_2021 %>%
  filter(ccf_fy=="2021",
         ccf_month_code!="SEPTEMBER") %>% ### just using 2021 and removing september claims
  mutate(out_of_home_flag = ifelse(section %in% c("Family Foster Care","Independent Living","Institutional Care","Court Operated Facility","County/Court Operated Facilities"), 1,0)) %>%  ### flag out-of-home facilities based on call with Teddy' -- he didn't mentioned either Court Operated Facility or County/Court Operated Facilities explicitly but instead included as part of institutional care so I still included (also are clearly out-of-home placements)
  mutate(section_clean = ifelse(section %in% c("Court Operated Facility","County/Court Operated Facilities"),"Institutional Care", section))

         # section_clean = ifelse(section %in% c("In-Home Care","Basic Grant"),"In Home", section_clean)) ### recoding 'Basic Grant' as 'In Home'; according to Teddy, 'Basic Grant' is similar to in-home-care, but with fewer restrictions (for counties with fewer than 75k people and tribes; capped at $15k -- and 100% reimbursed)

```

## Tables

### CCF Total Adjusted Reimbursement Amount by Section, FY 2021 (excluding September 2021)
```{r echo=FALSE,message=FALSE,warning=FALSE}
df_ccf_stacked_2020_total_amounts <- df_ccf_stacked_2021_only_cleaned %>% 
  group_by(section_clean) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

df_ccf_stacked_2020_total_amounts_overall <- df_ccf_stacked_2021_only_cleaned %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  mutate("CCF Section" = "Overall")

### combine tables for kable
df_ccf_stacked_2020_total_amounts_table <- rbind(df_ccf_stacked_2020_total_amounts,df_ccf_stacked_2020_total_amounts_overall)

### print table via kableextra
kable(df_ccf_stacked_2020_total_amounts_table[c(2,4,1,3,5),], format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") %>% 
  row_spec(5, bold = TRUE) %>% 
  pack_rows("In Home*", 1, 1, label_row_css = "background-color: #666; color: #fff;") %>% 
  pack_rows("Out of Home", 2, 4, label_row_css = "background-color: #666; color: #fff;") %>% 
  pack_rows("", 5, 5, label_row_css = "background-color: #666; color: #fff;") %>% 
  footnote(symbol = "In-home programming is also available, in some situations, to youth in out-of-home placements")
```

<br><br>

### CCF Total Adjusted Reimbursement Amount by Section and Subsection, FY 2021 (excluding September 2021)

Note: Subsection data appears to only be consistently entered (and thus, reliable) for family foster care
```{r echo=FALSE,message=FALSE,warning=FALSE}
### recode NA as "Missing" for analysis of subsection as we want to report out everything including the NAs
df_ccf_stacked_2020_only_cleaned_subsection_recode <- df_ccf_stacked_2021_only_cleaned %>% 
  mutate(subsection = ifelse(is.na(subsection)==TRUE, "Missing", subsection))

### in home, overall
df_ccf_in_home_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="In Home") %>% 
  group_by(section_clean) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

### in home, by subsection
df_ccf_in_home_subsection <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="In Home") %>% 
  group_by(subsection) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = subsection)

### combine tables 
df_ccf_in_home_final <- rbind(df_ccf_in_home_overall,df_ccf_in_home_subsection)

### family foster care, overall
df_ccf_foster_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Family Foster Care") %>% 
  group_by(section_clean) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

### family foster care, by subsection
df_ccf_foster_subsection <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Family Foster Care") %>% 
  group_by(subsection) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = subsection)

### combine tables 
df_ccf_foster_final <- rbind(df_ccf_foster_overall,df_ccf_foster_subsection)

### institutional care, overall
df_ccf_institution_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Institutional Care") %>% 
  group_by(section_clean) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

### institutional care, by subsection
df_ccf_institution_subsection <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Institutional Care") %>% 
  group_by(subsection) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = subsection)

### combine tables 
df_ccf_institution_final <- rbind(df_ccf_institution_overall,df_ccf_institution_subsection)

### independent living, overall
df_ccf_independent_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Independent Living") %>% 
  group_by(section_clean) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = section_clean)

### independent living, by subsection
df_ccf_independent_subsection <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  filter(section_clean=="Independent Living") %>% 
  group_by(subsection) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  ungroup() %>% 
  dplyr::rename("CCF Section" = subsection)

### combine tables 
df_ccf_independent_final <- rbind(df_ccf_independent_overall,df_ccf_independent_subsection)


### overall 
df_ccf_stacked_2020_total_amounts_overall <- df_ccf_stacked_2020_only_cleaned_subsection_recode %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>% 
  mutate("CCF Section" = "Overall")

### combine tables for kable
df_ccf_stacked_2020_subsection_table <- rbind(df_ccf_in_home_final,df_ccf_foster_final,df_ccf_institution_final,df_ccf_independent_final,df_ccf_stacked_2020_total_amounts_overall)

### print table via kableextra
kable(df_ccf_stacked_2020_subsection_table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") %>% 
  row_spec(13, bold = TRUE) %>% 
  pack_rows("In Home*", 1, 2, label_row_css = "background-color: #666; color: #fff;") %>% 
  pack_rows("Out of Home", 3, 12, label_row_css = "background-color: #666; color: #fff;") %>% 
  pack_rows("", 13, 13, label_row_css = "background-color: #666; color: #fff;") %>% 
  footnote(symbol = "In-home programming is also available, in some situations, to youth in out-of-home placements") %>% 
  add_indent(c(2,4,5,6,7,9,10,12))
```

<br><br>

### Raw 'Heading'/Programming Categories for 'In-Home' Programming, FY 2021 (excluding September 2021)

Note: 'In-Home' programming is the only CCF section for which there is near-complete data. However, as you can see, there is not consistency in coding/naming conventions. Here, I'm only showing the first 50 of 279 in-home programs:
```{r echo=FALSE,message=FALSE,warning=FALSE}
### in home, by heading
df_ccf_in_home_heading <- df_ccf_stacked_2021_only_cleaned %>% 
  filter(section_clean=="In Home") %>% 
  group_by(heading) %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>%
  ungroup() %>% 
  dplyr::rename("CCF Heading/Programming" = heading)

### in home, by heading
df_ccf_in_home_overall <- df_ccf_stacked_2021_only_cleaned %>% 
  filter(section_clean=="In Home") %>% 
  summarize(`Total Adj Reimburse Claim` = scales::dollar(sum(adjusted_reimbursed_amt)),
            `Total Days of Care Provided` = sum(days_care_provided),
            `Unique Children/Placements` = sum(total_children[ccf_month_code=="AUGUST"]), ### this file ends in august (as september -- the last month in the fiscal year -- was not complete at the time of analysis)
            `Total Placements/Month` = sum(monthly_children),
            `Adj Reimburse Claim Per Days Claimed` = scales::dollar(sum(adjusted_reimbursed_amt)/sum(days_care_provided)),
            `Adj Reimburse Claim Per Unique Youth/Placement` = scales::dollar(sum(adjusted_reimbursed_amt)/`Unique Children/Placements`),
            `Adj Reimburse Claim Per Unique Placement/Month` = scales::dollar(sum(adjusted_reimbursed_amt)/`Total Placements/Month`)) %>%
  ungroup() %>% 
  dplyr::mutate("CCF Heading/Programming" = "Overall")

### combine tables 
df_ccf_in_home_heading_table <- rbind(df_ccf_in_home_heading,df_ccf_in_home_overall) %>% 
  head(50)

### print table via kableextra
kable(df_ccf_in_home_heading_table, format.args = list(big.mark = ","), align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") 
```

<br><br>

## Maps 
```{r include=FALSE}
### pull census/acs data via tidycensus package

### set census api key via tidycensus package
### this allows us to pull census/acs data via the tidycensus package
tidycensus::census_api_key("1ba246a0db6cfbd596219470af425fe932cf064b", install = TRUE, overwrite = TRUE)
readRenviron("~/.Renviron")

### read in county-level cdc/acs juvenile population estimates, split by race/ethnicity and sex, for base juvenile population rate calculations
mi_age_10_17_sex_race_final <- readr::read_delim("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Ezapop\\ezapop_10_17_race_eth_sex_mi.txt" , delim = "|")

### pull other acs/census data for additional context/mapping, if wanted

### overall population
mi_overall_pop <- tidycensus::get_acs(geography = "County",
                                              state = "MI",
                                              variables = "B01003_001",
                                              geometry = FALSE) %>%
  clean_names() %>%
  dplyr::select(geoid,name,estimate) %>%
  dplyr::rename(estimate_total_pop = estimate)

### weighted estimate of percentage of census tracts residents living below federal poverty threshold
mi_poverty_status <- tidycensus::get_acs(geography = "County", 
                                              state = "MI",
                                              variables = "S1701_C03_001", 
                                              geometry = FALSE) %>% 
  clean_names() %>% 
  dplyr::select(geoid,estimate) %>% 
  dplyr::rename(estimate_below_poverty = estimate)

### weighted estimate of income
mi_median_income <- tidycensus::get_acs(geography = "County", 
                                             state = "MI",
                                             variables = "S1901_C01_012", 
                                             geometry = FALSE) %>% 
  clean_names() %>% 
  dplyr::select(geoid,estimate) %>% 
  dplyr::rename(estimate_income = estimate)


### weighted estimate of percentage of race from 2010 census; couldn't find overall race estimates from 2018 ACS
### pulled estimated counts and constructed percent estimate
### these are the ids of race variables that we want to pull 
race_vars <- c(estimate_white = "P005003",
               estimate_black = "P005004",
               estimate_asian = "P005006",
               estimate_hispanic = "P004003")

mi_race_2010 <- tidycensus::get_decennial(geography = "County", 
                                               state = "MI",
                                               variables = race_vars,
                                               summary_var = "P001001",
                                               geometry = FALSE) %>% 
  clean_names() %>% 
  mutate(estimate = (value/summary_value)*100) ###create percent estimate from estimated counts

### pivot race file to be wide and unique by census tract 
mi_race_2010 %<>%
  dplyr::select(geoid,variable,estimate) %>% 
  spread(variable,estimate, fill = NA) 
```

```{r include=FALSE}
### join all acs variables together in one file 
mi_acs_census_county <- left_join(mi_poverty_status, mi_median_income, by="geoid")

mi_acs_census_county <- left_join(mi_acs_census_county, mi_overall_pop, by="geoid")

mi_acs_census_county <- left_join(mi_acs_census_county, mi_race_2010, by="geoid")
```

```{r include=FALSE}
### read in county-level iowa data to create county,state, geoid crosswalk with acs/census data 
### this is the official iowa county shapefile, obtained here: https://www.census.gov/geographies/mapping-files/time-series/geo/tiger-line-file.html 
### this is not used for mapping, however, hence we remove geography below; it's just a crosswalk across county name, geoid, and county fip code
mi_geo_county <- read_sf("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\Geospatial_Mapping\\US County Geo Data\\tl_2019_us_county\\tl_2019_us_county.shp") %>%
  clean_names() %>% 
  filter(statefp=="26") %>% ### filter on michigan using state fips code (26)
  dplyr::select(geoid, county_name_short=name, county_fip=countyfp) 

### convert to dataframe and remove geometry -- this will not be 
mi_geo_county <- as.data.frame(mi_geo_county) %>%
    dplyr::select(-(geometry))
```

```{r include=FALSE}
### CCF Total Adjusted Reimbursement Amount by section and county, FY 2020 
df_ccf_stacked_2020_total_amounts_map <- df_ccf_stacked_2021_only_cleaned %>% 
  group_by(agency_name) %>% 
  summarize(total_adj_reimburse_per_total_youth_month_placements_in_home = sum(adjusted_reimbursed_amt[section_clean=="In Home"])/sum(monthly_children[section_clean=="In Home"]),
            total_adj_reimburse_per_total_youth_month_placements_inst_care = sum(adjusted_reimbursed_amt[section_clean=="Institutional Care"])/sum(monthly_children[section_clean=="Institutional Care"])) %>% 
  ungroup() %>% 
  dplyr::mutate(county_name_short =  gsub(" County", "", agency_name)) 
```

```{r include=FALSE}
### merge county code/geoid crosswalk to acs data
mi_acs_census_county_crosswalk <- inner_join(mi_acs_census_county,mi_geo_county,by = "geoid")

### county-level estimates

### clean up acs/census estimates for eventual use as map labels
mi_acs_census_county_crosswalk_full <- mi_acs_census_county_crosswalk %>% 
    group_by(county_name_short) %>% 
    summarize(estimate_total_pop = sum(estimate_total_pop, na.rm=TRUE),
              estimate_below_poverty_mean = round(mean(estimate_below_poverty, na.rm=TRUE),digits = 1),
              estimate_income_median = round(mean(estimate_income, na.rm=TRUE),digits = 1),
              estimate_asian_mean = round(mean(estimate_asian, na.rm=TRUE),digits = 1),
              estimate_black_mean = round(mean(estimate_black, na.rm=TRUE),digits = 1),
              estimate_hispanic_mean = round(mean(estimate_hispanic, na.rm=TRUE),digits = 1),
              estimate_white_mean = round(mean(estimate_white, na.rm=TRUE),digits = 1)) %>% 
    ungroup() 

### calculate rates using population estimates by county from 2019 American Community Survey
mi_acs_census_county_no_geo_rates <- mi_acs_census_county_crosswalk_full %>% 
  left_join(df_ccf_stacked_2020_total_amounts_map, by = "county_name_short") 
```

```{r include=FALSE}
### read in michigan county-level shape file -- clipped to shoreline
mi_county_shape <- read_sf("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\Misc_Documents\\Shapefiles\\mi_shape_shoreline_clipped\\Counties_(v17a).shp") %>%
  clean_names() %>% 
  dplyr::rename(county_name_short = name,
                county_name_full = label)
  
### merge county shapefile to acs, census, and iowa data to attach geography and render the file map-able
mi_acs_census_county_geo <- merge(mi_county_shape, mi_acs_census_county_no_geo_rates, by = "county_name_short") 

### create institutional care claim amount to in home claim amount ratio
mi_acs_census_county_geo %<>%
  mutate(inst_care_reimburse_to_in_home_ratio = total_adj_reimburse_per_total_youth_month_placements_inst_care/total_adj_reimburse_per_total_youth_month_placements_in_home) %>% 
  mutate(inst_care_reimburse_to_in_home_ratio= ifelse(is.infinite(inst_care_reimburse_to_in_home_ratio),NA,inst_care_reimburse_to_in_home_ratio))

### create shapefile with only michigan state borders for additional mapping layer 
mi_state_geo <- mi_county_shape %>% 
  dplyr::summarise()
```

```{r include=FALSE}
### define color palletes for each layer in all interactive maps

### define pallete for total_adj_reimburse_per_total_youth_month_placements_in_home at county level
pal_percent_claim_per_placement_month_in_home <- colorQuantile(palette = c("#00475d","#007392","#0db4e4","#9ed4ef"), domain = mi_acs_census_county_geo$total_adj_reimburse_per_total_youth_month_placements_in_home, n = 4, reverse = TRUE) ### use reverse to invert colors 

### define pallete for total_adj_reimburse_per_total_youth_month_placements_inst_care at county level
pal_percent_claim_per_placement_month_inst_care <- colorQuantile(palette = c("#00475d","#007392","#0db4e4","#9ed4ef"), domain = mi_acs_census_county_geo$total_adj_reimburse_per_total_youth_month_placements_inst_care, n = 4, reverse = TRUE) ### use reverse to invert colors 

### define pallete for total_adj_reimburse_per_total_youth_month_placements_inst_care at county level
pal_percent_claim_inst_care_in_home_ratio <- colorQuantile(palette = c("#00475d","#007392","#0db4e4","#9ed4ef"), domain = mi_acs_census_county_geo$inst_care_reimburse_to_in_home_ratio, n = 4, reverse = TRUE) ### use reverse to invert colors 
```

### Interactive Map 

<br>

#### In Home and Institutional Care Reimbursement Claims per Placement/Month, FY 2021 (excluding September 2021)

Toggle between the three layers using the buttons in the top right corner. 

You can also hover over each county to learn more--including the exact in home and institutional care reimbursement claims per per placement/month in FY 2021, the ratio of institutional reimbursement to in home reimbursement, the overall county population size, as well as the poverty rate, and overall race/ethnicity breakdown.

<br>

```{r echo=FALSE, warning=FALSE, message=FALSE, out.width = '150%'}
### create label that will pop-up when user hovers over each county; call this label for each polygon layer added because we want this to appear with each layer
label_acs_census_county_popup <- paste0('<strong>', mi_acs_census_county_geo$county_name_short," County",'</strong>',"<br/>", "<br/>", 
                                        '<strong>',"Adjusted Reimbursement Claim per Placement/Month",'</strong>',"<br/>",
                                         "In Home: ", scales::dollar(mi_acs_census_county_geo$total_adj_reimburse_per_total_youth_month_placements_in_home),"<br/>", 
                                            "Institutional Care: ", scales::dollar(mi_acs_census_county_geo$total_adj_reimburse_per_total_youth_month_placements_inst_care),"<br/>", 
                                            "Institutional Care to In Home Ratio: ", round(mi_acs_census_county_geo$inst_care_reimburse_to_in_home_ratio, digits=0),":1","<br/>", "<br/>", 
                    '<strong>',"Population, SES, and Race/Ethnicity Data (from 2019 ACS)",'</strong>',"<br/>",
                                        "Overall Population: ",format(round(mi_acs_census_county_geo$estimate_total_pop, digits=0), big.mark=",", scientific=FALSE),"<br/>",
                                        "Poverty Rate: ",mi_acs_census_county_geo$estimate_below_poverty_mean,"%","<br/>",
                                        "Asian Population: ",mi_acs_census_county_geo$estimate_asian_mean,"%","<br/>",
                                        "Black Population: ",mi_acs_census_county_geo$estimate_black_mean,"%","<br/>",
                                        "Hispanic Population: ",mi_acs_census_county_geo$estimate_hispanic_mean,"%","<br/>",
                                        "White Population: ",mi_acs_census_county_geo$estimate_white_mean,"%") %>%
  lapply(htmltools::HTML)

### create legend labels for all mapped layers
label_in_home <- c("Less than $554","$554 to $876","$876 to $1,592","$1,592+","NA")

label_inst_care <- c("Less than $2,947","$2,947 to $4,646","$4,646 to $7,960","$7,960+","NA")

label_inst_care_in_home_ratio <- c("Less than 3:1","3:1 to 5:1","5:1 to 9:1","More than 9:1","NA")

### map with leaflet 
mi_acs_census_county_geo %>%
    sf::st_transform(crs = "+init=epsg:4326") %>%
    leaflet(height = 600, width = 900) %>%
  addProviderTiles(provider = "CartoDB.Positron",
                   options = providerTileOptions(minZoom = 6.5, maxZoom = 9)) %>%
  addPolylines(color = "Black",
               stroke = FALSE,
               opacity = .01,
               weight = .01) %>%
    addPolygons(weight = 1,
              color = "Black",
              fillColor = ~ pal_percent_claim_per_placement_month_in_home(mi_acs_census_county_geo$total_adj_reimburse_per_total_youth_month_placements_in_home),
                fillOpacity = 0.7,
                label = ~ label_acs_census_county_popup,
                labelOptions = labelOptions(direction = "auto"),
               highlightOptions  = highlightOptions(
                opacity = 1,
                weight = 2,
                fillOpacity = 1,
                bringToFront = TRUE,
                sendToBack = FALSE),
              group = "In Home") %>%
      addPolygons(weight = 1,
              color = "Black",
              fillColor = ~ pal_percent_claim_per_placement_month_inst_care(mi_acs_census_county_geo$total_adj_reimburse_per_total_youth_month_placements_inst_care),
                fillOpacity = 0.7,
                label = ~ label_acs_census_county_popup,
                labelOptions = labelOptions(direction = "auto"),
               highlightOptions  = highlightOptions(
                opacity = 1,
                weight = 2,
                fillOpacity = 1,
                bringToFront = TRUE,
                sendToBack = FALSE),
              group = "Institutional Care") %>%
        addPolygons(weight = 1,
              color = "Black",
              fillColor = ~ pal_percent_claim_inst_care_in_home_ratio(mi_acs_census_county_geo$inst_care_reimburse_to_in_home_ratio),
                fillOpacity = 0.7,
                label = ~ label_acs_census_county_popup,
                labelOptions = labelOptions(direction = "auto"),
               highlightOptions  = highlightOptions(
                opacity = 1,
                weight = 2,
                fillOpacity = 1,
                bringToFront = TRUE,
                sendToBack = FALSE),
              group = "Institutional/In Home Ratio") %>%
    addPolylines(data = mi_acs_census_county_geo,
                 color = "Black",
               opacity = .5,
               weight = .5) %>%
      addLegend("topleft",
              pal = pal_percent_claim_per_placement_month_in_home,
              values = ~ mi_acs_census_county_geo$total_adj_reimburse_per_total_youth_month_placements_in_home,
              group = "In Home",
              title = "In Home",
              opacity = 2,
              labFormat = function(type, cuts, p) {paste0(label_in_home)}) %>% 
          addLegend("topleft",
              pal = pal_percent_claim_per_placement_month_inst_care,
              values = ~ mi_acs_census_county_geo$total_adj_reimburse_per_total_youth_month_placements_inst_care,
              group = "Institutional Care",
              title = "Institutional Care",
              opacity = 2,
              labFormat = function(type, cuts, p) {paste0(label_inst_care)}) %>% 
     addLegend("topleft",
              pal = pal_percent_claim_inst_care_in_home_ratio,
              values = ~ mi_acs_census_county_geo$inst_care_reimburse_to_in_home_ratio,
              group = "Institutional/In Home Ratio",
              title = "Institutional/In Home Ratio",
              opacity = 2,
              labFormat = function(type, cuts, p) {paste0(label_inst_care_in_home_ratio)}) %>% 
addLayersControl(
  baseGroups = c("In Home","Institutional Care","Institutional/In Home Ratio"),
  position = "topright",
  options = layersControlOptions(collapsed = FALSE)) %>%
  htmlwidgets::onRender("
    function(el, x) {
      var updateLegend = function () {
          var selectedGroup = document.querySelectorAll('input:checked')[0].nextSibling.innerText.substr(1);

          document.querySelectorAll('.legend').forEach(a => a.hidden=true);
          document.querySelectorAll('.legend').forEach(l => {
            if (l.children[0].children[0].innerText == selectedGroup) l.hidden=false;
          });
      };
      updateLegend();
      this.on('baselayerchange', e => updateLegend());
    }") ### the javascript specified after htmlwidgets attaches each legend to the selected layer; this is quite temperamental. Doesn't work with multiple interactive maps and doesn't work with tabs if isn't in first tab
```

<br><br>

### Static Maps

<br>

```{r include=FALSE}
### set constants for static plots (this may need to change in final rmd)
default_font_color <- "#4e4d47"
default_font_family <- "Arial"

### define options for saving plots
knitr::opts_chunk$set(
    out.width = "115%",
    dpi = 500,
    fig.width = 10,
    fig.height = 7.5,
    strip.white = T,
    dev = "png")
```

```{r include=FALSE}
### create static map theme (based on https://timogrossenbacher.ch/2019/04/bivariate-maps-with-ggplot2-and-sf/)
theme_map <- function(...) {
  theme_minimal() +
  theme(
    text = element_text(family = default_font_family,
                        color = default_font_color),
    # remove all axes
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    # add a subtle grid
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # borders and margins
    plot.margin = unit(c(.5, .5, .2, .5), "cm"),
    panel.border = element_blank(),
    panel.spacing = unit(c(-.1, 0.2, .2, 0.2), "cm"),
    # titles
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 9, hjust = 0,
                               color = default_font_color),
    plot.title = element_text(size = 15, hjust = 0.5,
                              color = default_font_color),
    plot.subtitle = element_text(size = 10, hjust = 0.5,
                                 color = default_font_color,
                                 margin = margin(b = -0.1,
                                                 t = -0.1,
                                                 l = 2,
                                                 unit = "cm"),
                                 debug = F),
    # captions
    plot.caption = element_text(size = 7,
                                hjust = .5,
                                margin = margin(t = 0.2,
                                                b = 0,
                                                unit = "cm"),
                                color = "#939184"),
    ...
  )
}
```


#### In Home Reimbursement Claims per Placement/Month, FY 2021 (excluding September 2021)

```{r echo=FALSE, warning=FALSE, message=FALSE, out.width = '150%'}
### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- mi_acs_census_county_geo %>%
  pull(total_adj_reimburse_per_total_youth_month_placements_in_home) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_in_home <- c("$1,592+","$876 to $1,592","$554 to $876", "Less than $554")

### create a new variable with the specified quantiles
mi_acs_census_county_geo %<>%
  mutate(reimburse_per_placement_in_home_quartile = cut(-total_adj_reimburse_per_total_youth_month_placements_in_home,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_in_home,
                               include.lowest = T)) 

### map via ggplot 
ggplot(
  # define main data source
  data = mi_acs_census_county_geo
) +
  # use the "alpha hack" (as the "fill" aesthetic is already taken)
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  # use thin white stroke for municipality borders
  geom_sf(
    mapping = aes(
      fill = reimburse_per_placement_in_home_quartile
      ),
    color = "white",
    size = 0.1
  ) +
 scale_fill_manual(
    values = c("#00475d","#007392","#0db4e4","#9ed4ef"),
    name = "Reimbursement Claim per Placement/Month",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use thicker white stroke for borders
  geom_sf(
    data = mi_acs_census_county_geo,
    fill = "transparent",
    color = "white",
    size = .75
  )  +
    geom_sf(
    data = mi_state_geo,
    fill = "transparent",
    color = "grey",
    size = 0.3
  )  +
  # add titles
  labs(x = NULL,
       y = NULL,
       title = "Reimbursement Claim per Placement/Month",
         subtitle = "In Home Programming, FY 2021") +
  # add theme
  theme_map()
```

<br><br>

#### Institutional Care Reimbursement Claims per Placement/Month, FY 2021 (excluding September 2021)


```{r echo=FALSE, warning=FALSE, message=FALSE, out.width = '150%'}
### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- mi_acs_census_county_geo %>%
  pull(total_adj_reimburse_per_total_youth_month_placements_inst_care) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_inst_care <- c("$7,960+","$4,646 to $7,960","$2,947 to $4,646", "Less than $2,947")

### create a new variable with the specified quantiles
mi_acs_census_county_geo %<>%
  mutate(reimburse_per_placement_inst_care_quartile = cut(-total_adj_reimburse_per_total_youth_month_placements_inst_care,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_inst_care,
                               include.lowest = T)) 

### map via ggplot 
ggplot(
  # define main data source
  data = mi_acs_census_county_geo
) +
  # use the "alpha hack" (as the "fill" aesthetic is already taken)
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  # use thin white stroke for municipality borders
  geom_sf(
    mapping = aes(
      fill = reimburse_per_placement_inst_care_quartile
      ),
    color = "white",
    size = 0.1
  ) +
 scale_fill_manual(
    values = c("#00475d","#007392","#0db4e4","#9ed4ef"),
    name = "Reimbursement Claim per Placement/Month",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use thicker white stroke for borders
  geom_sf(
    data = mi_acs_census_county_geo,
    fill = "transparent",
    color = "white",
    size = .75
  )  +
  geom_sf(
    data = mi_state_geo,
    fill = "transparent",
    color = "grey",
    size = 0.3
  )  +
  # add titles
  labs(x = NULL,
       y = NULL,
       title = "Reimbursement Claim per Placement/Month",
         subtitle = "Institutional Care, FY 2021") +
  # add theme
  theme_map()
```

<br><br>

#### Institutional Care to In Home Programming CCF Reimbursement Claim Ratio, FY 2021 (excluding September 2021)

```{r echo=FALSE, warning=FALSE, message=FALSE, out.width = '150%'}
### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- mi_acs_census_county_geo %>%
  pull(inst_care_reimburse_to_in_home_ratio) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_inst_care_in_home_ratio <- c("Over 9:1","5:1 to 9:1","3:1 to 5:1", "Less than 3:1")

### create a new variable with the specified quantiles
mi_acs_census_county_geo %<>%
  mutate(inst_care_reimburse_to_in_home_ratio_quartile = cut(-inst_care_reimburse_to_in_home_ratio,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_inst_care_in_home_ratio,
                               include.lowest = T)) 

### map via ggplot 
ggplot(
  # define main data source
  data = mi_acs_census_county_geo
) +
  # use the "alpha hack" (as the "fill" aesthetic is already taken)
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  # use thin white stroke for municipality borders
  geom_sf(
    mapping = aes(
      fill = inst_care_reimburse_to_in_home_ratio_quartile
      ),
    color = "white",
    size = 0.1
  ) +
 scale_fill_manual(
    values = c("#00475d","#007392","#0db4e4","#9ed4ef"),
    name = "Institutional Care to In Home Programming CCF Claim Ratio",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use thicker white stroke for borders
  geom_sf(
    data = mi_acs_census_county_geo,
    fill = "transparent",
    color = "white",
    size = .75
  )  +
  geom_sf(
    data = mi_state_geo,
    fill = "transparent",
    color = "grey",
    size = 0.3
  )  +
  # add titles
  labs(x = NULL,
       y = NULL,
       title = "Institutional to In Home Reimbursement Ratio",
         subtitle = "FY 2021") +
  # add theme
  theme_map()
```

<br><br>
