---
title: "mi_tcs_county_placement_cleaning"
author: "Andrew Byrum"
date: "2/8/2022"
output: html_document
---

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","tidylog")
````

1. Read in Pertinent TCS Files for Placement Analysis: 'cases', 'charges', 'dispositions', and 'placements'
```{r include=FALSE}
# library(remotes)
# 
# remotes::install_github("CSGJCResearch/csgjcr")

# set csg path -- until i am able to download csgjcr packages
csg_path <- "C:/Users/abyrum/The Council of State Governments/JC Research - Documents/JC Research - JJ_Michigan - JJ_Michigan/Data/Raw/Courts/JIS/TCS"

# cases
tcs_cases <- read_xlsx(
  file.path(
    csg_path, "TCS_Cases_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

# charges
tcs_charges <- read_xlsx(
  file.path(
    csg_path, "TCS_Charges_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

# dispositions
tcs_dispositions <- read_xlsx(
  file.path(
    csg_path, "TCS_DispositionsPerCharge_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

# # sentencing -- this is "Sentencing results on adult criminal FJ and DJ sentencings."
# tcs_sentencing <- read_xlsx(
#   file.path(
#     csg_path, "TCS_Sentencings_A.xlsx"),
#   .name_repair = make_clean_names
#   ) %>%
#   mutate(across(where(is.POSIXct), as.Date))

# placements
tcs_placements <- read_xlsx(
  file.path(
    csg_path, "TCS_Placements_A.xlsx"),
  .name_repair = make_clean_names
  ) %>%
  mutate(across(where(is.POSIXct), as.Date))

```

# 2. De-dup/figure out primary keys for 'cases', 'charges', 'dispositions', and 'placements' and merge together

* `juvenile_nbr` (unique individual ID) and `case_number` (unique case ID, though not sure of "case" definition) appear to be main primary key across files, but will need to use dates at the very least to create pre- and post- disposition/adjudication distinctions in placement data *

* maybe also use `jurist_nbr` ("The professional number associated to the Judge assigned to the case."), either `case_year` or `year`, `tc_sreport_court_jcl` ("AS400 caseload report court code."),

* what's the difference between `case_year` ("Year the case was filed.") and `year` ("Year of the caseload being run/reported.")? and why does the data dictionary indicate that `year` "Must be included in some form to link tables" but not `case_year`?

* two unique juvenile_nbr's can have one case_number? 

* what is `ordertype` in the placements data? many records with value of `ORD` as opposed to `PCN` are missing start dates and/or end dates...


**seemingly important dates:**

* offense_dt
* case_file_dt
* adjudication_dt
* arraignment_dt
* disposition
* case_reopen_dt
* case_closed_dt

```{r include=FALSE}
# de-dup cases file -- there is a very slight discrepancy in N size when de-duping by only juvenile_nbr and case_number as opposed to also including one or more of the above dates; keeping as juvenile_nbr and case_number makes most intuitive sense pending confirmation from JIS contacts (also de-duping by offense_dt as we may need this for later joins...)
tcs_cases_de_dup <- tcs_cases %>%
  filter(!is.na(juvenile_nbr)==TRUE,
         juvenile_nbr!=0, ### there are a handful of records where juvenile_nbr=0; appears to be data error as the records don't consistently share other identifying info like dates and county
         !is.na(case_number)==TRUE) %>% 
  distinct(juvenile_nbr,case_number,offense_dt,.keep_all = TRUE)

# de-dup charges file -- using case_id (same as 'case_number' in tcs_cases and 'id' (which is "Unique ID for the record.")); no records dropped

# issue: there are 1,288 records in the cases df that do not appear at all in the charges df; further there is no juvenile_nbr in the charges data which is concerning for the merge b/c i have seen instances where one case_number has two different juvenile_nbr's attached to it; not sure if we can use these data
tcs_charges_de_dup <- tcs_charges %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(id)==TRUE) %>% 
  dplyr::rename(case_number = case_id) %>% 
  distinct(id,case_number,.keep_all = TRUE)

# de-dup dispositions file -- using case_id (same as 'case_number' in tcs_cases and 'id' (which is "Unique ID for the record.")); no records dropped -- will have to further de-dup by disposition later

# looks like there are some pure dups
tcs_dispositions_de_dup <- tcs_dispositions %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(name_nbr)==TRUE) %>% 
  dplyr::rename(case_number = case_id,
                juvenile_nbr= name_nbr) %>% 
  distinct(juvenile_nbr,case_number,charge_count,charge_count,dispo_dt,event_nbr,.keep_all = TRUE)
  

# de-dup placements file -- using case_id (same as 'case_number' in tcs_cases and 'id' (which is "Unique ID for the record.")); no records dropped 

# looks like there are some pure dups
tcs_placements_de_dup <- tcs_placements %>% 
    filter(!is.na(case_id)==TRUE,
         !is.na(name_nbr)==TRUE) %>% 
  dplyr::rename(case_number = case_id,
                juvenile_nbr= name_nbr) %>% 
  distinct(name_nbr,case_number,.keep_all = TRUE)
```

```{r}
tcs_cases_de_dup_charges <- left_join(tcs_cases_de_dup,tcs_charges_de_dup,by="case_number")
```

