---
title: "mi_front_end_prelim_adjudication_viz"
author: "Andrew Byrum"
date: "3/2022"
output: html_document
---

# {.tabset .tabset-fade .tabset-pills}
```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","tidylog","csgjcr","psych")
```

```{r include=FALSE}
# file path to analytic files
MI_path <- csg_sp_path("JC Research - JJ_Michigan - JJ_Michigan/Data/Converted/Final/Analytic Files")

### import final analytic file
df_mi_front_end_analytic <- read_csv(file = file.path(MI_path, "MI_JJ_joined_file_v4.csv")) %>% 
  ### clean dates and add labels to vars we want to include in tables
  mutate(petition_date = mdy(petition_date),
         disp_date = mdy(disp_date),
         offense_date = mdy(offense_date),
         petition_year = as.character(year(petition_date))) %>% 
  mutate(petition_year = ifelse(is.na(petition_year)==TRUE,"Missing",petition_year)) %>% 
  mutate(race_ethnic = ifelse(is.na(race_ethnic)==TRUE,8,race_ethnic)) %>% 
  mutate(race_ethnic = factor(race_ethnic,
         levels = c(1,2,3,4,5,6,7,8),
         labels = c("White", "Black", "Hispanic", "American Indian/Alaska Native","Asian/Pacific Islander", "Multiracial","Other","Missing"))) %>% 
  mutate(sex = ifelse(is.na(sex)==TRUE,3,sex)) %>% 
  mutate(sex = factor(sex,
         levels = c(1,2,3),
         labels = c("Female", "Male","Missing"))) %>% 
  mutate(off_lvl_disp = ifelse(is.na(off_lvl_disp)==TRUE,7,off_lvl_disp)) %>% 
  mutate(off_lvl_disp = factor(off_lvl_disp,
         levels = c(1,2,3,4,5,6,7),
         labels = c("Felony, Person", "Felony, Non-Person", "Misdemeanor, Person", "Misdemeanor, Non-Person","Status","Other","Missing"))) %>% 
  mutate(off_lvl_pet = ifelse(is.na(off_lvl_pet)==TRUE,7,off_lvl_pet)) %>% 
  mutate(off_lvl_pet = factor(off_lvl_pet,
         levels = c(1,2,3,4,5,6,7),
         labels = c("Felony, Person", "Felony, Non-Person", "Misdemeanor, Person", "Misdemeanor, Non-Person","Status","Other","Missing"))) %>% 
  mutate(age_cat_old = factor(age_cat,
         levels = c(1,2,3,4,5),
         labels = c("Less than 12", "12 to 14", "14 to 16", "16 to 18","18+"))) %>% 
  mutate(age_cat = case_when(age < 11 ~ 1,
                             age >= 11 & age < 13 ~ 2,
                             age >= 13 & age < 17 ~ 3,
                             age >= 17 & age < 21 ~ 4,
                             is.na(age_cat)==TRUE~5),
         age_cat = factor(age_cat,
         levels = c(1,2,3,4,5),
         labels = c("10 and under", "11 to 12", "13 to 16", "17+","Missing"))) %>% 
  mutate(disp_desc = ifelse(is.na(disp_desc)==TRUE,4,disp_desc)) %>% 
  mutate(disp_desc = factor(disp_desc,
         levels = c(1,2,3,4),
         labels = c("Adjudication", "Non-Adjudication", "Other","Missing")))
```


## Trends over Time, 2016-2020

<br>

### Petitions, Consent Calendar %, Adjudication %: 2016 - 2020 (PCS and TCS only)
```{r echo=FALSE,warning=FALSE, message=FALSE}
### 2016-2020
petition_count_year_table_2016_2020 <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         file_src%in%c(3,4)) %>% 
  mutate(cc_ind = ifelse(is.na(cc_ind)==TRUE,0,cc_ind)) %>% 
  group_by(petition_year) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]),
            `Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions (N)`*100, digits = 1),
            `Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0]),
            `Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Non-Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0]),
            `Non-Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Other Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Other" & cc_ind==0]),
            `Other Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Other" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Missing Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0]),
            `Missing Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0])/`Petitions (N)`*100, digits = 1)) %>% 
  ungroup() 


petition_count_year_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         file_src%in%c(3,4)) %>% 
  mutate(cc_ind = ifelse(is.na(cc_ind)==TRUE,0,cc_ind)) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]),
            `Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions (N)`*100, digits = 1),
            `Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0]),
            `Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Non-Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0]),
            `Non-Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Other Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Other" & cc_ind==0]),
            `Other Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Other" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Missing Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0]),
            `Missing Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0])/`Petitions (N)`*100, digits = 1)) %>% 
  mutate(petition_year = "Overall")

### combine
petition_count_year_table_combined_grouped <- rbind(petition_count_year_table_2016_2020,petition_count_year_table_overall)

### print table via kableextra
kable(petition_count_year_table_combined_grouped, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

### Petitions, Consent Calendar %, Adjudication %: 2016 - 2020 (all data sources)
```{r echo=FALSE,warning=FALSE, message=FALSE}
### 2016-2020
petition_count_year_table_2016_2020 <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  mutate(cc_ind = ifelse(is.na(cc_ind)==TRUE,0,cc_ind)) %>% 
  group_by(petition_year) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]),
            `Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions (N)`*100, digits = 1),
            `Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0]),
            `Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Non-Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0]),
            `Non-Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Other Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Other" & cc_ind==0]),
            `Other Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Other" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Missing Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0]),
            `Missing Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0])/`Petitions (N)`*100, digits = 1)) %>% 
  ungroup() 


petition_count_year_table_overall <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020)) %>% 
  mutate(cc_ind = ifelse(is.na(cc_ind)==TRUE,0,cc_ind)) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]),
            `Consent Calendar (%)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions (N)`*100, digits = 1),
            `Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0]),
            `Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Non-Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0]),
            `Non-Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Other Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Other" & cc_ind==0]),
            `Other Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Other" & cc_ind==0])/`Petitions (N)`*100, digits = 1),
            `Missing Adjudication, Non-CC (N)` = n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0]),
            `Missing Adjudication, Non-CC (%)` = round(n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0])/`Petitions (N)`*100, digits = 1)) %>% 
  mutate(petition_year = "Overall")

### combine
petition_count_year_table_combined_grouped <- rbind(petition_count_year_table_2016_2020,petition_count_year_table_overall)

### print table via kableextra
kable(petition_count_year_table_combined_grouped, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```


```{r include=FALSE}
### set theme and font size
theme_set(theme_minimal(24, base_family = "Calibri"))

### disable scientific notation for viz
options(scipen=999)

### full jj blue palette for reference -- NEED NEW PALETTE
jj_pal <- c("#00475d","#007392","#0db4e4","#9ed4ef","#d4e9f8")

new_pal_five <- c("#d6df23","#007392","#eeed90","#0db4e4","#315c15")

new_pal_six <- c("#7fc241","#d6df23","#007392","#eeed90","#0db4e4","#315c15")

new_pal_blue_two <- c("#007392","#0db4e4")

new_pal_blue_two_other <- c("#007392","#d6df23")
```

<br><br>

### VIZ: Petitions, Consent Calendar %, Adjudication %: 2016 - 2020 (TCS AND PCS ONLY B/C OF CONSENT CALENDAR)
```{r echo=FALSE,warning=FALSE, message=FALSE}
### 2016-2020
petition_count_year_table_2016_2020 <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         file_src%in%c(3,4),
         disp_desc!="Missing") %>% 
  mutate(cc_ind = ifelse(is.na(cc_ind)==TRUE,0,cc_ind)) %>%  
  group_by(petition_year) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Consent Calendar` = n_distinct(pet_id[cc_ind==1])/`Petitions (N)`,
            `Adjudication` = n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0])/`Petitions (N)`,
            `Non-Adjudication` = n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0])/`Petitions (N)`,
            `Other` = n_distinct(pet_id[disp_desc=="Other" & cc_ind==0])/`Petitions (N)`,
            `Missing` = n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0])/`Petitions (N)`) %>% 
  ungroup() 

### use gather for plot
petition_count_year_table_2016_2020_plot <- petition_count_year_table_2016_2020 %>%
  gather(adj_type, value, c(`Adjudication`,`Consent Calendar`,`Non-Adjudication`,`Other`)) %>% 
  mutate(petition_year = as.numeric(petition_year))

### plot
adjudication_percent_pcs_tcs_only_with_consent_calendar <- ggplot(data = petition_count_year_table_2016_2020_plot, aes(y = value, x = reorder(petition_year,-petition_year), fill = forcats::fct_rev(adj_type))) + 
  geom_bar(stat = "identity", color = "gray80") +
  # scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = rev(c("#00475d","#007392","#0db4e4","#9ed4ef"))) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
    geom_label(
    aes(
      y = value,
      label = scales::percent(value, accuracy=1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 4,
    colour = "black",
    fill = "white",
    show.legend = FALSE
  ) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12),
        axis.text.x = element_blank(),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

adjudication_percent_pcs_tcs_only_with_consent_calendar

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\adjudication_percent_pcs_tcs_only_with_consent_calendar.png", adjudication_percent_pcs_tcs_only_with_consent_calendar, width = 8, height = 6)
```

<br><br>

### VIZ: Consent Calendar %: 2016 - 2020 (TCS AND PCS ONLY B/C OF CONSENT CALENDAR)
```{r echo=FALSE,warning=FALSE, message=FALSE}
### 2016-2020
petition_count_year_table_2016_2020 <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         file_src%in%c(3,4),
         disp_desc!="Missing") %>% 
  mutate(cc_ind = ifelse(is.na(cc_ind)==TRUE,0,cc_ind)) %>%  
  group_by(petition_year) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Consent Calendar` = n_distinct(pet_id[cc_ind==1])/`Petitions (N)`,
            `Adjudication` = n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0])/`Petitions (N)`,
            `Non-Adjudication` = n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0])/`Petitions (N)`,
            `Other` = n_distinct(pet_id[disp_desc=="Other" & cc_ind==0])/`Petitions (N)`,
            `Missing` = n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0])/`Petitions (N)`) %>% 
  ungroup() 

### plot
consent_calendar_petition_percent_over_time_tcs_pcs <- ggplot(data = petition_count_year_table_2016_2020,
            mapping = aes(x = forcats::fct_rev(petition_year), y = `Consent Calendar`, fill = petition_year)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.3))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Consent Calendar`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

consent_calendar_petition_percent_over_time_tcs_pcs

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\consent_calendar_petition_percent_over_time_tcs_pcs.png", consent_calendar_petition_percent_over_time_tcs_pcs, width = 8, height = 6)
```

<br><br>

### VIZ: Petitions, Consent Calendar %, Adjudication %: 2016 - 2020 (all data sources)
```{r echo=FALSE,warning=FALSE, message=FALSE}
### 2016-2020
petition_count_year_table_2016_2020 <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019,2020),
         disp_desc!="Missing",
         cc_ind!=1) %>% ### remove consent calendar for viz with all counties
  mutate(cc_ind = ifelse(is.na(cc_ind)==TRUE,0,cc_ind)) %>% 
  group_by(petition_year) %>% 
  summarise(`Petitions (N)` = n_distinct(pet_id), 
            `Consent Calendar` = n_distinct(pet_id[cc_ind==1])/`Petitions (N)`,
            `Adjudication` = n_distinct(pet_id[disp_desc=="Adjudication" & cc_ind==0])/`Petitions (N)`,
            `Non-Adjudication` = n_distinct(pet_id[disp_desc=="Non-Adjudication" & cc_ind==0])/`Petitions (N)`,
            `Other` = n_distinct(pet_id[disp_desc=="Other" & cc_ind==0])/`Petitions (N)`,
            `Missing` = n_distinct(pet_id[disp_desc=="Missing" & cc_ind==0])/`Petitions (N)`) %>% 
  ungroup() 

### use gather for plot
petition_count_year_table_2016_2020_plot <- petition_count_year_table_2016_2020 %>%
  gather(adj_type, value, c(`Adjudication`,`Non-Adjudication`,`Other`)) %>% 
  mutate(petition_year = as.numeric(petition_year))

### plot
adjudication_percent_all_data_sources_no_consent <- ggplot(data = petition_count_year_table_2016_2020_plot, aes(y = value, x = reorder(petition_year,-petition_year), fill = forcats::fct_rev(adj_type))) + 
  geom_bar(stat = "identity", color = "gray80") +
  # scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = rev(c("#007392","#0db4e4","#9ed4ef"))) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
    geom_label(
    aes(
      y = value,
      label = scales::percent(value, accuracy=1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 4,
    colour = "black",
    fill = "white",
    show.legend = FALSE
  ) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12),
        axis.text.x = element_blank(),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

adjudication_percent_all_data_sources_no_consent

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\adjudication_percent_all_data_sources_no_consent.png", adjudication_percent_all_data_sources_no_consent, width = 8, height = 6)
```

<br><br>

## Petitions 

<br>

### Petitions per 10k youth by county, 2016-2019 (annual mean petitions per 10k youth, 10-16)
```{r echo=FALSE,message=FALSE,warning=FALSE}
### import ezapop race/ethnicity data for 10-17 y/o michigan residents for rate calculation
df_ezapop_race_ethnicity_10_16_county_level <- readr::read_delim("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Data\\Ezapop\\ezapop_10_16_race_eth_sex_mi.txt", delim = "|") %>% 
  mutate(county_name =  gsub(" County", "", county_name),
         county_id = as.numeric(paste0(state_code,county_code))) %>% 
  dplyr::select(county_name,county_id,overall_10_16_population)

### create overall file for numerator in % calculation below
df_mi_front_end_analytic_county <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(county_id)==TRUE) %>% 
  distinct(pet_id,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode where there is county data
  group_by(county_id,petition_year) %>% 
  summarize(petition_count = n_distinct(pet_id[age>=10 & age <17])) %>% 
  ungroup() %>% 
  group_by(county_id) %>% 
  summarize(petition_count_mean = mean(petition_count,na.rm=TRUE)) %>%
  ungroup() %>%
  left_join(df_ezapop_race_ethnicity_10_16_county_level, by = "county_id") %>% 
  mutate(petitions_per_10k_youth = round(petition_count_mean/overall_10_16_population*10000, digits = 1))

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- df_mi_front_end_analytic_county %>%
  pull(petitions_per_10k_youth) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels youth pop
label_petition_rate <- c("323 to 437","283 to 323","210 to 283", "85 to 210")

### create a new variable with the specified quantiles
df_mi_front_end_analytic_county %<>%
  mutate(petitions_per_10k_youth_quartile = cut(-petitions_per_10k_youth,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_petition_rate,
                               include.lowest = T)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) 


### plot
front_end_petition_rate_per_county <- ggplot(data = df_mi_front_end_analytic_county,
            mapping = aes(x = reorder(county_anonymous, petitions_per_10k_youth), y = petitions_per_10k_youth, fill = petitions_per_10k_youth_quartile)) + 
  geom_bar(stat = "identity", color="white", size=0.15) +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(limits=c(min(0), 
                                           max(450))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 15, y = 385, label = "Each bar represents one county's\n petition rate", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = "Petitions per 10k Youth") +
    coord_flip() +
  guides(fill = guide_legend(reverse = FALSE)) 

front_end_petition_rate_per_county

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\front_end_petition_rate_per_county.png", front_end_petition_rate_per_county, width = 8, height = 6)
```

<br>

### Distribution of County Youth Population by Petition Rate Quartile
```{r echo=FALSE,message=FALSE,warning=FALSE}
### plot county population size
ggplot(data = df_mi_front_end_analytic_county,
            mapping = aes(x = reorder(county_anonymous, petitions_per_10k_youth), y = overall_10_16_population, fill = petitions_per_10k_youth_quartile)) + 
  geom_bar(stat = "identity", color="white", size=0.15) +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::comma_format()) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 15, y = 360, label = "Each bar represents one county's\n petition rate", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = "Overall Youth Population Estimate (N)", x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = "Petitions per 10k Youth") +
    coord_flip() +
  guides(fill = FALSE) 
```

<br><br>

## Consent Calendar (TCS & PCS only)

<br>

### Count/Proportion by Race/Ethnicity, 2016-2019
```{r echo=FALSE,warning=FALSE, message=FALSE}
df_mi_front_end_analytic_consent <- df_mi_front_end_analytic %>% 
  filter(!is.na(cc_ind)==TRUE)

petition_count_race_table_overall <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(race_ethnic)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  mutate(race_ethnic = "Overall")

petition_count_race_table <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(race_ethnic)==TRUE) %>% 
  group_by(race_ethnic) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/petition_count_race_table_overall$`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  ungroup() 

### combine
petition_count_race_table_combined <- rbind(petition_count_race_table,petition_count_race_table_overall)

### print table via kableextra
kable(petition_count_race_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8:9, bold = TRUE)
```

<br><br>

### VIZ: Count/Proportion by Race/Ethnicity, 2016-2019 (ROW PERCENT)
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_race_table_overall <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(race_ethnic)==TRUE,
         race_ethnic!="Missing") %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  mutate(race_ethnic = "Overall")


petition_count_race_table <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(race_ethnic)==TRUE,
         race_ethnic!="Missing") %>% 
  group_by(race_ethnic) %>% 
  dplyr::summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`,
            `Petitions, Consent Calendar (Column %)` = n_distinct(pet_id[cc_ind==1])/petition_count_race_table_overall$`Petitions, Consent Calendar (N)`) %>% 
  ungroup() %>% 
  mutate(race_ethnic = factor(race_ethnic,
                              levels = c("American Indian/Alaska Native","Asian/Pacific Islander","Black","Hispanic","Multiracial","White","Other")))


### plot
consent_calendar_race_ethnicity_row_percent_tcs_pcs <- ggplot(data = petition_count_race_table,
            mapping = aes(x = forcats::fct_rev(race_ethnic), y = `Petitions, Consent Calendar (Row %)`, fill = race_ethnic)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.3))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Petitions, Consent Calendar (Row %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

consent_calendar_race_ethnicity_row_percent_tcs_pcs

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\consent_calendar_race_ethnicity_row_percent_tcs_pcs.png", consent_calendar_race_ethnicity_row_percent_tcs_pcs, width = 8, height = 6)
```

<br><br>

### VIZ: Count/Proportion by Race/Ethnicity, 2016-2019 (COLUMN PERCENT)
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_race_table_overall <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(race_ethnic)==TRUE,
         race_ethnic!="Missing") %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  mutate(race_ethnic = "Overall")


petition_count_race_table <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(race_ethnic)==TRUE,
         race_ethnic!="Missing") %>% 
  group_by(race_ethnic) %>% 
  dplyr::summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`,
            `Petitions, Consent Calendar (Column %)` = n_distinct(pet_id[cc_ind==1])/petition_count_race_table_overall$`Petitions, Consent Calendar (N)`) %>% 
  ungroup() %>% 
  mutate(race_ethnic = factor(race_ethnic,
                              levels = c("American Indian/Alaska Native","Asian/Pacific Islander","Black","Hispanic","Multiracial","White","Other")))


### plot
consent_calendar_race_ethnicity_column_percent_tcs_pcs <- ggplot(data = petition_count_race_table,
            mapping = aes(x = forcats::fct_rev(race_ethnic), y = `Petitions, Consent Calendar (Column %)`, fill = race_ethnic)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.8))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Petitions, Consent Calendar (Column %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

consent_calendar_race_ethnicity_column_percent_tcs_pcs

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\consent_calendar_race_ethnicity_column_percent_tcs_pcs.png", consent_calendar_race_ethnicity_column_percent_tcs_pcs, width = 8, height = 6)
```

<br><br>

### Count/Proportion by Offense (most serious petitioned offense), 2016-2019
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_off_table_overall <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  mutate(off_lvl_pet = "Overall")

petition_count_off_table <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE) %>% 
  group_by(off_lvl_pet) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/petition_count_off_table_overall$`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  ungroup() 

### combine
petition_count_off_table_combined <- rbind(petition_count_off_table,petition_count_off_table_overall)

### print table via kableextra
kable(petition_count_off_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7:8, bold = TRUE)
```

<br><br>

### VIZ: Count/Proportion by Offense, 2016-2019 (most serious petitioned offense), 2016-2019 (row percentages)

```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_off_table_overall <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE,
         off_lvl_pet!="Missing",
         off_lvl_pet!="Other") %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  mutate(off_lvl_pet = "Overall")

petition_count_off_table <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE,
         off_lvl_pet!="Missing",
         off_lvl_pet!="Other") %>% 
  group_by(off_lvl_pet) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`,
            `Petitions, Consent Calendar (Column %)` = n_distinct(pet_id[cc_ind==1])/petition_count_off_table_overall$`Petitions, Consent Calendar (N)`) %>% 
  ungroup() %>% 
  mutate(off_lvl_pet = factor(off_lvl_pet,
                                levels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status")))


### plot
consent_calendar_offense_row_percent_other_missing_exclude_pcs_tcs <- ggplot(data = petition_count_off_table,
            mapping = aes(x = forcats::fct_rev(off_lvl_pet), y = `Petitions, Consent Calendar (Row %)`, fill = off_lvl_pet)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.3))) +
  scale_x_discrete(labels = scales::wrap_format(7)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Petitions, Consent Calendar (Row %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

consent_calendar_offense_row_percent_other_missing_exclude_pcs_tcs
  
  
ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\consent_calendar_offense_row_percent_other_missing_exclude_pcs_tcs.png", consent_calendar_offense_row_percent_other_missing_exclude_pcs_tcs, width = 8, height = 6)
```

<br><br>

### VIZ: Count/Proportion by Offense, 2016-2019 (most serious petitioned offense), 2016-2019 (column percentages)

```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_off_table_overall <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE,
         off_lvl_pet!="Missing",
         off_lvl_pet!="Other") %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  mutate(off_lvl_pet = "Overall")

petition_count_off_table <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE,
         off_lvl_pet!="Missing",
         off_lvl_pet!="Other") %>% 
  group_by(off_lvl_pet) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`,
            `Petitions, Consent Calendar (Column %)` = n_distinct(pet_id[cc_ind==1])/petition_count_off_table_overall$`Petitions, Consent Calendar (N)`) %>% 
  ungroup() %>% 
  mutate(off_lvl_pet = factor(off_lvl_pet,
                                levels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status")))


### plot
consent_calendar_offense_column_percent_other_missing_exclude_pcs_tcs <- ggplot(data = petition_count_off_table,
            mapping = aes(x = forcats::fct_rev(off_lvl_pet), y = `Petitions, Consent Calendar (Column %)`, fill = off_lvl_pet)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.4))) +
  scale_x_discrete(labels = scales::wrap_format(7)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Petitions, Consent Calendar (Column %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

consent_calendar_offense_column_percent_other_missing_exclude_pcs_tcs
  
  
ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\consent_calendar_offense_column_percent_other_missing_exclude_pcs_tcs.png", consent_calendar_offense_column_percent_other_missing_exclude_pcs_tcs, width = 8, height = 6)
```

<br><br>

### Count/Proportion by Age, 2016-2019
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table_overall <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  mutate(age_cat = "Overall") 

petition_count_age_table <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE) %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = round(n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`*100, digits = 1),
            `Petitions, Consent Calendar (Column %)` = round(n_distinct(pet_id[cc_ind==1])/petition_count_age_table_overall$`Petitions, Consent Calendar (N)`*100, digits = 1)) %>% 
  ungroup() 

### combine
petition_count_age_table_combined <- rbind(petition_count_age_table,petition_count_age_table_overall)

### print table via kableextra
kable(petition_count_age_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5:6, bold = TRUE)
```

<br><br>

### VIZ: Count/Proportion by Age, 2016-2019 (ROW PERCENT)
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table_overall <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE,
         age_cat!="Missing") %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`,
            `Petitions, Consent Calendar (Column %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar (N)`) %>% 
  mutate(age_cat = "Overall") 

petition_count_age_table <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE,
         age_cat!="Missing") %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`,
            `Petitions, Consent Calendar (Column %)` = n_distinct(pet_id[cc_ind==1])/petition_count_age_table_overall$`Petitions, Consent Calendar (N)`) %>% 
  ungroup() 

### plot
consent_calendar_age_row_percent_missing_exclude_pcs_tcs <- ggplot(data = petition_count_age_table,
            mapping = aes(x = forcats::fct_rev(age_cat), y = `Petitions, Consent Calendar (Row %)`, fill = age_cat)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.3))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Petitions, Consent Calendar (Row %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

consent_calendar_age_row_percent_missing_exclude_pcs_tcs

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\consent_calendar_age_row_percent_missing_exclude_pcs_tcs.png", consent_calendar_age_row_percent_missing_exclude_pcs_tcs, width = 8, height = 6)
```

<br><br>

### VIZ: Count/Proportion by Age, 2016-2019 (COLUMN PERCENT)
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table_overall <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE,
         age_cat!="Missing") %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`,
            `Petitions, Consent Calendar (Column %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Consent Calendar (N)`) %>% 
  mutate(age_cat = "Overall") 

petition_count_age_table <- df_mi_front_end_analytic_consent %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE,
         age_cat!="Missing") %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id), 
            `Petitions, Consent Calendar (N)` = n_distinct(pet_id[cc_ind==1]), 
            `Petitions, Consent Calendar (Row %)` = n_distinct(pet_id[cc_ind==1])/`Petitions, Overall (N)`,
            `Petitions, Consent Calendar (Column %)` = n_distinct(pet_id[cc_ind==1])/petition_count_age_table_overall$`Petitions, Consent Calendar (N)`) %>% 
  ungroup() 

### plot
consent_calendar_age_column_percent_missing_exclude_pcs_tcs <- ggplot(data = petition_count_age_table,
            mapping = aes(x = forcats::fct_rev(age_cat), y = `Petitions, Consent Calendar (Column %)`, fill = age_cat)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.85))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Petitions, Consent Calendar (Column %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

consent_calendar_age_column_percent_missing_exclude_pcs_tcs

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\consent_calendar_age_column_percent_missing_exclude_pcs_tcs.png", consent_calendar_age_column_percent_missing_exclude_pcs_tcs, width = 8, height = 6)
```

<br><br>


## Adjudication

<br>


### Count/Proportion by Offense (most serious petitioned offense), 2016-2019

Note: Petitions with Missing Adjudication data dropped from Adjudication/Non-Adjudication/Other %'s (8% of all petitions). Consent calendar petitions also dropped.
```{r echo=FALSE,warning=FALSE, message=FALSE}
df_mi_front_end_analytic_adjudication <- df_mi_front_end_analytic %>% 
  filter((cc_ind==0 | is.na(cc_ind)==TRUE) & disp_desc!="Missing")

### petitioned offense
petition_count_off_table_overall_adj <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Adjudication (N)`*100, digits = 1),
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Other (N)`*100, digits = 1)) %>%  
  mutate(off_lvl = "Overall")

petition_count_off_table_adj <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE) %>% 
  group_by(off_lvl_pet) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/petition_count_off_table_overall_adj$`Adjudication (N)`*100, digits = 1),
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/petition_count_off_table_overall_adj$`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/petition_count_off_table_overall_adj$`Other (N)`*100, digits = 1)) %>%  
  rename(off_lvl = off_lvl_pet)

### combine
petition_count_off_table_adj_combined <- rbind(petition_count_off_table_adj,petition_count_off_table_overall_adj)

# ### join both final offense tables
# ### join two tables
# adjudication_count_off_table_final <- left_join(petition_count_off_table_pet_combined,petition_count_off_table_adj_combined, by = "off_lvl")

### print table via kableextra
kable(petition_count_off_table_adj_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7:8, bold = TRUE)
```

<br><br>

### VIZ: Count/Proportion by Offense (most serious petitioned offense), 2016-2019 (column percentages)

Note: Petitions with Missing Adjudication data dropped from Adjudication/Non-Adjudication/Other %'s (8% of all petitions). Consent calendar petitions also dropped.
```{r echo=FALSE,warning=FALSE, message=FALSE}
### petitioned offense
petition_count_off_table_overall_adj <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE,
         off_lvl_pet!="Missing",
         off_lvl_pet!="Other") %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Adjudication (N)`*100, digits = 1),
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Other (N)`*100, digits = 1)) %>%  
  mutate(off_lvl = "Overall")

petition_count_off_table_adj <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE,
         off_lvl_pet!="Missing",
         off_lvl_pet!="Other") %>% 
  group_by(off_lvl_pet) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Adjudication (Column %)` = n_distinct(pet_id[disp_desc=="Adjudication"])/petition_count_off_table_overall_adj$`Adjudication (N)`,
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/petition_count_off_table_overall_adj$`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/petition_count_off_table_overall_adj$`Other (N)`*100, digits = 1)) %>%  
  ungroup() %>% 
  rename(off_lvl = off_lvl_pet) %>% 
  mutate(off_lvl = factor(off_lvl,
                                levels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status")))


### plot
adjudication_offense_column_percent_other_missing_excluded <- ggplot(data = petition_count_off_table_adj,
            mapping = aes(x = forcats::fct_rev(off_lvl), y = `Adjudication (Column %)`, fill = off_lvl)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.3))) +
  scale_x_discrete(labels = scales::wrap_format(7)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Adjudication (Column %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

adjudication_offense_column_percent_other_missing_excluded
  
  
ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\adjudication_offense_column_percent_other_missing_excluded.png", adjudication_offense_column_percent_other_missing_excluded, width = 8, height = 6)
```

<br><br>

### VIZ: Count/Proportion by Offense (most serious petitioned offense), 2016-2019 (row percentages)

Note: Petitions with Missing Adjudication data dropped from Adjudication/Non-Adjudication/Other %'s (8% of all petitions). Consent calendar petitions also dropped.
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_off_table_adj <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(off_lvl_pet)==TRUE,
         off_lvl_pet!="Missing",
         off_lvl_pet!="Other") %>% 
  group_by(off_lvl_pet) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`,
            `Adjudication (Column %)` = n_distinct(pet_id[disp_desc=="Adjudication"])/petition_count_off_table_overall_adj$`Adjudication (N)`,
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`,
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/petition_count_off_table_overall_adj$`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/petition_count_off_table_overall_adj$`Other (N)`*100, digits = 1)) %>%  
  ungroup() %>% 
  rename(off_lvl = off_lvl_pet) %>% 
  mutate(off_lvl = factor(off_lvl,
                                levels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status")))


### plot
adjudication_offense_row_percent_other_missing_excluded <- ggplot(data = petition_count_off_table_adj,
            mapping = aes(x = forcats::fct_rev(off_lvl), y = `Adjudication (Row %)`, fill = off_lvl)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.75))) +
  scale_x_discrete(labels = scales::wrap_format(7)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Adjudication (Row %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

adjudication_offense_row_percent_other_missing_excluded
  
  
ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\adjudication_offense_row_percent_other_missing_excluded.png", adjudication_offense_row_percent_other_missing_excluded, width = 8, height = 6)
```

<br><br>

### Count/Proportion by Age, 2016-2019

Note: Petitions with Missing Adjudication data dropped from Adjudication/Non-Adjudication/Other %'s (8% of all petitions). Consent calendar petitions also dropped.
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table_overall <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Adjudication (N)`*100, digits = 1),
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Other (N)`*100, digits = 1)) %>% 
  mutate(age_cat = "Overall") 

petition_count_age_table <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE) %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/petition_count_age_table_overall$`Adjudication (N)`*100, digits = 1),
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/petition_count_age_table_overall$`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/petition_count_age_table_overall$`Other (N)`*100, digits = 1)) %>% 
  ungroup() 

### combine
petition_count_age_table_combined <- rbind(petition_count_age_table,petition_count_age_table_overall)

### print table via kableextra
kable(petition_count_age_table_combined, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5:6, bold = TRUE)
```

<br><br>

### VIZ: Count/Proportion by Age, 2016-2019 (ROW PERCENT)

Note: Petitions with Missing Adjudication data dropped from Adjudication/Non-Adjudication/Other %'s (8% of all petitions). Consent calendar petitions also dropped.
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table_adj <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE,
         age_cat!="Missing") %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`,
            `Adjudication (Column %)` = n_distinct(pet_id[disp_desc=="Adjudication"])/petition_count_off_table_overall_adj$`Adjudication (N)`,
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`,
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/petition_count_off_table_overall_adj$`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/petition_count_off_table_overall_adj$`Other (N)`*100, digits = 1)) %>%  
  ungroup() 
  # mutate(off_lvl = factor(off_lvl,
  #                               levels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status")))


### plot
adjudication_age_row_percent_missing_excluded <- ggplot(data = petition_count_age_table_adj,
            mapping = aes(x = forcats::fct_rev(age_cat), y = `Adjudication (Row %)`, fill = age_cat)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.65))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Adjudication (Row %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

adjudication_age_row_percent_missing_excluded

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\adjudication_age_row_percent_missing_excluded.png", adjudication_age_row_percent_missing_excluded, width = 8, height = 6)
```

<br><br>

### VIZ: Count/Proportion by Age, 2016-2019 (COLUMN PERCENT)

Note: Petitions with Missing Adjudication data dropped from Adjudication/Non-Adjudication/Other %'s (8% of all petitions). Consent calendar petitions also dropped.
```{r echo=FALSE,warning=FALSE, message=FALSE}
petition_count_age_table_overall <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE,
         age_cat!="Missing") %>%  
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Adjudication"])/`Adjudication (N)`*100, digits = 1),
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`*100, digits = 1),
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Other (N)`*100, digits = 1)) %>% 
  mutate(age_cat = "Overall") 

petition_count_age_table_adj <- df_mi_front_end_analytic_adjudication %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(age_cat)==TRUE,
         age_cat!="Missing") %>% 
  group_by(age_cat) %>% 
  summarise(`Petitions, Overall (N)` = n_distinct(pet_id[!is.na(disp_desc)==TRUE]),
            `Adjudication (N)` = n_distinct(pet_id[disp_desc=="Adjudication"]),
            `Adjudication (Row %)` = n_distinct(pet_id[disp_desc=="Adjudication"])/`Petitions, Overall (N)`,
            `Adjudication (Column %)` = n_distinct(pet_id[disp_desc=="Adjudication"])/petition_count_age_table_overall$`Adjudication (N)`,
            `Non-Adjudication (N)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"]),
            `Non-Adjudication (Row %)` = n_distinct(pet_id[disp_desc=="Non-Adjudication"])/`Petitions, Overall (N)`,
            `Non-Adjudication (Column %)` = round(n_distinct(pet_id[disp_desc=="Non-Adjudication"])/petition_count_age_table_overall$`Non-Adjudication (N)`*100, digits = 1),
             `Other (N)` = n_distinct(pet_id[disp_desc=="Other"]),
             `Other (Row %)` = round(n_distinct(pet_id[disp_desc=="Other"])/`Petitions, Overall (N)`*100, digits = 1),
             `Other (Column %)` = round(n_distinct(pet_id[disp_desc=="Other"])/petition_count_age_table_overall$`Other (N)`*100, digits = 1)) %>%  
  ungroup() 
  # mutate(off_lvl = factor(off_lvl,
  #                               levels = c("Felony, Person","Felony, Non-Person","Misdemeanor, Person","Misdemeanor, Non-Person","Status")))


### plot
adjudication_age_column_percent_missing_excluded <- ggplot(data = petition_count_age_table_adj,
            mapping = aes(x = forcats::fct_rev(age_cat), y = `Adjudication (Column %)`, fill = age_cat)) + 
  geom_bar(stat = "identity", color = "gray40") +
  scale_fill_manual(values = c("#007392","#007392","#007392","#007392","#007392","#007392")) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.9))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 4, y = .2, label = "Each bar represents the % of detentions for status offenses\nwithin one county", colour = "#00475d", size = 4) +
    theme(strip.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold", hjust = 1, size = 12)) +
    labs(y = NULL, x = NULL,
    caption = NULL,
    title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  guides(fill = FALSE) + 
  geom_label_repel(aes(label = percent(`Adjudication (Column %)`, accuracy = .1)),
                  direction = 'x',
                  hjust = 0.75,
                  label.padding = 0.5,
                  fill = "white",
                  color = "gray40",
                  box.padding = 0.25,
                  fontface = "bold",
                  na.rm = TRUE,
                  show.legend = FALSE)

adjudication_age_column_percent_missing_excluded

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\adjudication_age_column_percent_missing_excluded.png", adjudication_age_column_percent_missing_excluded, width = 8, height = 6)
```

<br><br>

### Adjudications per 10k youth by county, 2016-2019
```{r echo=FALSE,message=FALSE,warning=FALSE}
### create overall file for numerator in % calculation below
df_mi_front_end_analytic_county_adj <- df_mi_front_end_analytic %>% 
  filter(petition_year%in%c(2016,2017,2018,2019),
         !is.na(county_id)==TRUE) %>% 
  distinct(pet_id,.keep_all = TRUE) %>% ### de-dup by person and placement episode since we want to take the mean of a value duplicated across all placements within placement episode; we want one record per youth per placement episode where there is county data
  group_by(county_id,petition_year) %>% 
  summarize(adjudication_case_count = n_distinct(pet_id[disp_desc=="Adjudication" & age>=10 & age <17])) %>% 
  ungroup() %>% 
  group_by(county_id) %>% 
  summarize(adjudication_case_count_mean = mean(adjudication_case_count,na.rm=TRUE)) %>%
  ungroup() %>%
  left_join(df_ezapop_race_ethnicity_10_16_county_level, by = "county_id") %>% 
  mutate(adjudications_per_10k_youth = round(adjudication_case_count_mean/overall_10_16_population*10000, digits = 1))

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- df_mi_front_end_analytic_county_adj %>%
  pull(adjudications_per_10k_youth) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels youth pop
label_adj_rate <- c("133 to 194","110 to 133","60 to 110", "0 to 60")

### create a new variable with the specified quantiles
df_mi_front_end_analytic_county_adj %<>%
  mutate(adjudication_per_10k_youth_quartile = cut(-adjudications_per_10k_youth,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_adj_rate,
                               include.lowest = T)) %>% 
  mutate(county_anonymous = paste0("County ", row_number())) 


### plot
front_end_adjudication_rate_per_county <- ggplot(data = df_mi_front_end_analytic_county_adj,
            mapping = aes(x = reorder(county_anonymous, adjudications_per_10k_youth), y = adjudications_per_10k_youth, fill = adjudication_per_10k_youth_quartile)) + 
  geom_bar(stat = "identity", color="white", size=0.15) +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(limits=c(min(0), 
                                           max(200))) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  annotate("text", x = 15, y = 165, label = "Each bar represents one county's\n adjudication rate", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = NULL, x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = "Adjudications per 10k Youth") +
    coord_flip() +
  guides(fill = guide_legend(reverse = FALSE)) 

front_end_adjudication_rate_per_county

ggsave("C:\\Users\\abyrum\\The Council of State Governments\\JC Research - Documents\\JC Research - JJ_Michigan - JJ_Michigan\\Work Products\\r_viz\\front_end_ppt_03_12\\front_end_adjudication_rate_per_county.png", front_end_adjudication_rate_per_county, width = 8, height = 6)
```

<br>

### Distribution of County Youth Population by Adjudication Rate Quartile
```{r echo=FALSE,message=FALSE,warning=FALSE}
### plot county population size 
ggplot(data = df_mi_front_end_analytic_county_adj,
            mapping = aes(x = reorder(county_anonymous, adjudications_per_10k_youth), y = overall_10_16_population, fill = adjudication_per_10k_youth_quartile)) + 
  geom_bar(stat = "identity", color="white", size=0.15) +
  scale_fill_manual(values = c("#00475d","#007392","#0db4e4","#9ed4ef")) +
  scale_y_continuous(labels = scales::comma_format()) +
  scale_x_discrete(labels = scales::wrap_format(18)) +
  # annotate("text", x = 15, y = 150, label = "Each bar represents one county's\n adjudication rate", colour = "#00475d", size = 4) +
    theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = "Overall Youth Population Estimate (N)",
         x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = "Adjudications per 10k Youth") +
    coord_flip() +
  guides(fill = FALSE) 
```

<br><br>
